### 2015-06-16 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya.tex
Iliya corrections

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for double-spaced preprint

%Phys Rev B
%Letter or rapid communication - 3500 words
%\documentclass[prb,groupedaddress,reprint]{revtex4-1}
%APL
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,reprint]{revtex4-1}
%\documentclass[aip,jap,reprint]{revtex4-1}
\usepackage[english]{babel}
\usepackage{graphicx}% Include figure files
\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%
filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}
\usepackage[figure,table]{hypcap} %links should lead to the begining
                                %of figure or table...

\begin{document} %Max size in pdf for APL - 4 print pages

\title{Super absorption and efficient absorption of light by spherical
  nanoparticles}

\author{Konstantin Ladutenko} \email[e-mail: ]{fisik2000@mail.ru}
\affiliation{ITMO University, 49 Kronverskii Ave., St.~Petersburg
  197101, Russian Federation\\}

\affiliation{Ioffe Physical-Technical Institute of the Russian Academy
  of Sciences, 26 Polytekhnicheskaya Str., St.~Petersburg 194021,
  Russian Federation}

\author{Ovidio Pe\~{n}a-Rodr\'{i}guez} \affiliation{Instituto de
  Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid,\\
  Jos\'{e} Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain}

% \author{Irina Melchakova} \author{Alexander Shalin}
% \affiliation{ITMO University, 49 Kronverskii Ave., St.~Petersburg
% 197101, Russian Federation\\} TODO не хватает адреса
% \affiliation{Kotel’nikov Institute of Radio Engineering and
% Electronics of RAS (Ulyanovsk branch),\\48 Goncharov Str., Ulyanovsk
% 432011, Russian Federation} \affiliation{Ulyanovsk State University,
% 42 L. Tolstoy Str., Ulyanovsk 432017, Russian Federation}
% \author{Ilya Yagupov} \author{Pavel Belov} \affiliation{ITMO
% University, 49 Kronverskii Ave., St.~Petersburg 197101, Russian
% Federation\\}
\author{Ali Mirzaei} \author{Andrey Miroshnichenko} \author{Ilya
  Shadrivov} \affiliation{Nonlinear Physics Centre, Research School of
  Physics and Engineering, The Australian National University, 59
  Mills Rd, Acton, ACT, 2601, Australia}

\date{\today}
% APL 250 words! Moreover, some designs have spectral Phys Rev B less
% then 500 words, about 5% ot total paper length
% emacs M-x count-words

\begin{abstract}
  Spherical subwavelength nanoparticles have a fundamental limit as to
  how much light they can absorb. This limit is based on the
  assumption that only one mode is excited in the nanoparticle. Using
  genetic algorithm, we design multi-layer nanoparticles, in which we
  can make several resonant modes overlap at the same frequency, thus
  significantly beating the theoretical limit of absorption, and we
  call this super-absorption. We further introduce the efficiency of
  the absorption for a nanoparticle, which is absorption normalized by
  the physical size of the particle, and show that efficient absorbers
  are not always operating in super-absorbing regime.
\end{abstract}

\pacs% insert suggested PACS numbers in braces on next line
{41.20.Jb 42.25.Bs 02.60.Pn 02.70.-c}
% 41.20.Jb Electromagnetic wave propagation 42.25.Bs Wave propagation,
% transmission and absorption
%% 42.25.Fx Diffraction and scattering
% 02.60.Pn Numerical optimization 02.70.-c Computational techniques;
% simulations

\maketitle %\maketitle must follow title, authors, abstract and \pacs

Mie theory~[TODO], which is over 100 years old now, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these days~[TODO], since it is one
of the primary tools for analyzing wave scattering by spherical
objects. Further development of the Mie theory~\cite{Yang-2003,
  Pena-scattnlay-2009} made it possible to apply study the
multilayered spherical particles [TODO]. Such particles have various
applications in cancer treatment [TODO 5,6 from Ovidio draft] and
medical diagnostics [TODO 7 from Ovidio draft],
cloaking~\cite{Semouchkina-2013, Ladutenko-2014} and plasmonic~[TODO]
devices, as well as for improving solar cells performance [TODO].

The scattering properties of multilayer cylinders and spheres was
studied in great detail by Fan~et~al.~[Fan-PRL, Fan-APL]. In these
works authors introduced the concept of a super scattering, when the
scattering cross-section of a multilayer particle exceeds that of a
homogeneous particle of the same size in the so-called single-channel
limit. The super scattering appears when we design a multilayer
structure so that several modes become nearly degenerate, i.e. their
resonance frequencies coincide or get close to each other. In a
homogeneous particle, the resonances appear at different frequencies,
and there is no design freedom for a fixed geometry of the structure
to make these resonances overlap, and this limits the achievable
scattering cross-section.

Similar fundamental limitations exist for the absorbing properties of
sub-wavelength nanoparticles.  Tribelsky [TODO] has derived a
theoretical limit of a maximum absorption cross-section (ACS) value
for a single channel, i.e., when only one mode of the sphere is
excited.  As a result the absorption coefficients $\tilde{a}_n= {\rm
  Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} - |b_n|^2 $
become limited by $1/4$, here $a_n$ and $b_n$ are scattering
coefficient as defined in Mie theory [TODO Bohren Huffman]).

To overcome these limitations, we employ similar approach for
enhancing absorption cross-section [Fan-APL]. In particular, we
propose to use the multi-layer structures, and by means of genetic
algorithm we optimize the ACS of these particles. We analyze the
absorption cross-section of these particles, and present the
super-absorption regime. We further introduce the absorption
efficiency, which is the ACS normalized to the geometric cross-section
of the particles. Here we show that there is a strong counter-play
between the increased absorption for larger particles vs size for
smaller particles, and quite remarkably we find that the most {\em
  efficient} absorption can be achieved in a single channel limit for
small particles.

We start our analyses by considering the triple layered $Si/Ag/Si$
spherical particle illuminated with a plane wave~(Fig. TODO ). In what
follows we describe the materials using experimentally measured
parameters from the Ref.~[TODO].  To optimize the thickness of each
layer we implemented~[link to GitHub] an adaptive differential
evolution algorithm~\cite{Storn-DE-first-1997}, which is called
JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
optimization algorithm are published previously in
Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
Scattnlay~\cite{Pena-scattnlay-2009} software, whose results were
verified with a number of other implementations of the Mie solutions
and with a commercially available software such as CST Microwave
studio.

It is obvious that in general, a bigger particle will have a bigger
absorption cross-section, so sphere with the diameter of 1 cm will
absorb more light than any sphere at the nanoscale. Therefore, we use
absorption efficiency $Q_{\rm abs}=C_{\rm abs}/2\pi R_{\rm total}^2$,
where $R_{\rm total}$ is the outer radius of the particle and $C_{\rm
  abs}$ is the absorption cross-section. We maximize absorption
efficiency at a fixed wavelength of incident light (we have chosen
$\lambda=500$~nm).

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
    \caption{ Results of the optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved at the particle radius of 36~nm and
      Ag/Si design (zero sized core). Dashed lines show theoretical
      limits for the first channel and second channel
      absorption. Second and third peaks in the absorption efficiency
      curve exceed the theoretical limit for the second mode
      absorption at R=63~nm and R=81~nm. (b) Mie
coefficients for individual excited modes of the optimized structures
[Kostya - why do they have tildas - are these not directly Mie
coefficients?]. (c) Optimized layer thicknesses. For the total
particle radius below 46~nm the genetic algorithm converges to the
two-layer structure, when core size vanishes, and the optimum design
is a bi-layer $Ag/Si$ particle.

      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency.  We show the results of our genetic optimization algorithm
in Fig.~\ref{fig:overview}a.  Dashed lines show theoretical absorption
limit of a dipole ($n=1$) and a quadrupole ($n=2$)
resonances~[Tribelsky:TODO], which are given as $$Q^{(n)}_{\rm abs\
  max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi R_{\rm
  total}/\lambda$, and $n$ is an angular momentum of the
mode. Following Ref.~[Fan-APL], where authors introduce super
scattering for spherical particles, here we we introduce
super-absorption, when the ACS is larger than the theoretical limit
for absorption by the mode with highest excited angular momentum
$n$. In our parameter space we have just modes up to the quadrupole
excited ($n=2$), and in order to get a super-absorption our efficiency
should be higher than that of a quadrupole. We clearly see this
super-absorption at $R_{\rm total}>60$~nm, in Fig.~\ref{fig:overview}
(a).

In Fig.~\ref{fig:overview}b we present the values of Mie coefficients
for individual excited modes in the structure, while horizontal dashed
line shows the theoretical limit (1/4) for each of
them. $\tilde{a}_{1,2}$ are electric dipole and electric quadrupole,
while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
quadrupole. For small particles, as expected, the absorption is
dominated by an electric dipole $\tilde{a}_1$.  At $R_{\rm total} >
56.6$~nm the optimization procedure finds that the designs with both
electric and magnetic dipoles have larger ACS, than the structure with
only the electric dipole excited. This is why the curves in
Figs.~\ref{fig:overview} (b,c) experience the discontinuity. We also
note that there is a very narrow range of particle sizes, between
80.7~nm and 82.1~nm, where our analyses finds that the design
supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
$\tilde{b}_2$, has larger ACS, and this explains two more
discontinuities of the curves at the respective size values.

Fig.~\ref{fig:overview} (c) shows optimized sizes of the layers inside
the multi-layer structure. It reveals quite a curious result, that the
dipole branch (i.e. for particle radii below 56.6~nm) has two
parts. For $R_{\rm total}<46$~nm the best absorber has just two
layers, as the radius of the core of the three-layer structure
vanishes, and the particle reduces to $Ag/Si$ core-shell structure.
At $R_{\rm total}=46$ dipole channel becomes practically
undistinguishable from the theoretical limit (it becomes
$\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
inner $Si$ layer in order to keep $\tilde{a}_1$ near the theoretical
limit as the $R_{\rm total}$ increases.  As a side effect, the
quadrupole contribution $\tilde{a}_2$ appears, however, it does not
help to reach super-absorption limit $n=2$.

Remarkably, the absolute maximum absorption efficiency is not reached
within the super-absorption regime. Figure~\ref{fig:overview} shows
that the maximum efficiency is reached for small particle size, and
the ACS is still well below the single channel limit. It appears that
the $Ag/Si$ core-shell nanoparticle, with the total radii of
approximately 36~nm is the most efficient absorbing in the considered
structure, which ACS reaching values over 5 times the physical
cross-section area of the particle.  From practical point of view it
is quite important that the maximum can be reached in a bi-layer
structure, instead of a triple-layer, and it should be easier and
cheaper to produce.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
    \caption{Spectra of Mie coefficients of (a) efficient and (b-c)super absorption design.      
      \label{fig:spectra}
    }%
  }
\end{figure}
%
To study spectral properties of the structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview} (a).  As expected, the design
corresponding to the maximum absorption efficiency at R=36~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at R=63~nm and
R=81~nm have a signature of the super absorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra} (c) is an almost flat top of the electric
dipole resonance. (TODO add some explanation, why it flat? Any ideas?
- not really, maybe there are two different dipole "types", and we see
their interference?)

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
    \caption{ Amplitude of electric field for R=36 nm (a,c) and
      ``super'' (b,d) designs in E-k  (a-b) and H-k (c-d) planes. 
      \label{fig:field}
    }%
  }
\end{figure}
%
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at R=36 nm and in a super-absorbing design with R=???? nm.
We set different scale for these two designs so that black circles
that denote outer boundary are plotted to be the same size [I am
actually not convinced that this is the best way to present it. Can
you show them in "true" scale?].  We also plot streamlines of the
Poynting vector which characterize energy flow. For the effective
design of the absorber, the power from a large cross-sectional area
flows into the particle.  In case of super-absorption regime, we
observe power flow vortices, which make absorbtion more efficient as
the electromagnetic energy propagates several times through the
absorbing materials.

% . Our initial idea was to show the same effect in absorption, and
% R=63 with R=81nm are such `superabsopting` designs. However, in 3D
% case (in contrast to 2D investigated with Ali) it turned out that
% sometimes it is preferable to use a smaller particle with single
% resonance to achieve the best efficiency. This way, in 3D case using
% real materials for a multilayer spherical particle
% ``superabsorbing'' design do not always leads to best absorption
% efficiency. Moreover, same effect exists for scattering from SiAgSi
% optimized structure. At WL=500 nm ``super'' scattering mode with two
% resonances gives the best efficiency, however, at WL=400 nm a single
% resonance small particle has a better scattering efficiency compared
% to larger particles with ``super'' design.

% \begin{acknowledgments}
%   The authors would like to thank the Ministry of Education and
%   Science of the Russian Federation (Goszadanie 2014/190, Zadanie
%   No. 3.561.2014/K, project 14.584.21.0009 10), Russian Foundation
%   for Basic Research (Grant 15-02-01344), and Government of the
%   Russian Federation (Grant 074-U01) for the financial support. The
%   simulations of cloak designs has been funded by the Russian
%   Science Foundation Grant No. 14-12-01227.% We
%   %   would also like to appreciate Alexander Krasnok for the help
%   %   with
%   %   CST simulations and Ilya V. Shadrivov for valuable comments on
%   %   the
%   %   manuscript.
% \end{acknowledgments}

In conclusion, we find the effect of the super-absorption, when the
absorption cross-section of the nanoparticle can exceed the
theoretical limit for the absorption by the highest excited mode. This
occur when several resonance modes of the structure overlap at the
same frequency. We introduce efficiency of the absorption as an
absorption cross-section divided by a geometric cross-section of the
particle, and quite unexpectedly we find that the most efficient
absorbers are smaller nanoparticles working in a single mode
regime. We present their spectral characteristics and field structure.

WE NEED TO WRITE ABOUT THIS AND SOME OTHER WORKS IN THE
INTRODUCTION. THE TOPIC IS DONE TO DEATH. It is intersting, that
similar conclusion was made by Miller et al~[TODO Fundamental Limits
to Extinction by Metallic Nanoparticles Phys. Rev. Lett. 112, 123903 –
Published 26 March 2014 O. D. Miller, C. W. Hsu, M. T. H. Reid,
W. Qiu, B. G. DeLacy, J. D. Joannopoulos, M. Soljačić, and
S. G. Johnson] for extinction of arbitrary particles.

\bibliography{2015-Ladutenko-Qabs}
\end{document}

### 2015-06-16 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya.tex
Merged most of the changes from Ilya, add of Fig1 from Ali, changed powerflow fig

@@
 
-% \author{Irina Melchakova} \author{Alexander Shalin}
-% \affiliation{ITMO University, 49 Kronverskii Ave., St.~Petersburg
-% 197101, Russian Federation\\} TODO не хватает адреса
-% \affiliation{Kotel’nikov Institute of Radio Engineering and
-% Electronics of RAS (Ulyanovsk branch),\\48 Goncharov Str., Ulyanovsk
-% 432011, Russian Federation} \affiliation{Ulyanovsk State University,
-% 42 L. Tolstoy Str., Ulyanovsk 432017, Russian Federation}
-% \author{Ilya Yagupov} \author{Pavel Belov} \affiliation{ITMO
-% University, 49 Kronverskii Ave., St.~Petersburg 197101, Russian
-% Federation\\}
+% \author{Pavel Belov} \affiliation{ITMO University, 49 Kronverskii
+% Ave., St.~Petersburg 197101, Russian Federation\\}
 \author{Ali Mirzaei} \author{Andrey Miroshnichenko} \author{Ilya
@@
 \date{\today}
-% APL 250 words! Moreover, some designs have spectral Phys Rev B less
-% then 500 words, about 5% ot total paper length
+% APL 250 words! Phys Rev B less then 500 words, about
+% 5% ot total paper length
 % emacs M-x count-words
@@
 
-Mie theory~[TODO], which is over 100 years old now, describes
+Mie theory~\cite{Mie-1908}, which is over 100 years old now, describes
 interaction of electromagnetic waves with spherical particles. Mie
-solution is still of great interest these days~[TODO], since it is one
-of the primary tools for analyzing wave scattering by spherical
-objects. Further development of the Mie theory~\cite{Yang-2003,
-  Pena-scattnlay-2009} made it possible to apply study the
-multilayered spherical particles [TODO]. Such particles have various
-applications in cancer treatment [TODO 5,6 from Ovidio draft] and
-medical diagnostics [TODO 7 from Ovidio draft],
-cloaking~\cite{Semouchkina-2013, Ladutenko-2014} and plasmonic~[TODO]
-devices, as well as for improving solar cells performance [TODO].
+solution is still of great interest these
+days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
+since it is one of the primary tools for analyzing wave scattering by
+spherical objects. Further development of the Mie
+theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
+study the multilayered spherical
+particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
+various applications in cancer treatment~\cite{Zhang-2010,
+  Hirsch-2003} and medical diagnostics~\cite{Allain-2002},
+cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
+plasmonic~\cite{Martin-2013, Alu-2005} devices, study on thermal
+properties of insulating material~\cite{Xie-2013}, as well as for
+improving solar cells performance~\cite{Kameya-2011,Mann-2011}, and so
+on.
 
 The scattering properties of multilayer cylinders and spheres was
-studied in great detail by Fan~et~al.~[Fan-PRL, Fan-APL]. In these
+studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In these
 works authors introduced the concept of a super scattering, when the
@@
 Similar fundamental limitations exist for the absorbing properties of
-sub-wavelength nanoparticles.  Tribelsky [TODO] has derived a
+sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has derived a
 theoretical limit of a maximum absorption cross-section (ACS) value
@@
 become limited by $1/4$, here $a_n$ and $b_n$ are scattering
-coefficient as defined in Mie theory [TODO Bohren Huffman]).
+coefficient as defined in Mie theory~\cite{Bohren-1983}.
 
 To overcome these limitations, we employ similar approach for
-enhancing absorption cross-section [Fan-APL]. In particular, we
+enhancing absorption cross-section~\cite{Fan-2011}. In particular, we
 propose to use the multi-layer structures, and by means of genetic
@@
 follows we describe the materials using experimentally measured
-parameters from the Ref.~[TODO].  To optimize the thickness of each
-layer we implemented~[link to GitHub] an adaptive differential
+parameters from the Ref.~\cite{palik-1997}.  To optimize the thickness of each
+layer we implemented~\cite{JADE-web} an adaptive differential
 evolution algorithm~\cite{Storn-DE-first-1997}, which is called
@@
 Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
-Scattnlay~\cite{Pena-scattnlay-2009} software, whose results were
+Scattnlay~\cite{Pena-scattnlay-2009,Scattnlay-web} software, whose results were
 verified with a number of other implementations of the Mie solutions
 and with a commercially available software such as CST Microwave
-studio.
+studio~\cite{CST-web} and Comsol Multiphysics~\cite{Comsol-web}.
 
@@
       curve exceed the theoretical limit for the second mode
-      absorption at R=63~nm and R=81~nm. (b) Mie
-coefficients for individual excited modes of the optimized structures
-[Kostya - why do they have tildas - are these not directly Mie
-coefficients?]. (c) Optimized layer thicknesses. For the total
-particle radius below 46~nm the genetic algorithm converges to the
-two-layer structure, when core size vanishes, and the optimum design
-is a bi-layer $Ag/Si$ particle.
+      absorption at R=63~nm and R=81~nm. (b) Mie absorption
+      coefficients for individual excited modes of the optimized
+      structures. (c) Optimized layer thicknesses. For the total
+      particle radius below 46~nm the optimizer converges to
+      the two-layer structure, when core size vanishes, and the
+      optimum design is a bi-layer $Ag/Si$ particle.
 
@@
 limit of a dipole ($n=1$) and a quadrupole ($n=2$)
-resonances~[Tribelsky:TODO], which are given as $$Q^{(n)}_{\rm abs\
+resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm abs\
   max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi R_{\rm
   total}/\lambda$, and $n$ is an angular momentum of the
-mode. Following Ref.~[Fan-APL], where authors introduce super
+mode. Following Ref.~\cite{Fan-2011}, where authors introduce super
 scattering for spherical particles, here we we introduce
@@
 
-In Fig.~\ref{fig:overview}b we present the values of Mie coefficients
-for individual excited modes in the structure, while horizontal dashed
-line shows the theoretical limit (1/4) for each of
+In Fig.~\ref{fig:overview}b we present the values of Mie absorption
+coefficients for individual excited modes in the structure, while
+horizontal dashed line shows the theoretical limit (1/4) for each of
 them. $\tilde{a}_{1,2}$ are electric dipole and electric quadrupole,
@@
     \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
-    \caption{Spectra of Mie coefficients of (a) efficient and (b-c)super absorption design.      
+    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)super absorption design.      
       \label{fig:spectra}
@@
 additional absorption resonances, but they are located far from the
-wavelength of interest.  A noticeable feature of
-Fig.~\ref{fig:spectra} (c) is an almost flat top of the electric
-dipole resonance. (TODO add some explanation, why it flat? Any ideas?
-- not really, maybe there are two different dipole "types", and we see
-their interference?)
+wavelength of interest.
+
+A noticeable feature of Fig.~\ref{fig:spectra} (c) is an almost flat
+top of the electric dipole resonance. (TODO add some explanation, why
+it flat? Any ideas?  - not really, maybe there are two different
+dipole "types", and we see their interference?)
 
@@
 field in Fig.~\ref{fig:field} for two designs: with the best
-efficiency at R=36 nm and in a super-absorbing design with R=???? nm.
-We set different scale for these two designs so that black circles
-that denote outer boundary are plotted to be the same size [I am
-actually not convinced that this is the best way to present it. Can
-you show them in "true" scale?].  We also plot streamlines of the
-Poynting vector which characterize energy flow. For the effective
-design of the absorber, the power from a large cross-sectional area
-flows into the particle.  In case of super-absorption regime, we
-observe power flow vortices, which make absorbtion more efficient as
-the electromagnetic energy propagates several times through the
-absorbing materials.
-
-% . Our initial idea was to show the same effect in absorption, and
-% R=63 with R=81nm are such `superabsopting` designs. However, in 3D
-% case (in contrast to 2D investigated with Ali) it turned out that
-% sometimes it is preferable to use a smaller particle with single
-% resonance to achieve the best efficiency. This way, in 3D case using
-% real materials for a multilayer spherical particle
-% ``superabsorbing'' design do not always leads to best absorption
-% efficiency. Moreover, same effect exists for scattering from SiAgSi
-% optimized structure. At WL=500 nm ``super'' scattering mode with two
-% resonances gives the best efficiency, however, at WL=400 nm a single
-% resonance small particle has a better scattering efficiency compared
-% to larger particles with ``super'' design.
-
-% \begin{acknowledgments}
-%   The authors would like to thank the Ministry of Education and
-%   Science of the Russian Federation (Goszadanie 2014/190, Zadanie
-%   No. 3.561.2014/K, project 14.584.21.0009 10), Russian Foundation
-%   for Basic Research (Grant 15-02-01344), and Government of the
-%   Russian Federation (Grant 074-U01) for the financial support. The
-%   simulations of cloak designs has been funded by the Russian
-%   Science Foundation Grant No. 14-12-01227.% We
-%   %   would also like to appreciate Alexander Krasnok for the help
-%   %   with
-%   %   CST simulations and Ilya V. Shadrivov for valuable comments on
-%   %   the
-%   %   manuscript.
-% \end{acknowledgments}
+efficiency at $R=36$~nm and in a super-absorbing design with
+$R=63$~nm.  We set different scale for these two designs so that black
+circles that denote outer boundary are plotted to be the same size.
+We also plot streamlines of the Poynting vector which characterize
+energy flow. For the effective design of the absorber, the power from
+a large cross-sectional area flows into the particle.  In case of
+super-absorption regime, we observe power flow vortices, which make
+absorbtion more efficient as the electromagnetic energy propagates
+several times through the absorbing materials.
 

### 2015-06-16 2015-Ladutenko-Qabs/data/calc-SiAgSi-Qabs.py

@@ -131,16 +131,16 @@ comment='SiAgSi-flow'
 # comment='bulk-Ag-flow'
 
 WL_units='nm'
-npts = 101
-#factor=1.9
-factor=4.5
-flow_total = 39
-#flow_total = 7
+npts = 1501
+factor=2.8
+#factor=4.5
+#flow_total = 39
+flow_total = 13
 #flow_total = 0
 #crossplane='XY'
 
 # Options to plot: Eabs, Habs, Pabs, angleEx, angleHy
-field_to_plot='Pabs'
+field_to_plot='Eabs'
 #field_to_plot='angleHy'
 import matplotlib.pyplot as plt
 fig, axs = plt.subplots(2,2)#, sharey=True, sharex=True)
@@ -152,7 +152,7 @@ design = 1 #AgSi
 x, m, WL = SetXM(design)
 print "x =", x
 print "m =", m
-fieldplot(fig, axs[0,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor, flow_total,
+fieldplot(fig, axs[0,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor*63.0/36.0, flow_total,
           subplot_label='(a)')#,is_flow_extend=False)
 
 design = 2 #AgSi
@@ -168,7 +168,7 @@ design = 1 #AgSi
 x, m, WL = SetXM(design)
 print "x =", x
 print "m =", m
-fieldplot(fig, axs[1,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor, flow_total,
+fieldplot(fig, axs[1,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor*63.0/36.0, flow_total,
           subplot_label='(c)')#,is_flow_extend=False)
 
 design = 2 #AgSi

### 2015-06-16 2015-Ladutenko-Qabs/data/fieldplot.py

@@ -271,8 +271,8 @@ def fieldplot(fig, ax, x,m, WL, comment='', WL_units=' ', crossplane='XZ', field
             min_SP = -factor*x[-1]
             step_SP = 2.0*factor*x[-1]/(flow_total-1)
             x0, y0, z0 = 0, 0, 0
-            #max_length=factor*x[-1]*10
-            max_length=factor*x[-1]*5
+            max_length=factor*x[-1]*10
+            #max_length=factor*x[-1]*5
             max_angle = np.pi/160
             if is_flow_extend:
                 rg = range(0,flow_total*2+1)

### 2015-06-16 2015-Ladutenko-Qabs/data/plot-SiAgSi-overview.py

@@ -125,7 +125,7 @@ axs[Qsca].set_ylabel(r'$Q_{abs}$', labelpad=8.8)
 axs[Qsca].set_ylim(0, 7)
 axs[Design].set_ylabel('Width, nm', labelpad=2)
 axs[Design].set_ylim(0, 75)
-axs[Design].set_xlabel(r'$R_{\rm total}$, nm', labelpad=2)
+axs[Design].set_xlabel(r'$R$, nm', labelpad=2)
 plt.xlim(0,  89)
 #plt.xlim(0,  160)
 axs[NACS].annotate('(b)', xy=(0.99, 0.985), xycoords='axes fraction', fontsize=10,

### 2015-06-19 2015-Ladutenko-Qabs/data/calc-SiAgSi-Qabs.py
update of field figure + explanation

@@ -132,6 +132,7 @@ comment='SiAgSi-flow'
 
 WL_units='nm'
 npts = 1501
+#npts = 101
 factor=2.8
 #factor=4.5
 #flow_total = 39
@@ -184,7 +185,7 @@ for aaxs in axs:
         ax.locator_params(axis='x',nbins=5)
         ax.locator_params(axis='y',nbins=5)
 
-fig.subplots_adjust(hspace=0.3, wspace=-0.3)
+fig.subplots_adjust(hspace=0.3, wspace=-0.1)
 
 plt.savefig(comment+"-R"+str(int(round(x[-1]*WL/2.0/np.pi)))+"-"+crossplane+"-"
                     +field_to_plot+".pdf",pad_inches=0.02, bbox_inches='tight')

### 2015-06-19 2015-Ladutenko-Qabs/data/fieldplot.py

@@ -203,9 +203,11 @@ def fieldplot(fig, ax, x,m, WL, comment='', WL_units=' ', crossplane='XZ', field
         scale_z = np.linspace(min(coordZ)*WL/2.0/np.pi, max(coordZ)*WL/2.0/np.pi, npts)
 
         # Define scale ticks
-        min_tick = np.amin(Eabs_data[~np.isnan(Eabs_data)])
-        max_tick = np.amax(Eabs_data[~np.isnan(Eabs_data)])
-        scale_ticks = np.linspace(min_tick, max_tick, 6)
+        #min_tick = np.amin(Eabs_data[~np.isnan(Eabs_data)])
+        min_tick = 0
+        #max_tick = np.amax(Eabs_data[~np.isnan(Eabs_data)])
+        max_tick = 8
+        scale_ticks = np.linspace(min_tick, max_tick, 5)
 
         # Interpolation can be 'nearest', 'bilinear' or 'bicubic'
         #ax.set_title(label)
@@ -224,9 +226,9 @@ def fieldplot(fig, ax, x,m, WL, comment='', WL_units=' ', crossplane='XZ', field
                         )
         ax.axis("image")
 
-        # # Add colorbar
-        # cbar = fig.colorbar(cax, ticks = [a for a in scale_ticks], ax=ax)
-        # cbar.ax.set_yticklabels(['%4.2f' % (a) for a in scale_ticks]) # vertically oriented colorbar
+        # Add colorbar
+        cbar = fig.colorbar(cax, ticks = [a for a in scale_ticks], ax=ax)
+        cbar.ax.set_yticklabels(['%1.0f' % (a) for a in scale_ticks]) # vertically oriented colorbar
         # pos = list(cbar.ax.get_position().bounds)
         #fig.text(pos[0] - 0.02, 0.925, '|E|/|E$_0$|', fontsize = 14)
         lp2 = -10.0
@@ -306,7 +308,7 @@ def fieldplot(fig, ax, x,m, WL, comment='', WL_units=' ', crossplane='XZ', field
                 codes[0] = Path.MOVETO
                 path = Path(verts, codes)
                 #patch = patches.PathPatch(path, facecolor='none', lw=0.2, edgecolor='white',zorder = 2.7)
-                patch = patches.PathPatch(path, facecolor='none', lw=0.7, edgecolor='white',zorder = 1.9)
[…]

### 2015-07-06 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-aem.tex
Changes from Andrey

--- 2015-06-16 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya.tex
@@
 
-\title{Super absorption and efficient absorption of light by spherical
-  nanoparticles}
+\title{Super vs fficient absorption of light by spherical nanoparticles}
 
@@
 \begin{abstract}
-  Spherical subwavelength nanoparticles have a fundamental limit as to
+  Nanoparticles have a fundamental limit as to
   how much light they can absorb. This limit is based on the
-  assumption that only one mode is excited in the nanoparticle. Using
-  genetic algorithm, we design multi-layer nanoparticles, in which we
-  can make several resonant modes overlap at the same frequency, thus
-  significantly beating the theoretical limit of absorption, and we
-  call this super-absorption. We further introduce the efficiency of
-  the absorption for a nanoparticle, which is absorption normalized by
+  finite number of modes excited inside the nanoparticle at a given wavelength and maximal absorption capacity per mode.
+Thus, the enhanced absorption can be achieved when each mode supported by the nanopartice absorbs light up to the maximal capacity.
+Using genetic algorithm, we design multi-layer nanoparticles, in which we
+  can make several resonant modes overlap at the same frequency resulting in {\it super-absorption}. 
+  We further introduce the {\it efficiency of
+  the absorption} for a nanoparticle, which is absorption normalized by
   the physical size of the particle, and show that efficient absorbers
@@
 interaction of electromagnetic waves with spherical particles. Mie
-solution is still of great interest these
-days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
+solution is still of great current interest~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
 since it is one of the primary tools for analyzing wave scattering by
@@
 studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In these
-works authors introduced the concept of a super scattering, when the
+works authors introduced the concept of a super-scattering, when the
 scattering cross-section of a multilayer particle exceeds that of a
@@
 propose to use the multi-layer structures, and by means of genetic
-algorithm we optimize the ACS of these particles. We analyze the
+algorithm we optimize the ACS of such nanoparticles. We analyze the
 absorption cross-section of these particles, and present the
@@
 
-It is obvious that in general, a bigger particle will have a bigger
+It is a common understanding, that, in general, a bigger particle will have a bigger
 absorption cross-section, so sphere with the diameter of 1 cm will
-absorb more light than any sphere at the nanoscale. Therefore, we use
-absorption efficiency $Q_{\rm abs}=C_{\rm abs}/2\pi R_{\rm total}^2$,
+absorb more light than any nanoscale sphere at a give wavelength. Therefore, it is practical  to employ
+the absorption efficiency $Q_{\rm abs}=C_{\rm abs}/2\pi R_{\rm total}^2$,
 where $R_{\rm total}$ is the outer radius of the particle and $C_{\rm
   abs}$ is the absorption cross-section. We maximize absorption
-efficiency at a fixed wavelength of incident light (we have chosen
+efficiency at a fixed wavelength of the incident light (we have chosen
 $\lambda=500$~nm).
@@
   total}/\lambda$, and $n$ is an angular momentum of the
-mode. Following Ref.~\cite{Fan-2011}, where authors introduce super
-scattering for spherical particles, here we we introduce
-super-absorption, when the ACS is larger than the theoretical limit
-for absorption by the mode with highest excited angular momentum
-$n$. In our parameter space we have just modes up to the quadrupole
+mode. Following Ref.~\cite{Fan-2011}, where authors introduced a super
+scattering for spherical particles, here we introduce
+super-absorption. In our parameter space we have just modes up to the quadrupole
 excited ($n=2$), and in order to get a super-absorption our efficiency
@@
 vanishes, and the particle reduces to $Ag/Si$ core-shell structure.
-At $R_{\rm total}=46$ dipole channel becomes practically
-undistinguishable from the theoretical limit (it becomes
+At $R_{\rm total}=46$ dipole channel reaches its theoretical limit (it becomes
 $\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
@@
 %
-To study spectral properties of the structures with large ACS which we
+To study spectral properties of the structures with large ACS, which we
 obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
@@
 super-absorption regime, we observe power flow vortices, which make
-absorbtion more efficient as the electromagnetic energy propagates
+absorption more efficient as the electromagnetic energy propagates
 several times through the absorbing materials.
@@
 In conclusion, we find the effect of the super-absorption, when the
-absorption cross-section of the nanoparticle can exceed the
-theoretical limit for the absorption by the highest excited mode. This
-occur when several resonance modes of the structure overlap at the
-same frequency. We introduce efficiency of the absorption as an
-absorption cross-section divided by a geometric cross-section of the
-particle, and quite unexpectedly we find that the most efficient
-absorbers are smaller nanoparticles working in a single mode
+absorption cross-section of the nanoparticle can reach the
+theoretical limit for several modes at once, corresponding to  the super-absorption condition. Such situation realized when  several resonant modes of the structure overlap at the
+same frequency. Moreover, quite unexpectedly we find that the most efficient
+absorbers, which are characterized by enhanced absorption efficiencies, are smaller nanoparticles working in a single mode
 regime. We present their spectral characteristics and field structure.

### 2015-07-06 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-aem.tex
merge of Andrey changes

@@
 
-\title{Super vs fficient absorption of light by spherical nanoparticles}
+\title{Super vs fficient absorption of light by spherical
+  nanoparticles}
 
@@
 \begin{abstract}
-  Nanoparticles have a fundamental limit as to
-  how much light they can absorb. This limit is based on the
-  finite number of modes excited inside the nanoparticle at a given wavelength and maximal absorption capacity per mode.
-Thus, the enhanced absorption can be achieved when each mode supported by the nanopartice absorbs light up to the maximal capacity.
-Using genetic algorithm, we design multi-layer nanoparticles, in which we
-  can make several resonant modes overlap at the same frequency resulting in {\it super-absorption}. 
-  We further introduce the {\it efficiency of
-  the absorption} for a nanoparticle, which is absorption normalized by
-  the physical size of the particle, and show that efficient absorbers
-  are not always operating in super-absorbing regime.
+  Nanoparticles have a fundamental limit as to how much light they can
+  absorb. This limit is based on the finite number of modes excited
+  inside the nanoparticle at a given wavelength and maximal absorption
+  capacity per mode. Thus, the enhanced absorption can be achieved
+  when each mode supported by the nanopartice absorbs light up to the
+  maximal capacity. Using stochastic optimization algorithm, we design
+  multi-layer nanoparticles, in which we can make several resonant
+  modes overlap at the same frequency resulting in {\it
+    super-absorption}.  We further introduce the {\it efficiency of
+    the absorption} for a nanoparticle, which is absorption normalized
+  by the physical size of the particle, and show that efficient
+  absorbers are not always operating in super-absorbing regime.
 \end{abstract}
@@
 interaction of electromagnetic waves with spherical particles. Mie
-solution is still of great current interest~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
+solution is still of great current
+interest~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
 since it is one of the primary tools for analyzing wave scattering by
@@
 various applications in cancer treatment~\cite{Zhang-2010,
-  Hirsch-2003} and medical diagnostics~\cite{Allain-2002},
+  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
 cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
@@
 The scattering properties of multilayer cylinders and spheres was
-studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In these
-works authors introduced the concept of a super-scattering, when the
-scattering cross-section of a multilayer particle exceeds that of a
-homogeneous particle of the same size in the so-called single-channel
-limit. The super scattering appears when we design a multilayer
-structure so that several modes become nearly degenerate, i.e. their
-resonance frequencies coincide or get close to each other. In a
-homogeneous particle, the resonances appear at different frequencies,
-and there is no design freedom for a fixed geometry of the structure
-to make these resonances overlap, and this limits the achievable
-scattering cross-section.
+studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In
+these works authors introduced the concept of a super-scattering, when
+the scattering cross-section of a multilayer particle exceeds that of
+a homogeneous particle of the same size in the so-called
+single-channel limit. The super-scattering appears when we design a
+multilayer structure so that several modes become nearly degenerate,
+i.e. their resonance frequencies coincide or get close to each
+other. In a homogeneous particle, the resonances appear at different
+frequencies, and there is no design freedom for a fixed geometry of
+the structure to make these resonances overlap, and this limits the
+achievable scattering cross-section.
 
 Similar fundamental limitations exist for the absorbing properties of
-sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has derived a
-theoretical limit of a maximum absorption cross-section (ACS) value
-for a single channel, i.e., when only one mode of the sphere is
-excited.  As a result the absorption coefficients $\tilde{a}_n= {\rm
-  Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} - |b_n|^2 $
-become limited by $1/4$, here $a_n$ and $b_n$ are scattering
-coefficient as defined in Mie theory~\cite{Bohren-1983}.
+sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
+derived a theoretical limit of a maximum absorption cross-section
+(ACS) value for a single channel, i.e., when only one mode of the
+sphere is excited.  As a result the absorption coefficients
+$\tilde{a}_n= {\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm
+  Re}\{b_n\} - |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$
+are scattering coefficient as defined in Mie
+theory~\cite{Bohren-1983}.
 
@@
 follows we describe the materials using experimentally measured
-parameters from the Ref.~\cite{palik-1997}.  To optimize the thickness of each
-layer we implemented~\cite{JADE-web} an adaptive differential
+parameters from the Ref.~\cite{palik-1997}.  To optimize the thickness
+of each layer we implemented~\cite{JADE-web} an adaptive differential
 evolution algorithm~\cite{Storn-DE-first-1997}, which is called
@@
 Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
-Scattnlay~\cite{Pena-scattnlay-2009,Scattnlay-web} software, whose results were
-verified with a number of other implementations of the Mie solutions
-and with a commercially available software such as CST Microwave
-studio~\cite{CST-web} and Comsol Multiphysics~\cite{Comsol-web}.
+Scattnlay~\cite{Pena-scattnlay-2009,Scattnlay-web} software, whose
+results were verified with a number of other implementations of the
+Mie solutions and with a commercially available software such as CST
+Microwave studio~\cite{CST-web} and Comsol
+Multiphysics~\cite{Comsol-web}.
 
-It is a common understanding, that, in general, a bigger particle will have a bigger
-absorption cross-section, so sphere with the diameter of 1 cm will
-absorb more light than any nanoscale sphere at a give wavelength. Therefore, it is practical  to employ
-the absorption efficiency $Q_{\rm abs}=C_{\rm abs}/2\pi R_{\rm total}^2$,
-where $R_{\rm total}$ is the outer radius of the particle and $C_{\rm
-  abs}$ is the absorption cross-section. We maximize absorption
-efficiency at a fixed wavelength of the incident light (we have chosen
+It is a common understanding, that, in general, a bigger particle will
+have a bigger absorption cross-section, so sphere with the diameter of
+1 cm will absorb more light than any nanoscale sphere at a give
+wavelength. Therefore, it is practical to employ the absorption
+efficiency $Q_{\rm abs}=C_{\rm abs}/2\pi R_{\rm total}^2$, where
+$R_{\rm total}$ is the outer radius of the particle and $C_{\rm abs}$
+is the absorption cross-section. We maximize absorption efficiency at
+a fixed wavelength of the incident light (we have chosen
 $\lambda=500$~nm).
@@
       curve exceed the theoretical limit for the second mode
-      absorption at R=63~nm and R=81~nm. (b) Mie absorption
+      absorption at $R=63$~nm and $R=81$~nm. TODO add arrows to mark
+      local maxima on the plot (b) Mie absorption
       coefficients for individual excited modes of the optimized
@@
       optimum design is a bi-layer $Ag/Si$ particle. 
-
       \label{fig:overview}
@@
 limit of a dipole ($n=1$) and a quadrupole ($n=2$)
-resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm abs\
-  max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi R_{\rm
-  total}/\lambda$, and $n$ is an angular momentum of the
+resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm
+  abs\ max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi
+R_{\rm total}/\lambda$, and $n$ is an angular momentum of the
 mode. Following Ref.~\cite{Fan-2011}, where authors introduced a super
 scattering for spherical particles, here we introduce
-super-absorption. In our parameter space we have just modes up to the quadrupole
-excited ($n=2$), and in order to get a super-absorption our efficiency
-should be higher than that of a quadrupole. We clearly see this
-super-absorption at $R_{\rm total}>60$~nm, in Fig.~\ref{fig:overview}
-(a).
+super-absorption. In our parameter space we have just modes up to the
+quadrupole excited ($n=2$), and in order to get a super-absorption our
+efficiency should be higher than that of a quadrupole. We clearly see
+this super-absorption at $R_{\rm total}>60$~nm, in
+Fig.~\ref{fig:overview} (a).
 
@@
 vanishes, and the particle reduces to $Ag/Si$ core-shell structure.
-At $R_{\rm total}=46$ dipole channel reaches its theoretical limit (it becomes
-$\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
-inner $Si$ layer in order to keep $\tilde{a}_1$ near the theoretical
-limit as the $R_{\rm total}$ increases.  As a side effect, the
-quadrupole contribution $\tilde{a}_2$ appears, however, it does not
-help to reach super-absorption limit $n=2$.
+At $R_{\rm total}=46$ dipole channel reaches its theoretical limit (it
+becomes $\tilde{a}_1>0.249$).  It appears that the optimizer
+introduced the inner $Si$ layer in order to keep $\tilde{a}_1$ near
+the theoretical limit as the $R_{\rm total}$ increases.  As a side
+effect, the quadrupole contribution $\tilde{a}_2$ appears, however, it
+does not help to reach super-absorption limit $n=2$.
 
@@
 %
-To study spectral properties of the structures with large ACS, which we
-obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
-different cases for designs that correspond to local maxima of $Q_{\rm
-  abs}$ shown in Fig.~\ref{fig:overview} (a).  As expected, the design
-corresponding to the maximum absorption efficiency at R=36~nm has a
-single electric dipole resonance centered at the target wavelength
-$\lambda=500$~nm. Spectra of designs with maxima at R=63~nm and
-R=81~nm have a signature of the super absorption, i.e. there is an
+To study spectral properties of the structures with large ACS, which
+we obtained by the optimization, in Fig.~\ref{fig:spectra} we plot
+three different cases for designs that correspond to local maxima of
+$Q_{\rm abs}$ shown in Fig.~\ref{fig:overview} (a).  As expected, the
+design corresponding to the maximum absorption efficiency at R=36~nm
+has a single electric dipole resonance centered at the target
+wavelength $\lambda=500$~nm. Spectra of designs with maxima at R=63~nm
+and R=81~nm have a signature of the super absorption, i.e. there is an
 overlap of several resonances.  We note that these structures have
@@
 In conclusion, we find the effect of the super-absorption, when the
-absorption cross-section of the nanoparticle can reach the
-theoretical limit for several modes at once, corresponding to  the super-absorption condition. Such situation realized when  several resonant modes of the structure overlap at the
-same frequency. Moreover, quite unexpectedly we find that the most efficient
-absorbers, which are characterized by enhanced absorption efficiencies, are smaller nanoparticles working in a single mode
-regime. We present their spectral characteristics and field structure.
+absorption cross-section of the nanoparticle can reach the theoretical
+limit for several modes at once, corresponding to the super-absorption
+condition. Such situation realized when several resonant modes of the
+structure overlap at the same frequency. Moreover, quite unexpectedly
+we find that the most efficient absorbers, which are characterized by
+enhanced absorption efficiencies, are smaller nanoparticles working in
+a single mode regime. We present their spectral characteristics and
+field structure.
 

### 2015-07-06 2015-Ladutenko-Qabs/data/plot-SiAgSi-overview.py

@@ -101,6 +101,9 @@ axs[Qsca].text(55, 1.2, r'max($n=1$)', fontsize=10, color='red')
 axs[Qsca].text(55, 5.9, r'max($n=2$)', fontsize=10, color='blue')
 #lg=axs[Qsca].legend(loc='upper right',prop={'size':8})
 lg.draw_frame(False)
+axs[Qsca].arrow(36, 4.5, 0, 0.6, head_width=1.2, head_length=0.3, fc='k', ec='k')
+axs[Qsca].arrow(62.6, 3.35, 0, 0.6, head_width=1.2, head_length=0.3, fc='k', ec='k')
+axs[Qsca].arrow(81.4, 4.3, 0, -0.6, head_width=1.2, head_length=0.3, fc='k', ec='k')
 
 cax = axs[Design].plot(data_spaced[:,0], data_spaced[:,2], linewidth=plotwidth/1.5,
                        solid_joinstyle='round', solid_capstyle='round', color='red'

### 2015-07-13 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-aem.tex
Fig 3 is now recalculated

@@
 small particles.
+
+Another approach for an ideal absorber was given in a recent work by
+Grigoriev et al.~\cite{Grigoriev-2015}. However, they considered only
+a dipole approximation, the final value for our range of particle
+sizes is very close to the dipole limit predicted with
+Tribelsky~\cite{Tribelsky-2011}.  Thus, such super-absorption designs
+correspond to single mode limit.  At the same time, Grigoriev et
+al.~\cite{Grigoriev-2015} also provide an equation to design a
+core-shell structure from predefined materials. However, in case of
+$Si$ and $Ag$ materials and size parameter from our best design, their
+equation gives a complex value for core material filling factor, which
+is not practical for any experimental realisations.
+
+\begin{figure}
+  \center{
+    % Use pdfcrop to remove white margins
+    \includegraphics[width=0.4\textwidth]{fig/Fig1}%
+    \caption{ Shematic view of the simulated $Si/Ag/Si$ particle. 
+      \label{fig:geom}
+    }%
+  }
+\end{figure}
 
@@
 
-A noticeable feature of Fig.~\ref{fig:spectra} (c) is an almost flat
-top of the electric dipole resonance. (TODO add some explanation, why
-it flat? Any ideas?  - not really, maybe there are two different
-dipole "types", and we see their interference?)
+A noticeable feature of Fig.~\ref{fig:spectra}~(c) is an almost flat
+top of the electric dipole resonance.
+% maybe there are two different dipole "types", and we see their
+% interference?
+To answer this question we need to look at the internal coefficients of each layer.
+There is no interference between multipoles - they are orthogonal modes ;-)
+ Whereas resonant responses
+of other designs originate from coupling of incident plane wave with
+the corresponding multipole, it is not the case for the design with
+$R=81$~nm. Here, the particle is mostly composed from the $Si$ outer
+shell, that give enough volume for $\tilde{b}_2$.  Dipole response
+comes from the small inner part of the sphere and can not be directly
+excited with the incident wave.  It takes the power from the
+surrounding $\tilde{b}_2$ mode and very soon it reaches the
+fundamental limit for absorption.  This way, we can observe a flat top
+for the $\tilde{a}_1$ response accompanied with a significant value of
+$\tilde{b}_2$.  Our suggestion is indirectly proved by the reduced
+width of the $\tilde{b}_2$ resonance compared to other quadrupole
+responses.
 
@@
 a large cross-sectional area flows into the particle.  In case of
-super-absorption regime, we observe power flow vortices, which make
+super-absorption regime, we observe the formation of vortices in the power flow, which make
 absorption more efficient as the electromagnetic energy propagates
-several times through the absorbing materials.
+several times through the absorbing materials.  The reason for the
+smaller overall absorption efficiency of a super-design is obvious:
+spatial distribution of the electric field is not uniform inside the
+particle and the share of the volume with high absorption rate in the
+vortices do not compensate low absorption efficiency in the regions
+with small electric field ( absorbed power is expressed as $P_{\rm
+  abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)
 

### 2015-07-13 2015-Ladutenko-Qabs/data/calc-SiAgSi-Qabs.py

@@ -4,8 +4,6 @@
 #    Copyright (C) 2009-2015 Ovidio Peña Rodríguez <ovidio@bytesfall.com>
 #    Copyright (C) 2013-2015  Konstantin Ladutenko <kostyfisik@gmail.com>
 #
-#    This file is part of python-scattnlay
-#
 #    This program is free software: you can redistribute it and/or modify
 #    it under the terms of the GNU General Public License as published by
 #    the Free Software Foundation, either version 3 of the License, or

### 2015-07-13 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py

@@ -1,0 +1,340 @@
+#!/usr/bin/env python
+# -*- coding: UTF-8 -*-
+#
+#    Copyright (C) 2009-2015 Ovidio Peña Rodríguez <ovidio@bytesfall.com>
+#    Copyright (C) 2013-2015  Konstantin Ladutenko <kostyfisik@gmail.com>
+#
+#    This program is free software: you can redistribute it and/or modify
+#    it under the terms of the GNU General Public License as published by
+#    the Free Software Foundation, either version 3 of the License, or
+#    (at your option) any later version.
+#
+#    This program is distributed in the hope that it will be useful,
+#    but WITHOUT ANY WARRANTY; without even the implied warranty of
+#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#    GNU General Public License for more details.
+#
+#    The only additional remark is that we expect that all publications
+#    describing work using this software, or all commercial products
+#    using it, cite the following reference:
+#    [1] O. Pena and U. Pal, "Scattering of electromagnetic radiation by
+#        a multilayered sphere," Computer Physics Communications,
+#        vol. 180, Nov. 2009, pp. 2348-2354.
+#
+#    You should have received a copy of the GNU General Public License
+#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+import numpy as np
+import matplotlib.pyplot as plt
+from scattnlay import scattnlay
+from scattnlay import scattcoeffs
+###############################################################################
+def SetXM(design, extra_width = 0, WL=0, epsilon_Si=0, epsilon_Ag=0):
+    """ design value:
+    1: AgSi - a1
+    2: SiAgSi - a1, b1
+    3: SiAgSi - a1, b2
+    """
+    if WL == 0:
+        epsilon_Si = 18.4631066585 + 0.6259727805j
+        epsilon_Ag = -8.5014154589 + 0.7585845411j
+
+    index_Si = np.sqrt(epsilon_Si)
+    index_Ag = np.sqrt(epsilon_Ag)
+    isSiAgSi=True
+    isBulk = False
+    if design==1:
+        #36	5.62055	0	31.93	4.06	49	5.62055	500
+        isSiAgSi=False
[…]

### 2015-07-13 2015-Ladutenko-Qabs/data/fieldplot.py

@@ -39,6 +39,7 @@ def unit_vector(vector):
     """ Returns the unit vector of the vector.  """
     return vector / np.linalg.norm(vector)
 
+
 def angle_between(v1, v2):
     """ Returns the angle in radians between vectors 'v1' and 'v2'::
 
@@ -59,66 +60,70 @@ def angle_between(v1, v2):
             return np.pi
     return angle
 ###############################################################################
+
+
 def GetFlow3D(x0, y0, z0, max_length, max_angle, x, m, pl):
     # Initial position
     flow_x = [x0]
     flow_y = [y0]
     flow_z = [z0]
-    max_step = x[-1]/3
-    min_step = x[0]/2000
+    max_step = x[-1] / 3
+    min_step = x[0] / 2000
 #    max_step = min_step
-    step = min_step*2.0
+    step = min_step * 2.0
     if max_step < min_step:
         max_step = min_step
     coord = np.vstack(([flow_x[-1]], [flow_y[-1]], [flow_z[-1]])).transpose()
-    terms, E, H = fieldnlay(np.array([x]), np.array([m]), coord,pl=pl)
+    terms, E, H = fieldnlay(np.array([x]), np.array([m]), coord, pl=pl)
     Ec, Hc = E[0, 0, :], H[0, 0, :]
     S = np.cross(Ec, Hc.conjugate()).real
-    Snorm_prev = S/np.linalg.norm(S)
+    Snorm_prev = S / np.linalg.norm(S)
     Sprev = S
     length = 0
     dpos = step
     count = 0
     while length < max_length:
         count = count + 1
-        if (count>4000): # Limit length of the absorbed power streamlines
+        if (count > 4000):  # Limit length of the absorbed power streamlines
             break
-        if step<max_step:
-                step = step*2.0
+        if step < max_step:
+            step = step * 2.0
         r = np.sqrt(flow_x[-1]**2 + flow_y[-1]**2 + flow_z[-1]**2)
         while step > min_step:
-            #Evaluate displacement from previous poynting vector
+            # Evaluate displacement from previous poynting vector
             dpos = step
-            dx = dpos*Snorm_prev[0];
-            dy = dpos*Snorm_prev[1];
-            dz = dpos*Snorm_prev[2];
[…]

### 2015-07-13 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py
After Ilya changes

@@ -130,6 +130,9 @@ def GetEpsilon(WLs, fname):
     from scipy.interpolate import interp1d
     fRe = interp1d(WL, epsRe)
     fIm = interp1d(WL, epsIm)
+    # fRe = interp1d(WL, epsRe, kind=2)
+    # fIm = interp1d(WL, epsIm, kind=2)
+
     data = np.vstack((WLs, fRe(WLs)+fIm(WLs)*1j))
     # data = np.concatenate(WLs, np.array(fRe(WLs)))
     # data = np.concatenate(WLs, )
@@ -173,168 +176,172 @@ design = 1 #AgSi
 # epsilon_Ag = -8.5014154589 + 0.7585845411j
 # WL = 500
 from_WL = 400
-to_WL = 600
-total_points = 100
-extra_width = 5
+to_WL = 800
+total_points = 600
+for i in xrange(100):
+    extra_width = i-2
+    fname = "Ag-Si-channels-TotalR036-calc.dat"
+    design = 1 #AgSi
+    save_spectra(fname, from_WL, to_WL, total_points, design, extra_width)
+    data, data_spaced = load_data(fname)
 
-fname = "Ag-Si-channels-TotalR036-calc.dat"
-design = 1 #AgSi
-save_spectra(fname, from_WL, to_WL, total_points, design, extra_width)
-data, data_spaced = load_data(fname)
+    fname2 = "Si-Ag-Si-channels-TotalR063-calc.dat"
+    design = 2
+    save_spectra(fname2, from_WL, to_WL, total_points, design, extra_width)
+    data2, data_spaced2 = load_data(fname2)
+    data_spaced2 = data2
 
-fname2 = "Si-Ag-Si-channels-TotalR063-calc.dat"
-design = 2
-save_spectra(fname2, from_WL, to_WL, total_points, design, extra_width)
-data2, data_spaced2 = load_data(fname2)
-data_spaced2 = data2
+    fname3 = "Si-Ag-Si-channels-TotalR081-calc.dat"
+    design = 3
+    save_spectra(fname3, from_WL, to_WL, total_points, design, extra_width)
+    data3, data_spaced3 = load_data(fname3)
+    data_spaced3 = data3
 
-fname3 = "Si-Ag-Si-channels-TotalR081-calc.dat"
-design = 3
-save_spectra(fname3, from_WL, to_WL, total_points, design, extra_width)
-data3, data_spaced3 = load_data(fname3)
-data_spaced3 = data3
+    isAll = False
+    isAll = True
[…]

### 2015-07-16 2015-Ladutenko-Qabs/data/report-with-figures.tex
layered plot

%%\documentclass[fullscreen=true, handout]{beamer}
\documentclass[fullscreen=true]{beamer}
\usetheme[secheader]{Boadilla}
%%\usetheme{Boadilla}
%%\usetheme[height=7mm]{Rochester} 
%%\useinnertheme{rounded}
 \usecolortheme{seahorse}
%% \usecolortheme{whale}
%% \usecolortheme{rose}
%%\setbeamertemplate{navigation symbols}{\insertframenavigationsymbol}
%% or
\beamertemplatenavigationsymbolsempty
%% \setbeamertemplate[info line]{footline} %%Не работает
%% {\quad\strut\insertsection
%% \hfill\insertframenumber/\inserttotalframenumber\strut\quad} 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} %%apt-get install cm-super
%%\usepackage[english, russian]{babel}
\usepackage[english]{babel}
\emergencystretch=35pt %%Чтобы нe было строчек, вылезших на поля
\usepackage{ragged2e} %% to use \justifying
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{listings}
%% \lstset{language=C++,
%%   backgroundcolor=\color{Black},
%%    basicstyle=\color{White}\tiny\ttfamily,
%%    keywordstyle=\color{Orange},
%%    identifierstyle=\color{Cyan},
%%    stringstyle=\color{Red}, 
%%    commentstyle=\color{Green},  
%%    breaklines=true,
%%    breakatwhitespace=true,
%%    tabsize=10,
%%    showstringspaces=false%%
%% }
%%or better
\lstset{breakatwhitespace,
language=C++,
columns=fullflexible,
keepspaces,
breaklines,
tabsize=2,
backgroundcolor=\color{white},
basicstyle=\color{black}\small\ttfamily,
keywordstyle=\color{orange},
identifierstyle=\color{blue},
stringstyle=\color{red}, 
commentstyle=\color{green},  
showstringspaces=false,
extendedchars=true}
\newcommand{\transhi}{40} %% Переменная - хорошая прозрачность
\setbeamercovered{transparent = \transhi} 
\setbeamertemplate{caption}[numbered]
\begin{document}
%% ----------------------------------------------------------------
\title{Report \today}
%% ----------------------------------------------------------------
\section{Figures}
\begin{frame}{Legend} %%Добавить интриги
  \begin{block}{}
    \begin{enumerate}
    \item blue - dipole
    \item red  - qudrupole
    \item green - octupole      
    \end{enumerate}
  \end{block}
  \begin{block}{}
    \begin{enumerate}
    \item solid - electric
    \item dashed  - magnetic
    \end{enumerate}
  \end{block}
  \begin{block}{}
    \begin{enumerate}
    \item thin - inner (core) layer
    \item thicker - middle layer
    \item thick - outher layer      
    \end{enumerate}
  \end{block}
All curves are normalized to it`s maxima! As maxima goes out ot the
plotted range normalization changes!!!
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+00.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+00.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+00.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+01.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+01.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+01.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+02.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+02.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+02.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+03.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+03.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+03.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+04.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+04.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+04.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+05.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+05.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+05.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+06.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+06.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+06.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+07.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+07.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+07.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+08.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+08.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+08.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+09.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+09.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+09.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+10.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+10.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+10.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+11.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+11.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+11.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+12.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+12.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+12.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+13.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+13.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+13.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+14.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+14.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+14.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+15.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+15.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+15.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+16.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+16.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+16.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+17.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+17.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+17.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+18.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+18.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+18.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+19.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+19.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+19.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+20.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+20.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+20.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+21.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+21.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+21.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+22.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+22.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+22.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+23.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+23.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+23.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+24.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+24.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+24.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+25.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+25.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+25.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+26.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+26.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+26.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+27.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+27.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+27.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+28.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+28.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+28.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+29.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+29.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+29.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+30.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+30.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+30.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+31.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+31.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+31.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+32.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+32.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+32.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+33.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+33.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+33.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+34.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+34.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+34.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+35.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+35.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+35.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+36.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+36.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+36.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+37.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+37.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+37.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+38.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+38.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+38.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+39.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+39.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+39.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+40.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+40.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+40.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+41.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+41.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+41.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+42.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+42.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+42.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+43.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+43.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+43.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+44.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+44.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+44.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+45.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+45.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+45.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+46.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+46.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+46.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+47.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+47.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+47.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+48.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+48.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+48.pdf}
  \end{figure}
\end{frame}

\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+49.pdf}
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+49.pdf}%
    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+49.pdf}
  \end{figure}
\end{frame}
\end{document}

### 2015-07-16 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py

@@ -25,6 +25,7 @@
 #    along with this program.  If not, see <http://www.gnu.org/licenses/>.
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib.ticker as tkr
 from scattnlay import scattnlay
 from scattnlay import scattcoeffs
 ###############################################################################
@@ -140,8 +141,8 @@ def GetEpsilon(WLs, fname):
 ###############################################################################
 def save_spectra(fname, from_WL, to_WL, total_points, design, extra_width):
     WLs = np.linspace(from_WL, to_WL, total_points)
-    epsSi = GetEpsilon(WLs, "Si.txt")
-    epsAg = GetEpsilon(WLs, "Ag.txt")
+    epsSi = GetEpsilon(WLs, "Si-int.txt")
+    epsAg = GetEpsilon(WLs, "Ag-int.txt")
     data = calc(design, extra_width, WLs[0], epsSi[0,1], epsAg[0,1])
     for i in xrange(len(WLs)):
         data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi[i,1], epsAg[i,1])))
@@ -176,10 +177,10 @@ design = 1 #AgSi
 # epsilon_Ag = -8.5014154589 + 0.7585845411j
 # WL = 500
 from_WL = 400
-to_WL = 800
+to_WL = 600
 total_points = 600
-for i in xrange(100):
-    extra_width = i-2
+for i in xrange(1):
+    extra_width = 0
     fname = "Ag-Si-channels-TotalR036-calc.dat"
     design = 1 #AgSi
     save_spectra(fname, from_WL, to_WL, total_points, design, extra_width)
@@ -197,6 +198,11 @@ for i in xrange(100):
     data3, data_spaced3 = load_data(fname3)
     data_spaced3 = data3
 
+    # design = 3
+    fname4 = "absorb-layered-spectra-d0.dat"
+    data4, data_spaced4 = load_data(fname4)
+
+
     isAll = False
     isAll = True
     ############################# Plotting ######################
@@ -205,12 +211,13 @@ for i in xrange(100):
     mvals = ma.masked_where(np.nan in data_spaced, vals)
 
     if isAll:
[…]

### 2015-07-16 2015-Ladutenko-Qabs/data/plot-SiAgSi-overview.py

@@ -105,18 +105,18 @@ axs[Qsca].arrow(36, 4.5, 0, 0.6, head_width=1.2, head_length=0.3, fc='k', ec='k'
 axs[Qsca].arrow(62.6, 3.35, 0, 0.6, head_width=1.2, head_length=0.3, fc='k', ec='k')
 axs[Qsca].arrow(81.4, 4.3, 0, -0.6, head_width=1.2, head_length=0.3, fc='k', ec='k')
 
-cax = axs[Design].plot(data_spaced[:,0], data_spaced[:,2], linewidth=plotwidth/1.5,
-                       solid_joinstyle='round', solid_capstyle='round', color='red'
-                       , label="core"
-                       )
 
+cax = axs[Design].plot(data_spaced[:,0], data_spaced[:,4], linewidth=plotwidth,
+                       solid_joinstyle='round', solid_capstyle='round', color='black'
+                       , label="outer shell"
+                       )
 cax = axs[Design].plot(data_spaced[:,0], data_spaced[:,3], linewidth=plotwidth,
                        solid_joinstyle='round', solid_capstyle='round', color='green'
                        , label="inner shell"
                        )
-cax = axs[Design].plot(data_spaced[:,0], data_spaced[:,4], linewidth=plotwidth,
-                       solid_joinstyle='round', solid_capstyle='round', color='black'
-                       , label="outer shell"
+cax = axs[Design].plot(data_spaced[:,0], data_spaced[:,2], linewidth=plotwidth/1.5,
+                       solid_joinstyle='round', solid_capstyle='round', color='red'
+                       , label="core"
                        )
 lg=axs[Design].legend(loc='upper left',prop={'size':10})
 lg.draw_frame(False)

### 2015-07-16 2015-Ladutenko-Qabs/data/calc-SiAgSi-layered.py
clean up

@@ -1,0 +1,369 @@
+#!/usr/bin/env python
+# -*- coding: UTF-8 -*-
+#
+#    Copyright (C) 2009-2015 Ovidio Peña Rodríguez <ovidio@bytesfall.com>
+#    Copyright (C) 2013-2015  Konstantin Ladutenko <kostyfisik@gmail.com>
+#
+#    This program is free software: you can redistribute it and/or modify
+#    it under the terms of the GNU General Public License as published by
+#    the Free Software Foundation, either version 3 of the License, or
+#    (at your option) any later version.
+#
+#    This program is distributed in the hope that it will be useful,
+#    but WITHOUT ANY WARRANTY; without even the implied warranty of
+#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#    GNU General Public License for more details.
+#
+#    The only additional remark is that we expect that all publications
+#    describing work using this software, or all commercial products
+#    using it, cite the following reference:
+#    [1] O. Pena and U. Pal, "Scattering of electromagnetic radiation by
+#        a multilayered sphere," Computer Physics Communications,
+#        vol. 180, Nov. 2009, pp. 2348-2354.
+#
+#    You should have received a copy of the GNU General Public License
+#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+import numpy as np
+import matplotlib.pyplot as plt
+from scattnlay import scattnlay
+from scattnlay import scattcoeffs
+###############################################################################
+def SetXM(design, extra_width = 0, WL=0, epsilon_Si=0, epsilon_Ag=0):
+    """ design value:
+    1: AgSi - a1
+    2: SiAgSi - a1, b1
+    3: SiAgSi - a1, b2
+    """
+    if WL == 0:
+        epsilon_Si = 18.4631066585 + 0.6259727805j
+        epsilon_Ag = -8.5014154589 + 0.7585845411j
+
+    index_Si = np.sqrt(epsilon_Si)
+    index_Ag = np.sqrt(epsilon_Ag)
+    isSiAgSi=True
+    isBulk = False
+    if design==1:
+        #36	5.62055	0	31.93	4.06	49	5.62055	500
+        isSiAgSi=False
[…]

### 2015-07-16 2015-Ladutenko-Qabs/data/calc-SiAgSi3-field.py

@@ -1,0 +1,199 @@
+#!/usr/bin/env python
+# -*- coding: UTF-8 -*-
+#
+#    Copyright (C) 2009-2015 Ovidio Peña Rodríguez <ovidio@bytesfall.com>
+#    Copyright (C) 2013-2015  Konstantin Ladutenko <kostyfisik@gmail.com>
+#
+#    This program is free software: you can redistribute it and/or modify
+#    it under the terms of the GNU General Public License as published by
+#    the Free Software Foundation, either version 3 of the License, or
+#    (at your option) any later version.
+#
+#    This program is distributed in the hope that it will be useful,
+#    but WITHOUT ANY WARRANTY; without even the implied warranty of
+#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#    GNU General Public License for more details.
+#
+#    The only additional remark is that we expect that all publications
+#    describing work using this software, or all commercial products
+#    using it, cite the following reference:
+#    [1] O. Pena and U. Pal, "Scattering of electromagnetic radiation by
+#        a multilayered sphere," Computer Physics Communications,
+#        vol. 180, Nov. 2009, pp. 2348-2354.
+#
+#    You should have received a copy of the GNU General Public License
+#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+# This test case calculates the electric field in the 
+# E-k plane, for an spherical Si-Ag-Si nanoparticle.
+
+import scattnlay
+from scattnlay import fieldnlay
+from scattnlay import scattnlay
+import numpy as np
+import cmath
+# from fieldplot import GetFlow3D
+# from fieldplot import GetField
+from fieldplot import fieldplot
+
+###############################################################################
+def SetXM(design):
+    """ design value:
+    1: AgSi - a1
+    2: SiAgSi - a1, b1
+    3: SiAgSi - a1, b2
+    """
+    epsilon_Si = 18.4631066585 + 0.6259727805j
+    epsilon_Ag = -8.5014154589 + 0.7585845411j
[…]

### 2015-07-16 2015-Ladutenko-Qabs/data/field-Ag-flow.py

@@ -1,261 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: UTF-8 -*-
-#
-#    Copyright (C) 2009-2015 Ovidio Peña Rodríguez <ovidio@bytesfall.com>
-#    Copyright (C) 2013-2015  Konstantin Ladutenko <kostyfisik@gmail.com>
-#
-#    This file is part of python-scattnlay
-#
-#    This program is free software: you can redistribute it and/or modify
-#    it under the terms of the GNU General Public License as published by
-#    the Free Software Foundation, either version 3 of the License, or
-#    (at your option) any later version.
-#
-#    This program is distributed in the hope that it will be useful,
-#    but WITHOUT ANY WARRANTY; without even the implied warranty of
-#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-#    GNU General Public License for more details.
-#
-#    The only additional remark is that we expect that all publications
-#    describing work using this software, or all commercial products
-#    using it, cite the following reference:
-#    [1] O. Pena and U. Pal, "Scattering of electromagnetic radiation by
-#        a multilayered sphere," Computer Physics Communications,
-#        vol. 180, Nov. 2009, pp. 2348-2354.
-#
-#    You should have received a copy of the GNU General Public License
-#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
-
-# This test case calculates the electric field in the 
-# E-k plane, for an spherical Si-Ag-Si nanoparticle. Core radius is 17.74 nm,
-# inner layer 23.31nm, outer layer 22.95nm. Working wavelength is 800nm, we use
-# silicon epsilon=13.64+i0.047, silver epsilon= -28.05+i1.525
-
-import scattnlay
-from scattnlay import fieldnlay
-from scattnlay import scattnlay
-import numpy as np
-import cmath
-
-
-def get_index(array,value):
-    idx = (np.abs(array-value)).argmin()
[…]

### 2015-07-16 2015-Ladutenko-Qabs/data/calc-SiAgSi3-field.py
SiAgSi fiels plot for design 3

@@ -37,7 +37,7 @@ import cmath
 from fieldplot import fieldplot
 
 ###############################################################################
-def SetXM(design):
+def SetXM(design, WL = 0):
     """ design value:
     1: AgSi - a1
     2: SiAgSi - a1, b1
@@ -52,31 +52,36 @@ def SetXM(design):
     if design==1:
         #36	5.62055	0	31.93	4.06	49	5.62055	500
         isSiAgSi=False
-        WL=500 #nm
+        if WL == 0:
+            WL=500 #nm
         core_width = 0.0 #nm Si
         inner_width = 31.93 #nm Ag
         outer_width = 4.06 #nm  Si
     elif design==2:
         #62.5	4.48866	29.44	10.33	22.73	0	4.48866	500
-        WL=500 #nm
+        if WL == 0:
+            WL=500 #nm
         core_width = 29.44 #nm Si
         inner_width = 10.33 #nm Ag
         outer_width = 22.73 #nm  Si
     elif design == 3:
         #81.4	3.14156	5.27	8.22	67.91	0	3.14156	500
-        WL=500 #nm
+        if WL == 0:
+            WL=500 #nm
         core_width = 5.27 #nm Si
         inner_width = 8.22 #nm Ag
         outer_width = 67.91 #nm  Si
     elif design==4:
-        WL=800 #nm
+        if WL == 0:
+            WL=800 #nm
         epsilon_Si = 13.64 + 0.047j
         epsilon_Ag = -28.05 + 1.525j
         core_width = 17.74 #nm Si
         inner_width = 23.31 #nm Ag
         outer_width = 22.95 #nm  Si
     elif design==5:
-        WL=354 #nm
+        if WL == 0:
+            WL=354 #nm
         core_r = WL/20.0
         epsilon_Ag = -2.0 + 0.28j   #original
         index_Ag = np.sqrt(epsilon_Ag)
@@ -124,18 +129,18 @@ def SetXM(design):
 #design = 2
 #design = 3
 #design = 4   # WL=800
-comment='SiAgSi-flow'
+comment='SiAgSi3-flow'
 # design = 5   # Bulk Ag
 # comment='bulk-Ag-flow'
 
 WL_units='nm'
 npts = 1501
 #npts = 101
-factor=2.8
+factor=1.2
 #factor=4.5
[…]

### 2015-07-16 2015-Ladutenko-Qabs/data/fieldplot.py

@@ -215,11 +215,12 @@ def fieldplot(fig, ax, x, m, WL, comment='', WL_units=' ', crossplane='XZ',
 
         # Define scale ticks
         #min_tick = np.amin(Eabs_data[~np.isnan(Eabs_data)])
-        min_tick = 0
+        min_tick = 0.1
         #max_tick = np.amax(Eabs_data[~np.isnan(Eabs_data)])
-        max_tick = 8
-        scale_ticks = np.linspace(min_tick, max_tick, 5)
-
+        max_tick = 60
+        #scale_ticks = np.linspace(min_tick, max_tick, 5)
+        #scale_ticks = np.power(10.0, np.linspace(np.log10(min_tick), np.log10(max_tick), 6))
+        scale_ticks = [0.1,0.3,1,3,10,30]
         # Interpolation can be 'nearest', 'bilinear' or 'bicubic'
         # ax.set_title(label)
         # build a rectangle in axes coords
@@ -231,14 +232,14 @@ def fieldplot(fig, ax, x, m, WL, comment='', WL_units=' ', crossplane='XZ',
         #         transform=ax.transAxes)
         cax = ax.imshow(Eabs_data, interpolation='nearest', cmap=cm.jet,
                         origin='lower', vmin=min_tick, vmax=max_tick, extent=(min(scale_x), max(scale_x), min(scale_z), max(scale_z))
-                        #,norm = LogNorm()
+                        ,norm = LogNorm()
                         )
         ax.axis("image")
 
         # Add colorbar
         cbar = fig.colorbar(cax, ticks=[a for a in scale_ticks], ax=ax)
         # vertically oriented colorbar
-        cbar.ax.set_yticklabels(['%1.0f' % (a) for a in scale_ticks])
+        cbar.ax.set_yticklabels(['%g' % (a) for a in scale_ticks])
         # pos = list(cbar.ax.get_position().bounds)
         #fig.text(pos[0] - 0.02, 0.925, '|E|/|E$_0$|', fontsize = 14)
         lp2 = -10.0
@@ -285,7 +286,7 @@ def fieldplot(fig, ax, x, m, WL, comment='', WL_units=' ', crossplane='XZ',
             # max_length=factor*x[-1]*5
             max_angle = np.pi / 160
             if is_flow_extend:
-                rg = range(0, flow_total * 2 + 1)
+                rg = range(0, flow_total * 5 + 1)
             else:
                 rg = range(0, flow_total)
             for flow in rg:

### 2015-07-16 2015-Ladutenko-Qabs/data/calc-SiAgSi3-field.py
final of filed plot for 3rd design

@@ -158,7 +158,7 @@ x, m, WL = SetXM(design, WL)
 print "x =", x
 print "m =", m
 fieldplot(fig, axs[0,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor, flow_total,
-          subplot_label='(a)')#,is_flow_extend=False)
+          subplot_label='(a) E-k WL=504nm')#,is_flow_extend=False)
 
 design = 3 #AgSi
 WL = 487
@@ -166,7 +166,7 @@ x, m, WL = SetXM(design, WL)
 print "x =", x
 print "m =", m
 fieldplot(fig, axs[0,1], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor, flow_total,
-          subplot_label='(b)')#,is_flow_extend=False)
+          subplot_label='(b) E-k WL=487nm')#,is_flow_extend=False)
 
 crossplane='YZ'
 
@@ -176,7 +176,7 @@ x, m, WL = SetXM(design, WL)
 print "x =", x
 print "m =", m
 fieldplot(fig, axs[1,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor, flow_total,
-          subplot_label='(c)')#,is_flow_extend=False)
+          subplot_label='(c) H-k WL=504nm')#,is_flow_extend=False)
 
 design = 3 #AgSi
 WL = 487
@@ -184,7 +184,7 @@ x, m, WL = SetXM(design, WL)
 print "x =", x
 print "m =", m
 fieldplot(fig, axs[1,1], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor, flow_total,
-          subplot_label='(d)')#,is_flow_extend=False)
+          subplot_label='(d) H-k WL=487nm')#,is_flow_extend=False)
 
 
 for aaxs in axs:

### 2015-07-16 2015-Ladutenko-Qabs/data/fieldplot.py

@@ -216,16 +216,16 @@ def fieldplot(fig, ax, x, m, WL, comment='', WL_units=' ', crossplane='XZ',
         # Define scale ticks
         #min_tick = np.amin(Eabs_data[~np.isnan(Eabs_data)])
         min_tick = 0.1
-        #max_tick = np.amax(Eabs_data[~np.isnan(Eabs_data)])
-        max_tick = 60
+        max_tick = np.amax(Eabs_data[~np.isnan(Eabs_data)])
+        #max_tick = 60
         #scale_ticks = np.linspace(min_tick, max_tick, 5)
         #scale_ticks = np.power(10.0, np.linspace(np.log10(min_tick), np.log10(max_tick), 6))
-        scale_ticks = [0.1,0.3,1,3,10,30]
+        scale_ticks = [0.1,0.3,1,3,10, max_tick]
         # Interpolation can be 'nearest', 'bilinear' or 'bicubic'
         # ax.set_title(label)
         # build a rectangle in axes coords
-        ax.annotate(subplot_label, xy=(1.0, 1.1), xycoords='axes fraction',  # fontsize=10,
-                    horizontalalignment='right', verticalalignment='top')
+        ax.annotate(subplot_label, xy=(0.0, 1.1), xycoords='axes fraction',  # fontsize=10,
+                    horizontalalignment='left', verticalalignment='top')
         # ax.text(right, top, subplot_label,
         #         horizontalalignment='right',
         #         verticalalignment='bottom',
@@ -239,7 +239,7 @@ def fieldplot(fig, ax, x, m, WL, comment='', WL_units=' ', crossplane='XZ',
         # Add colorbar
         cbar = fig.colorbar(cax, ticks=[a for a in scale_ticks], ax=ax)
         # vertically oriented colorbar
-        cbar.ax.set_yticklabels(['%g' % (a) for a in scale_ticks])
+        cbar.ax.set_yticklabels(['%2.1f' % (a) for a in scale_ticks])
         # pos = list(cbar.ax.get_position().bounds)
         #fig.text(pos[0] - 0.02, 0.925, '|E|/|E$_0$|', fontsize = 14)
         lp2 = -10.0

### 2015-07-17 2015-Ladutenko-Qabs/data/report-with-figures.tex
plot field design 3

@@
 \usepackage[T1]{fontenc} %%apt-get install cm-super
-%%\usepackage[english, russian]{babel}
-\usepackage[english]{babel}
+\usepackage[english, russian]{babel}
+%%\usepackage[english]{babel}
 \emergencystretch=35pt %%Чтобы нe было строчек, вылезших на поля
@@
 \section{Figures}
-\begin{frame}{Legend} %%Добавить интриги
-  \begin{block}{}
-    \begin{enumerate}
-    \item blue - dipole
-    \item red  - qudrupole
-    \item green - octupole      
-    \end{enumerate}
-  \end{block}
-  \begin{block}{}
-    \begin{enumerate}
-    \item solid - electric
-    \item dashed  - magnetic
-    \end{enumerate}
-  \end{block}
-  \begin{block}{}
-    \begin{enumerate}
-    \item thin - inner (core) layer
-    \item thicker - middle layer
-    \item thick - outher layer      
-    \end{enumerate}
-  \end{block}
-All curves are normalized to it`s maxima! As maxima goes out ot the
-plotted range normalization changes!!!
-\end{frame}
 
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+00.pdf}
+\subsection{01Eps-re.pdf}
 \begin{frame}
   \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+00.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+00.pdf}
+    \includegraphics[height=0.8\textheight]{fig/01Eps-re.pdf}%
+    \caption{Проблема с недостатоком разрешения - мало точек для
+      материальных параметров.}
   \end{figure}
@@
 
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+01.pdf}
+\subsection{02Eps-im.pdf}
 \begin{frame}
   \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+01.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+01.pdf}
+    \includegraphics[height=0.8\textheight]{fig/02Eps-im.pdf}%
+    \caption{Особено это хорошо заметно для мнимой части. Сделал
+      кубическую интерполяцию}
   \end{figure}
@@
 
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+02.pdf}
+\subsection{03-SiAgSi-ab-spectra4.pdf}
 \begin{frame}
   \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+02.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+02.pdf}
+    \includegraphics[height=0.8\textheight]{fig/03-SiAgSi-ab-spectra4.pdf}%
+    \caption{Все кривые стали глаже, этот рисунок вставил в статью.}
   \end{figure}
@@
 
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+03.pdf}
+\subsection{04SiAgSi3-flow-R81-YZ-Eabs-13.pdf}
 \begin{frame}
   \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+03.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+03.pdf}
+    \includegraphics[height=0.8\textheight]{fig/04SiAgSi3-flow-R81-YZ-Eabs-13.pdf}%
+    \caption{Картинки полей для
+      обоих случаев очень похоже - здесь нарисован |E|. Немного
+      отличается величина усиления поля для разных длин волн, сильно
+      отличается то, как рисуются линии потока энергии.}
   \end{figure}
@@
 
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+04.pdf}
+\subsection{05SiAgSi3-flow-R81-YZ-Eabs-39.pdf}
 \begin{frame}
   \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+04.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+04.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+05.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+05.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+05.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+06.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+06.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+06.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+07.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+07.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+07.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+08.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+08.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+08.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+09.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+09.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+09.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+10.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+10.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+10.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+11.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+11.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+11.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+12.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+12.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+12.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+13.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+13.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+13.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+14.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+14.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+14.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+15.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+15.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+15.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+16.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+16.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+16.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+17.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+17.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+17.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+18.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+18.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+18.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+19.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+19.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+19.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+20.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+20.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+20.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+21.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+21.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+21.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+22.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+22.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+22.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+23.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+23.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+23.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+24.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+24.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+24.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+25.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+25.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+25.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+26.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+26.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+26.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+27.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+27.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+27.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+28.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+28.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+28.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+29.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+29.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+29.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+30.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+30.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+30.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+31.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+31.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+31.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+32.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+32.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+32.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+33.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+33.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+33.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+34.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+34.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+34.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+35.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+35.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+35.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+36.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+36.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+36.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+37.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+37.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+37.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+38.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+38.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+38.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+39.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+39.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+39.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+40.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+40.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+40.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+41.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+41.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+41.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+42.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+42.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+42.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+43.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+43.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+43.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+44.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+44.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+44.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+45.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+45.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+45.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+46.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+46.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+46.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+47.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+47.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+47.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+48.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+48.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+48.pdf}
-  \end{figure}
-\end{frame}
-
-\subsection{2015-04-01-SiAgSi-ab-spectra-calc-d+49.pdf}
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/2015-04-01-SiAgSi-ab-spectra-calc-d+49.pdf}%
-    \caption{2015-04-01-SiAgSi-ab-spectra-calc-d+49.pdf}
+    \includegraphics[height=0.8\textheight]{fig/05SiAgSi3-flow-R81-YZ-Eabs-39.pdf}%
+    \caption{Более плотное покрытие линиями потока энергии. Ничего дополнительного для
+      меня к картинке с коэффициентами по слоям не добавляют, поэтому
+      пока их в рукопись не добавлял.
+}
   \end{figure}

### 2015-07-17 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py

@@ -141,11 +141,18 @@ def GetEpsilon(WLs, fname):
 ###############################################################################
 def save_spectra(fname, from_WL, to_WL, total_points, design, extra_width):
     WLs = np.linspace(from_WL, to_WL, total_points)
-    epsSi = GetEpsilon(WLs, "Si-int.txt")
-    epsAg = GetEpsilon(WLs, "Ag-int.txt")
-    data = calc(design, extra_width, WLs[0], epsSi[0,1], epsAg[0,1])
+    # epsSi = GetEpsilon(WLs, "Si-int.txt")
+    # epsAg = GetEpsilon(WLs, "Ag-int.txt")    
+    # data = calc(design, extra_width, WLs[0], epsSi[0,1], epsAg[0,1])
+    # for i in xrange(len(WLs)):
+    #     data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi[i,1], epsAg[i,1])))
+    epsSi = 18.4631066585 + 0.6259727805j
+    epsAg = -8.5014154589 + 0.7585845411j
+    WL = 500
+    data = calc(design, extra_width, from_WL, epsSi, epsAg)
     for i in xrange(len(WLs)):
-        data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi[i,1], epsAg[i,1])))
+        data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi, epsAg)))
+    
     data = data[1:]
     np.savetxt(fname,data)
 ###############################################################################

### 2015-07-17 2015-Ladutenko-Qabs/data/calc-SiAgSi3-field.py

@@ -134,12 +134,12 @@ comment='SiAgSi3-flow'
 # comment='bulk-Ag-flow'
 
 WL_units='nm'
-npts = 1501
+npts = 501
 #npts = 101
 factor=1.2
 #factor=4.5
 #flow_total = 39
-flow_total = 13
+flow_total = 0
 #flow_total = 2
 #crossplane='XY'
 

### 2015-07-17 2015-Ladutenko-Qabs/data/fieldplot.py

@@ -214,13 +214,13 @@ def fieldplot(fig, ax, x, m, WL, comment='', WL_units=' ', crossplane='XZ',
             min(coordZ) * WL / 2.0 / np.pi, max(coordZ) * WL / 2.0 / np.pi, npts)
 
         # Define scale ticks
-        #min_tick = np.amin(Eabs_data[~np.isnan(Eabs_data)])
-        min_tick = 0.1
+        min_tick = np.amin(Eabs_data[~np.isnan(Eabs_data)])
+        #min_tick = 0.1
         max_tick = np.amax(Eabs_data[~np.isnan(Eabs_data)])
         #max_tick = 60
         #scale_ticks = np.linspace(min_tick, max_tick, 5)
-        #scale_ticks = np.power(10.0, np.linspace(np.log10(min_tick), np.log10(max_tick), 6))
-        scale_ticks = [0.1,0.3,1,3,10, max_tick]
+        scale_ticks = np.power(10.0, np.linspace(np.log10(min_tick), np.log10(max_tick), 6))
+        #scale_ticks = [0.1,0.3,1,3,10, max_tick]
         # Interpolation can be 'nearest', 'bilinear' or 'bicubic'
         # ax.set_title(label)
         # build a rectangle in axes coords

### 2015-07-22 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya-v2.tex
Clean up

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for double-spaced preprint

%Phys Rev B
%Letter or rapid communication - 3500 words
%\documentclass[prb,groupedaddress,reprint]{revtex4-1}
%APL
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,reprint]{revtex4-1}
%\documentclass[aip,jap,reprint]{revtex4-1}
\usepackage[english]{babel}
\usepackage{graphicx}% Include figure files
\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%
filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}
\usepackage[figure,table]{hypcap} %links should lead to the begining
                                %of figure or table...

\begin{document} %Max size in pdf for APL - 4 print pages

% \title{More efficient than a ``super'' absorption in spherical
% nanoparticles} %KSL
% \title{Super-absorption and efficient absorption of light by
% spherical nanoparticles} %IVS
\title{Super absorption of light by nanoparticles} %AEM
% Proposed reviewers: Anatoly Zayats
% Andrea Alu
% Sergei Bozhevolnyi

\author{Konstantin Ladutenko} \email[e-mail: ]{fisik2000@mail.ru}
\affiliation{ITMO University, 49 Kronverskii Ave., St.~Petersburg
  197101, Russian Federation}

\affiliation{Ioffe Physical-Technical Institute of the Russian Academy
  of Sciences, 26 Polytekhnicheskaya Str., St.~Petersburg 194021,
  Russian Federation}

\author{Pavel Belov} \affiliation{ITMO University, 49 Kronverskii
  Ave., St.~Petersburg 197101, Russian Federation}

\author{Ovidio Pe\~{n}a-Rodr\'{i}guez} \affiliation{Instituto de
  Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid, Jos\'{e}
  Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain}

\author{Ali Mirzaei} \author{Andrey Miroshnichenko} \author{Ilya
  Shadrivov} \affiliation{Nonlinear Physics Centre, Research School of
  Physics and Engineering, The Australian National University, 59
  Mills Rd, Acton, ACT, 2601, Australia}

\date{\today}
% APL 250 words! Phys Rev B less then 500 words, about
% 5% ot total paper length
% emacs M-x count-words

\begin{abstract}
  Nanoparticles have a fundamental limit as to how much light they can
  absorb. This limit is based on the finite number of modes excited
  inside the nanoparticle at a given wavelength and maximal absorption
  capacity per mode. The enhanced absorption can be achieved
  when each mode supported by the nanopartice absorbs light up to the
  maximum capacity. Using stochastic optimization algorithm, we design
  multi-layer nanoparticles, in which we can make several resonant
  modes overlap at the same frequency resulting in {\it
    super-absorption}.  We further introduce the {\it efficiency of
    the absorption} for a nanoparticle, which is the absorption normalized
  by the physical size of the particle, and show that efficient
  absorbers are not always operating in super-absorbing regime.
\end{abstract}

\pacs% insert suggested PACS numbers in braces on next line
{41.20.Jb 42.25.Bs 02.60.Pn 02.70.-c}
% 41.20.Jb Electromagnetic wave propagation 42.25.Bs Wave propagation,
% transmission and absorption
%% 42.25.Fx Diffraction and scattering
% 02.60.Pn Numerical optimization 02.70.-c Computational techniques;
% simulations

\maketitle %\maketitle must follow title, authors, abstract and \pacs

Mie theory~\cite{Mie-1908}, which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to study the multi-layered spherical
particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
various applications in cancer treatment~\cite{Zhang-2010,
  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of thermal properties of insulating materials~\cite{Xie-2013}, as well as for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.

The scattering properties of multilayer cylinders and spheres was
studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
these works authors introduced the concept of a super-scattering, when
the scattering cross-section of a multilayer particle exceeds that of
a homogeneous particle of the same size in the so-called
single-channel limit. The super-scattering appears when a
multi-layer structure has several nearly degenerate modes,
i.e. their resonance frequencies coincide or close to each other. In a homogeneous particle, the resonances appear at different frequencies, and there is no design freedom to make these resonances overlap, and this limits the
achievable scattering cross-section.

Similar fundamental limitations exist for the absorbing properties of
sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
derived a theoretical limit of a maximum absorption cross-section
(ACS) value for a single channel, i.e., when only one mode of the
sphere is excited.  As a result the absorption coefficients
$\tilde{a}_n= {\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm
  Re}\{b_n\} - |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$
are scattering coefficient as defined within the Mie
theory~\cite{Bohren-1983}.

To overcome these limitations, we employ similar approach to the one used for
enhancing absorption cross-section~\cite{Fan-2011}. In particular, we
propose to use the multi-layer structures, and by means of stochastic
optimization algorithm we optimize the ACS of such nanoparticles. We
analyze the absorption cross-section of these particles, and present
the super-absorption regime. We further introduce the absorption
efficiency, which is the ACS normalized to the geometric cross-section
of the particles. Here we show that there is a strong counter-play
between the increased absorption for larger particles vs size for
smaller particles, and quite remarkably we find that the most {\em
  efficient} absorption can be achieved in a single channel limit for
small particles.

Another approach for an ideal absorber is given in a recent work by
Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only
a dipole approximation, and the final result is very close to the dipole limit predicted by
Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
corresponds to the single mode limit.  At the same time, Grigoriev et
al.~\cite{Grigoriev-2015} also provide an equation to design a
core-shell structure from given materials. However, in the case of
$Si$ core and $Ag$ shell materials and sizes taken from the best design obtained in the present paper, their equation gives a complex value for the core material filling factor, which cannot be achieved in an experimental realisations.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/Fig1}%
    \caption{ Shematic view of the simulated $Si/Ag/Si$ particle. 
      \label{fig:geom}
    }%
  }
\end{figure}

We start our analyses by considering the triple layered $Si/Ag/Si$
spherical particle illuminated with a plane
wave schematically shown in Fig.~\ref{fig:geom}. In what follows we describe the materials
using experimentally measured parameters from the
Ref.~\cite{palik-1997}, and, e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
layer we implemented~\cite{JADE-web} an adaptive differential
evolution algorithm~\cite{Storn-DE-first-1997}, which is called
JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
optimization algorithm are published previously in
Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
Scattnlay software~\cite{Pena-scattnlay-2009,Scattnlay-web}, whose
results are verified by a number of other implementations of the
Mie solutions and by a commercially available software including CST
Microwave studio~\cite{CST-web} and Comsol Multiphysics~\cite{Comsol-web}.

It is a common understanding that, in general, a bigger particle 
has a bigger absorption cross-section, so sphere with the diameter of
1 cm absorbs more light than any nanoscale sphere. Therefore, it is practical to employ {\em the absorption
efficiency} $Q_{\rm abs}=C_{\rm abs}/\pi R^2$, where $R$ is the outer
radius of the particle and $C_{\rm abs}$ is the absorption
cross-section.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
    \caption{ Results of the optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved for the particle of the radius of 36~nm and
      Ag/Si design (zero sized core). Dashed lines show theoretical
      limits for the first channel and second channel
      absorption. Second and third peaks in the absorption efficiency
      curve exceed the theoretical limit for the second mode
      absorption at $R=63$~nm and $R=81$~nm. Local maxima of
      absorption efficiency are additionally marked with arrows. (b) Mie absorption
      coefficients for individual excited modes of the optimized
      structures. (c) Optimized layer thicknesses. For the total
      particle radius below 46~nm the optimizer converges to
      the two-layer structure, when core size vanishes, and the
      optimum design is a bi-layer $Ag/Si$ particle. 
      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency. We maximize absorption efficiency at a fixed wavelength
of the incident light (we have chosen $\lambda=500$~nm). We show the results of our stochastic optimization
algorithm in Fig.~\ref{fig:overview}~(a).  Dashed lines show
theoretical absorption limit of a dipole ($n=1$) and a quadrupole
($n=2$) resonances~\cite{Tribelsky-2011}, which are given
as $$Q^{(n)}_{\rm abs\ max}=\frac{2n+1}{2q^2},$$ where the size
parameter $q=2\pi R/\lambda$, and $n$ is the angular momentum of the
mode. Following Ref.~\cite{Fan-2011}, where authors introduce
super-scattering for spherical particles, here we we introduce
super-absorption regime, when {\em the ACS is larger than the theoretical limit
for absorption by the mode with highest excited angular momentum
$n$}. In our parameter space we have just modes up to the quadrupole
excited ($n=2$), and in order to get a super-absorption our efficiency
should be higher than that of a quadrupole. We clearly see this
super-absorption regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).

In Fig.~\ref{fig:overview}~(b) we present the values of Mie absorption
coefficients for individual excited modes in the structure, while
horizontal dashed line shows the theoretical limit (1/4) for each of
them. $\tilde{a}_{1,2}$ are electric dipole and electric quadrupole,
while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
quadrupole. For small particles, as expected, the absorption is
dominated by an electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the
optimization procedure finds that the designs with both electric and
magnetic dipoles have larger ACS, than the structure with only the
electric dipole excited. This is why the curves in
Figs.~\ref{fig:overview}~(b,c) experience the discontinuity. We also
note that there is a very narrow range of particle sizes, between
80.7~nm and 82.1~nm, where our analyses finds that the design
supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
$\tilde{b}_2$ has larger ACS, and this explains two more
discontinuities of the curves at the respective size values.

Fig.~\ref{fig:overview}~(c) shows optimized sizes of the layers inside
the multi-layer structure. It reveals quite a curious result, that the
dipole branch (i.e. for particle radii below 56.6~nm) has two
parts. For $R<46$~nm the best absorber has just two layers, as the
radius of the core of the three-layer structure vanishes, and the
particle reduces to $Ag/Si$ core-shell structure.  At $R=46$~nm dipole
channel reaches its theoretical limit (it becomes
$\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
inner $Si$ layer in order to keep $\tilde{a}_1$ near the theoretical
limit as the $R$ increases.  As a side effect, the quadrupole
contribution $\tilde{a}_2$ appears; however, it does not help to reach
super-absorption limit for $n=2$.

Remarkably, the absolute maximum {\em absorption efficiency} is not reached
within the super-absorption regime. Figure~\ref{fig:overview} shows
that the maximum efficiency is achieved for small particle size, and
the ACS is still well below the single channel limit. It appears that
the $Ag/Si$ core-shell nanoparticle, with the total radii of
approximately 36~nm is the most efficient absorber in the considered
structure, whose ACS reaches values {\em over 5 times the physical
cross-section area of the particle}.  From practical point of view it
is quite important that the maximum can be reached in a bi-layer
structure, instead of a triple-layer, since it should be easier and
cheaper to fabricate.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)super-absorption design.      
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of the structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the super-absorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.

A noticeable feature of Fig.~\ref{fig:spectra}~(c) is an almost flat
top of the electric dipole resonance.  
%This effect might be related with the coupling between the electric
%dipole $\tilde{a}_1$ with the magnetic quadrupole $\tilde{b}_2$, but
%this hypothesis should be further tested.  Whereas resonant responses
%of other designs originate from coupling of incident plane wave with
%the corresponding multipole, it is not the case for the design with
%$R=81$~nm. Here, the particle is mostly composed from the $Si$ outer
%shell, that give enough volume for $\tilde{b}_2$.  Dipole response
%comes from the small inner part of the sphere and can not be directly
%excited with the incident wave.  It takes the power from the
%surrounding $\tilde{b}_2$ mode and very soon it reaches the
%fundamental limit for absorption.  This way, we can observe a flat top
%for the $\tilde{a}_1$ response accompanied with a significant value of
%$\tilde{b}_2$.  Our suggestion is indirectly proven by the reduced
%width of the $\tilde{b}_2$ resonance compared to other quadrupole
%responses.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
    \caption{ Amplitude of electric field for $R=36$~nm (a,c) and
      super-absorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to incident wave. 
      \label{fig:field}
    }%
  }
\end{figure}
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a super-absorbing design with
$R=63$~nm.  Using semi-transparent white curves we also plot
streamlines of the Poynting vector which characterize energy flow.
For the effective design of the absorber, the power from a large
cross-sectional area flows into the particle.  In case of
super-absorption regime, we observe the formation of vortices in the
power flow, which make absorption more efficient as the
electromagnetic energy propagates several times through the absorbing
materials.  The reason for the smaller overall absorption efficiency
of a super-absorbing design is obvious: spatial distribution of the electric
field is not uniform inside the particle and the share of the volume
with high absorption rate in the vortices do not compensate low
absorption efficiency in the regions with small electric field (
absorbed power is expressed as $P_{\rm abs}=\frac{1}{2}\int\sigma
\left|E\right|^2dx\,dy\,dz$)

In conclusion, we introduce and study the effect of the super-absorption, when the
absorption cross-section of the nanoparticle can reach the theoretical
limit for several modes at the same frequency. This becomes possible when several resonant modes of the
structure overlap at the same frequency, and this regime can be achieved in multi-layer nanoparticles. Moreover, quite unexpectedly we find that the most efficient absorbers, which are characterized by
enhanced absorption efficiencies, are smaller nanoparticles working in
a single mode regime. We present their spectral characteristics and
field structure.  The stochastic algorithm utilized in our approach is
very generic and the optimization can be repeated for any desired
wavelength or wavelength range.  As a result, one can design
spectrally-selective absorbers or broadband absorbers with almost
arbitrary prescribed properties.  It is interesting to note
that a similar conclusion was made by Miller et al.~\cite{Miller-2014}
for extinction of arbitrary particles: small size with only dipole
response is preferable for geometric volume normalized efficiency.

\begin{acknowledgments}

 AEM and IVS would like to acknowledge support from the Australian Research Council through Future Fellow and Discovery project schemes. 
  % The authors would like to thank the Ministry of Education and
  % Science of the Russian Federation (Goszadanie 2014/190, Zadanie
  % No. 3.561.2014/K, project 14.584.21.0009 10), Russian Foundation
  % for Basic Research (Grant 15-02-01344), and Government of the
  % Russian Federation (Grant 074-U01) for the financial support. The
  % simulations of cloak designs has been funded by the Russian
  % Science Foundation Grant No. 14-12-01227.
\end{acknowledgments}

\bibliography{2015-Ladutenko-Qabs}
\end{document}

### 2015-07-22 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya-v3.tex
Clean up

--- 2015-07-22 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya-v2.tex
@@
 % nanoparticles} %KSL
-% \title{Super-absorption and efficient absorption of light by
+% \title{Superabsorption and efficient absorption of light by
 % spherical nanoparticles} %IVS
-\title{Super absorption of light by nanoparticles} %AEM
-% Proposed reviewers: Anatoly Zayats
-% Andrea Alu
-% Sergei Bozhevolnyi
+\title{Superabsorption of light by nanoparticles} %AEM
+% Proposed reviewers: Anatoly Zayats Andrea Alu Sergei Bozhevolnyi
 
@@
   absorb. This limit is based on the finite number of modes excited
-  inside the nanoparticle at a given wavelength and maximal absorption
-  capacity per mode. The enhanced absorption can be achieved
-  when each mode supported by the nanopartice absorbs light up to the
-  maximum capacity. Using stochastic optimization algorithm, we design
-  multi-layer nanoparticles, in which we can make several resonant
+  in the nanoparticle at a given wavelength and maximum absorption
+  capacity per mode. The enhanced absorption can be achieved when each
+  mode supported by the nanopartice absorbs light up to the maximum
+  capacity. Using stochastic optimization algorithm, we design
+  multilayer nanoparticles, in which we can make several resonant
   modes overlap at the same frequency resulting in {\it
-    super-absorption}.  We further introduce the {\it efficiency of
-    the absorption} for a nanoparticle, which is the absorption normalized
+    superabsorption}.  We further introduce the {\it efficiency of the
+    absorption} for a nanoparticle, which is the absorption normalized
   by the physical size of the particle, and show that efficient
-  absorbers are not always operating in super-absorbing regime.
+  absorbers are not always operating in the superabsorbing regime.
 \end{abstract}
@@
 interaction of electromagnetic waves with spherical particles. Mie
-solution is still of great interest these days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
+solution is still of great interest these
+days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
 since it is one of the primary tools for analyzing wave scattering by
@@
 theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
-it to study the multi-layered spherical
+it to the study of multilayer spherical
 particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
@@
 cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
-plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of thermal properties of insulating materials~\cite{Xie-2013}, as well as for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.
+plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of
+thermal properties of insulating materials~\cite{Xie-2013}, as well as
+for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.
 
@@
 studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
-these works authors introduced the concept of a super-scattering, when
-the scattering cross-section of a multilayer particle exceeds that of
+these works the authors introduced the concept of superscattering,
+when scattering cross-section of a multilayer particle exceeds that of
 a homogeneous particle of the same size in the so-called
-single-channel limit. The super-scattering appears when a
-multi-layer structure has several nearly degenerate modes,
-i.e.
-their resonance frequencies coincide or close to each other.
-In a homogeneous particle, the resonances appear at different frequencies, and there is no design freedom to make these resonances overlap, and this limits the
+single-channel limit. Superscattering appears when a multilayer
+structure has several nearly degenerate modes, i.e. their resonance
+frequencies coincide or are close to each other. In a homogeneous
+particle, resonances appear at different frequencies, and there is no
+design freedom to make these resonances overlap, and this limits the
 achievable scattering cross-section.
@@
 Similar fundamental limitations exist for the absorbing properties of
-sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
+subwavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
 derived a theoretical limit of a maximum absorption cross-section
-(ACS) value for a single channel, i.e., when only one mode of the
-sphere is excited.  As a result the absorption coefficients
-$\tilde{a}_n= {\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm
-  Re}\{b_n\} - |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$
-are scattering coefficient as defined within the Mie
-theory~\cite{Bohren-1983}.
+(ACS) value for a single channel, i.e., when only one mode of a sphere
+is excited.  As a result, the absorption coefficients $\tilde{a}_n=
+{\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} -
+|b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
+coefficient as defined within the Mie theory~\cite{Bohren-1983}.
 
-To overcome these limitations, we employ similar approach to the one used for
-enhancing absorption cross-section~\cite{Fan-2011}. In particular, we
-propose to use the multi-layer structures, and by means of stochastic
-optimization algorithm we optimize the ACS of such nanoparticles. We
-analyze the absorption cross-section of these particles, and present
-the super-absorption regime. We further introduce the absorption
-efficiency, which is the ACS normalized to the geometric cross-section
-of the particles. Here we show that there is a strong counter-play
-between the increased absorption for larger particles vs size for
-smaller particles, and quite remarkably we find that the most {\em
-  efficient} absorption can be achieved in a single channel limit for
-small particles.
+To overcome these limitations, we employ similar approach to the one
+used for enhancing scattering cross-section~\cite{Fan-2011}. In
+particular, we propose to use the multilayer structures, and by means
+of stochastic optimization algorithm we optimize the ACS of such
+nanoparticles. We analyze the absorption cross-section of these
+particles, and present the superabsorption regime. We further
+introduce the absorption efficiency, which is the ACS normalized to
+the geometric cross-section of particles. Here we show that there is a
+strong counterplay between the increased absorption for larger
+particles vs size for smaller particles, and quite remarkably we find
+that the most {\em efficient} absorption can be achieved in a single
+channel limit for small particles.
 
-Another approach for an ideal absorber is given in a recent work by
-Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only
-a dipole approximation, and the final result is very close to the dipole limit predicted by
-Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
+Another approach for an ideal absorber is given in the recent work by
+Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only dipole
+approximation, and the final result is very close to the dipole limit
+predicted by Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
 corresponds to the single mode limit.  At the same time, Grigoriev et
@@
 core-shell structure from given materials. However, in the case of
-$Si$ core and $Ag$ shell materials and sizes taken from the best design obtained in the present paper, their equation gives a complex value for the core material filling factor, which cannot be achieved in an experimental realisations.
+$Si$ core and $Ag$ shell materials and sizes taken from the best
+design obtained in the present paper, their equation gives a complex
+value for the core material filling factor, which cannot be achieved
+in experimental realisations.
 
@@
 
-We start our analyses by considering the triple layered $Si/Ag/Si$
-spherical particle illuminated with a plane
-wave schematically shown in Fig.~\ref{fig:geom}. In what follows we describe the materials
-using experimentally measured parameters from the
-Ref.~\cite{palik-1997}, and, e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
+We start our analyses by considering the triple-layer $Si/Ag/Si$
+spherical particle illuminated with a plane wave schematically shown
+in Fig.~\ref{fig:geom}. In what follows we describe the materials
+using experimentally measured parameters from Ref.~\cite{palik-1997},
+and, e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
 $\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
@@
 JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
-optimization algorithm are published previously in
+optimization algorithm were published previously in
 Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
 Scattnlay software~\cite{Pena-scattnlay-2009,Scattnlay-web}, whose
-results are verified by a number of other implementations of the
-Mie solutions and by a commercially available software including CST
-Microwave studio~\cite{CST-web} and Comsol Multiphysics~\cite{Comsol-web}.
+results are verified by a number of other implementations of the Mie
+solutions and by commercially available software including CST
+Microwave studio~\cite{CST-web} and Comsol
+Multiphysics~\cite{Comsol-web}.
 
-It is a common understanding that, in general, a bigger particle 
-has a bigger absorption cross-section, so sphere with the diameter of
-1 cm absorbs more light than any nanoscale sphere. Therefore, it is practical to employ {\em the absorption
-efficiency} $Q_{\rm abs}=C_{\rm abs}/\pi R^2$, where $R$ is the outer
-radius of the particle and $C_{\rm abs}$ is the absorption
-cross-section.
+It is a common understanding that, in general, a larger particle has a
+larger absorption cross-section, so sphere with the diameter of 1 cm
+absorbs more light than any nanoscale sphere. Therefore, it is
+practical to employ {\em the absorption efficiency} $Q_{\rm
+  abs}=C_{\rm abs}/\pi R^2$, where $R$ is the outer radius of the
+particle and $C_{\rm abs}$ is the absorption cross-section.
 
@@
     \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
-    \caption{ Results of the optimization of the absorption efficiency
+    \caption{ Results of optimization of the absorption efficiency
       for the fixed wavelength of 500~nm. (a) Absorption efficiency
@@
       limits for the first channel and second channel
-      absorption. Second and third peaks in the absorption efficiency
+      absorption. The second and third peaks in the absorption efficiency
       curve exceed the theoretical limit for the second mode
@@
       particle radius below 46~nm the optimizer converges to
-      the two-layer structure, when core size vanishes, and the
-      optimum design is a bi-layer $Ag/Si$ particle. 
+      a bi-layer structure, when core size vanishes, and the
+      optimum design is a $Ag/Si$ particle. 
       \label{fig:overview}
@@
 radii of internal cores, whereas the target function is the absorption
-efficiency. We maximize absorption efficiency at a fixed wavelength
-of the incident light (we have chosen $\lambda=500$~nm). We show the results of our stochastic optimization
-algorithm in Fig.~\ref{fig:overview}~(a).  Dashed lines show
-theoretical absorption limit of a dipole ($n=1$) and a quadrupole
-($n=2$) resonances~\cite{Tribelsky-2011}, which are given
-as $$Q^{(n)}_{\rm abs\ max}=\frac{2n+1}{2q^2},$$ where the size
-parameter $q=2\pi R/\lambda$, and $n$ is the angular momentum of the
-mode. Following Ref.~\cite{Fan-2011}, where authors introduce
-super-scattering for spherical particles, here we we introduce
-super-absorption regime, when {\em the ACS is larger than the theoretical limit
-for absorption by the mode with highest excited angular momentum
-$n$}. In our parameter space we have just modes up to the quadrupole
-excited ($n=2$), and in order to get a super-absorption our efficiency
-should be higher than that of a quadrupole. We clearly see this
-super-absorption regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).
+efficiency. We maximize absorption efficiency at a fixed wavelength of
+the incident light (we have chosen $\lambda=500$~nm). We show the
+results of our stochastic optimization algorithm in
+Fig.~\ref{fig:overview}~(a).  Dashed lines show theoretical absorption
+limit of a dipole ($n=1$) and a quadrupole ($n=2$)
+resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm
+  abs\ max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi
+R/\lambda$, and $n$ is the angular momentum of the mode. Following
+Ref.~\cite{Fan-2011}, where the authors introduce superscattering for
+spherical particles, here we introduce superabsorption regime, when
+{\em the ACS is larger than the theoretical limit for absorption by
+  the mode with the highest excited angular momentum $n$}. In our
+parameter space we have just modes up to the quadrupole excited
+($n=2$), and in order to get superabsorption our efficiency should be
+higher than that of a quadrupole. We clearly see this superabsorption
+regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).
 
@@
 while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
-quadrupole. For small particles, as expected, the absorption is
-dominated by an electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the
-optimization procedure finds that the designs with both electric and
-magnetic dipoles have larger ACS, than the structure with only the
-electric dipole excited. This is why the curves in
+quadrupole. For small particles, as expected, absorption is dominated
+by electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the optimization
+procedure finds that the designs with both electric and magnetic
+dipoles have larger ACS than the structure with only the electric
+dipole excited. This is why the curves in
 Figs.~\ref{fig:overview}~(b,c) experience the discontinuity. We also
 note that there is a very narrow range of particle sizes, between
-80.7~nm and 82.1~nm, where our analyses finds that the design
+80.7~nm and 82.1~nm, where our analysis finds that the design
 supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
@@
 
-Fig.~\ref{fig:overview}~(c) shows optimized sizes of the layers inside
-the multi-layer structure. It reveals quite a curious result, that the
+Fig.~\ref{fig:overview}~(c) shows optimized sizes of layers inside a
+multilayer structure. It reveals quite a curious result, that the
 dipole branch (i.e. for particle radii below 56.6~nm) has two
 parts. For $R<46$~nm the best absorber has just two layers, as the
-radius of the core of the three-layer structure vanishes, and the
+radius of the core of a triple-layer structure vanishes, and the
 particle reduces to $Ag/Si$ core-shell structure.  At $R=46$~nm dipole
@@
 contribution $\tilde{a}_2$ appears; however, it does not help to reach
-super-absorption limit for $n=2$.
+superabsorption limit for $n=2$.
 
-Remarkably, the absolute maximum {\em absorption efficiency} is not reached
-within the super-absorption regime. Figure~\ref{fig:overview} shows
-that the maximum efficiency is achieved for small particle size, and
-the ACS is still well below the single channel limit. It appears that
-the $Ag/Si$ core-shell nanoparticle, with the total radii of
-approximately 36~nm is the most efficient absorber in the considered
-structure, whose ACS reaches values {\em over 5 times the physical
-cross-section area of the particle}.  From practical point of view it
-is quite important that the maximum can be reached in a bi-layer
+Remarkably, the absolute maximum {\em absorption efficiency} is not
+reached within the superabsorption regime. Figure~\ref{fig:overview}
+shows that the maximum efficiency is achieved for small particle size,
+and the ACS is still well below the single channel limit. It appears
+that the $Ag/Si$ core-shell nanoparticle with the total radii of
+approximately 36~nm is the most efficient absorber among the considered
+structures, whose ACS reaches values {\em over 5 times the physical
+  cross-section area of the particle}.  From a practical point of view,
+it is quite important that the maximum can be reached in a bi-layer
 structure, instead of a triple-layer, since it should be easier and
@@
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
-    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)super-absorption design.      
+    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra4.pdf}%
+    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design.
+Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer.
       \label{fig:spectra}
@@
 \end{figure}
-To study spectral properties of the structures with large ACS which we
+To study spectral properties of structures with large ACS which we
 obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
@@
 $\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
-$R=81$~nm have a signature of the super-absorption, i.e. there is an
+$R=81$~nm have a signature of the superabsorption, i.e. there is an
 overlap of several resonances.  We note that these structures have
 additional absorption resonances, but they are located far from the
-wavelength of interest.
-
-A noticeable feature of Fig.~\ref{fig:spectra}~(c) is an almost flat
-top of the electric dipole resonance.  
-%This effect might be related with the coupling between the electric
-%dipole $\tilde{a}_1$ with the magnetic quadrupole $\tilde{b}_2$, but
-%this hypothesis should be further tested.  Whereas resonant responses
-%of other designs originate from coupling of incident plane wave with
-%the corresponding multipole, it is not the case for the design with
-%$R=81$~nm. Here, the particle is mostly composed from the $Si$ outer
-%shell, that give enough volume for $\tilde{b}_2$.  Dipole response
-%comes from the small inner part of the sphere and can not be directly
-%excited with the incident wave.  It takes the power from the
-%surrounding $\tilde{b}_2$ mode and very soon it reaches the
-%fundamental limit for absorption.  This way, we can observe a flat top
-%for the $\tilde{a}_1$ response accompanied with a significant value of
-%$\tilde{b}_2$.  Our suggestion is indirectly proven by the reduced
-%width of the $\tilde{b}_2$ resonance compared to other quadrupole
-%responses.
+wavelength of interest.  A noticeable feature of
+Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
+dipole resonance.
+More detailed analysis shows that we have {\em excited several electric dipole resonances} with close resonance frequencies within our multilayer structure.
+Indeed, if we plot a superposition of the squares of the absolute values of the Mie coefficients, which characterize energy stored in each layer, we find that we excite resonances in all three layers, and they are slightly offset as shown in Fig.~\ref{fig:spectra} (d).
+Combined effect of these resonances produces the flat and relatively broadband electric resonance response shown in Fig.~\ref{fig:spectra} (c).
 
@@
     \caption{ Amplitude of electric field for $R=36$~nm (a,c) and
-      super-absorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
+      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
       planes normalized to incident wave. 
@@
 field in Fig.~\ref{fig:field} for two designs: with the best
-efficiency at $R=36$~nm and in a super-absorbing design with
-$R=63$~nm.  Using semi-transparent white curves we also plot
-streamlines of the Poynting vector which characterize energy flow.
-For the effective design of the absorber, the power from a large
-cross-sectional area flows into the particle.  In case of
-super-absorption regime, we observe the formation of vortices in the
-power flow, which make absorption more efficient as the
-electromagnetic energy propagates several times through the absorbing
-materials.  The reason for the smaller overall absorption efficiency
-of a super-absorbing design is obvious: spatial distribution of the electric
-field is not uniform inside the particle and the share of the volume
-with high absorption rate in the vortices do not compensate low
-absorption efficiency in the regions with small electric field (
-absorbed power is expressed as $P_{\rm abs}=\frac{1}{2}\int\sigma
-\left|E\right|^2dx\,dy\,dz$)
+efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
+Using semi-transparent white curves we also plot streamlines of the
+Poynting vector which characterize energy flow.  For the effective
+design of the absorber, the power from a large cross-sectional area
+flows into the particle.  In case of superabsorption regime, we
+observe the formation of vortices in the power flow, which make
+absorption more efficient as the electromagnetic energy propagates
+several times through the absorbing materials.  The reason for the
+smaller overall absorption efficiency of a superabsorbing design is
+obvious: spatial distribution of the electric field is not uniform
+inside the particle and the share of the volume with high absorption
+rate in the vortices does not compensate low absorption efficiency in
+the regions with small electric field (absorbed power is expressed as
+$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)
 
-In conclusion, we introduce and study the effect of the super-absorption, when the
-absorption cross-section of the nanoparticle can reach the theoretical
-limit for several modes at the same frequency. This becomes possible when several resonant modes of the
-structure overlap at the same frequency, and this regime can be achieved in multi-layer nanoparticles.
-Moreover, quite unexpectedly we find that the most efficient absorbers, which are characterized by
-enhanced absorption efficiencies, are smaller nanoparticles working in
-a single mode regime. We present their spectral characteristics and
-field structure.  The stochastic algorithm utilized in our approach is
-very generic and the optimization can be repeated for any desired
-wavelength or wavelength range.  As a result, one can design
-spectrally-selective absorbers or broadband absorbers with almost
-arbitrary prescribed properties.  It is interesting to note
-that a similar conclusion was made by Miller et al.~\cite{Miller-2014}
-for extinction of arbitrary particles: small size with only dipole
-response is preferable for geometric volume normalized efficiency.
+In conclusion, we introduce and study the effect of superabsorption,
+when the absorption cross-section of the nanoparticle can reach the
+theoretical limit for several modes at the same frequency. This
+becomes possible when several resonant modes of the structure overlap
+at the same frequency, and this regime can be achieved in multilayer
+nanoparticles. Moreover, quite unexpectedly we find that the most
+efficient absorbers, which are characterized by enhanced absorption
+efficiencies, are smaller nanoparticles working in a single mode
+regime. We present their spectral characteristics and field structure.
+The stochastic algorithm utilized in our approach is very generic and
+the optimization can be repeated for any desired wavelength or
+wavelength range.  As a result, one can design spectrally-selective
+absorbers or broadband absorbers with almost arbitrary prescribed
+properties.  It is interesting to note that a similar conclusion was
+made by Miller et al.~\cite{Miller-2014} for extinction of arbitrary
+particles: small size with only dipole response is preferable for
+geometric volume normalized efficiency.
 
 \begin{acknowledgments}
-
- AEM and IVS would like to acknowledge support from the Australian Research Council through Future Fellow and Discovery project schemes. 
-  % The authors would like to thank the Ministry of Education and
-  % Science of the Russian Federation (Goszadanie 2014/190, Zadanie
-  % No. 3.561.2014/K, project 14.584.21.0009 10), Russian Foundation
-  % for Basic Research (Grant 15-02-01344), and Government of the
-  % Russian Federation (Grant 074-U01) for the financial support. The
-  % simulations of cloak designs has been funded by the Russian
-  % Science Foundation Grant No. 14-12-01227.
+  Thanks to David A. Powell for his contribution to the analysis of
+  the spectrum feature.  AEM and IVS would like to acknowledge support
+  from the Australian Research Council through Future Fellow and
+  Discovery project schemes. KSL and PAB would like to thank the
+  Ministry of Education and Science of the Russian Federation and
+  Government of the Russian Federation (Grant 074-U01) for the
+  financial support.
 \end{acknowledgments}

### 2015-07-22 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs_revised.tex
Clean up

--- 2015-07-22 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya-v3.tex
@@
   absorb. This limit is based on the finite number of modes excited
-  in the nanoparticle at a given wavelength and maximum absorption
+  inside the nanoparticle at a given wavelength and maximum absorption
   capacity per mode. The enhanced absorption can be achieved when each
@@
   modes overlap at the same frequency resulting in {\it
-    superabsorption}.  We further introduce the {\it efficiency of the
-    absorption} for a nanoparticle, which is the absorption normalized
-  by the physical size of the particle, and show that efficient
-  absorbers are not always operating in the superabsorbing regime.
+    superabsorption}.  We further introduce the {\it efficiency of
+    the absorption} for a nanoparticle, which is the absorption
+  normalized by the physical size of the particle, and show that
+  efficient absorbers are not always operating in superabsorbing
+  regime.
 \end{abstract}
@@
 studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
-these works the authors introduced the concept of superscattering,
-when scattering cross-section of a multilayer particle exceeds that of
+these works the authors introduced the concept of superscattering, when
+scattering cross-section of a multilayer particle exceeds that of
 a homogeneous particle of the same size in the so-called
@@
 frequencies coincide or are close to each other. In a homogeneous
-particle, resonances appear at different frequencies, and there is no
-design freedom to make these resonances overlap, and this limits the
-achievable scattering cross-section.
+particle, resonances appear at different frequencies, and there is
+no design freedom to make these resonances overlap, and this limits
+the achievable scattering cross-section.
 
@@
 derived a theoretical limit of a maximum absorption cross-section
-(ACS) value for a single channel, i.e., when only one mode of a sphere
-is excited.  As a result, the absorption coefficients $\tilde{a}_n=
-{\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} -
-|b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
-coefficient as defined within the Mie theory~\cite{Bohren-1983}.
+(ACS) value for a single channel, i.e., when only one mode of a
+sphere is excited.  As a result, the absorption coefficients
+$\tilde{a}_n= {\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm
+  Re}\{b_n\} - |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$
+are scattering coefficient as defined within the Mie
+theory~\cite{Bohren-1983}.
 
 To overcome these limitations, we employ similar approach to the one
-used for enhancing scattering cross-section~\cite{Fan-2011}. In
+used for enhancing absorption cross-section~\cite{Fan-2011}. In
 particular, we propose to use the multilayer structures, and by means
@@
 introduce the absorption efficiency, which is the ACS normalized to
-the geometric cross-section of particles. Here we show that there is a
-strong counterplay between the increased absorption for larger
+the geometric cross-section of particles. Here we show that there
+is a strong counterplay between the increased absorption for larger
 particles vs size for smaller particles, and quite remarkably we find
@@
 Another approach for an ideal absorber is given in the recent work by
-Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only dipole
-approximation, and the final result is very close to the dipole limit
-predicted by Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
-corresponds to the single mode limit.  At the same time, Grigoriev et
-al.~\cite{Grigoriev-2015} also provide an equation to design a
-core-shell structure from given materials. However, in the case of
-$Si$ core and $Ag$ shell materials and sizes taken from the best
-design obtained in the present paper, their equation gives a complex
-value for the core material filling factor, which cannot be achieved
-in experimental realisations.
+Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only
+dipole approximation, and the final result is very close to the dipole
+limit predicted by Tribelsky~\cite{Tribelsky-2011}.  Such absorption
+design corresponds to the single mode limit.  At the same time,
+Grigoriev et al.~\cite{Grigoriev-2015} also provide an equation to
+design a core-shell structure from given materials. However, in the
+case of $Si$ core and $Ag$ shell materials and sizes taken from the
+best design obtained in the present paper, their equation gives a
+complex value for the core material filling factor, which cannot be
+achieved in experimental realisations.
 
@@
 
-We start our analyses by considering the triple-layer $Si/Ag/Si$
+We start our analyses by considering the triple layer $Si/Ag/Si$
 spherical particle illuminated with a plane wave schematically shown
 in Fig.~\ref{fig:geom}. In what follows we describe the materials
-using experimentally measured parameters from Ref.~\cite{palik-1997},
-and, e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
-$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
-layer we implemented~\cite{JADE-web} an adaptive differential
-evolution algorithm~\cite{Storn-DE-first-1997}, which is called
-JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
+using experimentally measured parameters from Ref.~\cite{palik-1997}, and, e.g. at $\lambda = 500$ nm $\epsilon_{Si}
+= 18.5 + i0.63$ and $\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the
+thickness of each layer we implemented~\cite{JADE-web} an adaptive
+differential evolution algorithm~\cite{Storn-DE-first-1997}, which is
+called JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
 optimization algorithm were published previously in
@@
       particle radius below 46~nm the optimizer converges to
-      a bi-layer structure, when core size vanishes, and the
-      optimum design is a $Ag/Si$ particle. 
+      a two-layer structure, when core size vanishes, and the
+      optimum design is a bi-layer $Ag/Si$ particle. 
       \label{fig:overview}
@@
 Ref.~\cite{Fan-2011}, where the authors introduce superscattering for
-spherical particles, here we introduce superabsorption regime, when
-{\em the ACS is larger than the theoretical limit for absorption by
-  the mode with the highest excited angular momentum $n$}. In our
+spherical particles, here we introduce superabsorption regime,
+when {\em the ACS is larger than the theoretical limit for absorption
+  by the mode with the highest excited angular momentum $n$}. In our
 parameter space we have just modes up to the quadrupole excited
-($n=2$), and in order to get superabsorption our efficiency should be
-higher than that of a quadrupole. We clearly see this superabsorption
-regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).
+($n=2$), and in order to get superabsorption our efficiency should
+be higher than that of a quadrupole. We clearly see this
+superabsorption regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).
 
@@
 while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
-quadrupole. For small particles, as expected, absorption is dominated
-by electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the optimization
-procedure finds that the designs with both electric and magnetic
-dipoles have larger ACS than the structure with only the electric
-dipole excited. This is why the curves in
+quadrupole. For small particles, as expected, absorption is
+dominated by electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the
+optimization procedure finds that the designs with both electric and
+magnetic dipoles have larger ACS than the structure with only the
+electric dipole excited. This is why the curves in
 Figs.~\ref{fig:overview}~(b,c) experience the discontinuity. We also
 note that there is a very narrow range of particle sizes, between
-80.7~nm and 82.1~nm, where our analysis finds that the design
+80.7~nm and 82.1~nm, where our analyses find that the design
 supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
@@
 
-Fig.~\ref{fig:overview}~(c) shows optimized sizes of layers inside a
-multilayer structure. It reveals quite a curious result, that the
+Fig.~\ref{fig:overview}~(c) shows optimized sizes of layers inside
+a multilayer structure. It reveals quite a curious result, that the
 dipole branch (i.e. for particle radii below 56.6~nm) has two
 parts. For $R<46$~nm the best absorber has just two layers, as the
-radius of the core of a triple-layer structure vanishes, and the
+radius of the core of a three-layer structure vanishes, and the
 particle reduces to $Ag/Si$ core-shell structure.  At $R=46$~nm dipole
@@
 that the $Ag/Si$ core-shell nanoparticle with the total radii of
-approximately 36~nm is the most efficient absorber among the considered
-structures, whose ACS reaches values {\em over 5 times the physical
-  cross-section area of the particle}.  From a practical point of view,
+approximately 36~nm is the most efficient absorber in the considered
+structure, whose ACS reaches values {\em over 5 times the physical
+  cross-section area of the particle}.  From practical point of view,
 it is quite important that the maximum can be reached in a bi-layer
@@
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra4.pdf}%
+    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
     \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design.      
-Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer.
       \label{fig:spectra}
@@
 Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
-dipole resonance.
-More detailed analysis shows that we have {\em excited several electric dipole resonances} with close resonance frequencies within our multilayer structure.
-Indeed, if we plot a superposition of the squares of the absolute values of the Mie coefficients, which characterize energy stored in each layer, we find that we excite resonances in all three layers, and they are slightly offset as shown in Fig.~\ref{fig:spectra} (d).
-Combined effect of these resonances produces the flat and relatively broadband electric resonance response shown in Fig.~\ref{fig:spectra} (c).
+dipole resonance.  It is related to the overlay of dipole contribution
+from the inner layers and outer shell.
 
@@
 field in Fig.~\ref{fig:field} for two designs: with the best
-efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
-Using semi-transparent white curves we also plot streamlines of the
-Poynting vector which characterize energy flow.  For the effective
-design of the absorber, the power from a large cross-sectional area
-flows into the particle.  In case of superabsorption regime, we
-observe the formation of vortices in the power flow, which make
-absorption more efficient as the electromagnetic energy propagates
-several times through the absorbing materials.  The reason for the
-smaller overall absorption efficiency of a superabsorbing design is
-obvious: spatial distribution of the electric field is not uniform
-inside the particle and the share of the volume with high absorption
-rate in the vortices does not compensate low absorption efficiency in
-the regions with small electric field (absorbed power is expressed as
-$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)
+efficiency at $R=36$~nm and in a superabsorbing design with
+$R=63$~nm.  Using semi-transparent white curves we also plot
+streamlines of the Poynting vector which characterize energy flow.
+For the effective design of the absorber, the power from a large
+cross-sectional area flows into the particle.  In case of
+superabsorption regime, we observe the formation of vortices in the
+power flow, which make absorption more efficient as the
+electromagnetic energy propagates several times through the absorbing
+materials.  The reason for the smaller overall absorption efficiency
+of a superabsorbing design is obvious: spatial distribution of the
+electric field is not uniform inside the particle and the share of the
+volume with high absorption rate in the vortices does not compensate low
+absorption efficiency in the regions with small electric field (absorbed power is expressed as $P_{\rm abs}=\frac{1}{2}\int\sigma
+\left|E\right|^2dx\,dy\,dz$)
 
-In conclusion, we introduce and study the effect of superabsorption,
-when the absorption cross-section of the nanoparticle can reach the
-theoretical limit for several modes at the same frequency. This
-becomes possible when several resonant modes of the structure overlap
-at the same frequency, and this regime can be achieved in multilayer
-nanoparticles. Moreover, quite unexpectedly we find that the most
-efficient absorbers, which are characterized by enhanced absorption
-efficiencies, are smaller nanoparticles working in a single mode
-regime. We present their spectral characteristics and field structure.
-The stochastic algorithm utilized in our approach is very generic and
-the optimization can be repeated for any desired wavelength or
-wavelength range.  As a result, one can design spectrally-selective
-absorbers or broadband absorbers with almost arbitrary prescribed
-properties.  It is interesting to note that a similar conclusion was
-made by Miller et al.~\cite{Miller-2014} for extinction of arbitrary
-particles: small size with only dipole response is preferable for
-geometric volume normalized efficiency.
+In conclusion, we introduce and study the effect of superabsorption, when the absorption cross-section of the
+nanoparticle can reach the theoretical limit for several modes at the
+same frequency. This becomes possible when several resonant modes of
+the structure overlap at the same frequency, and this regime can be
+achieved in multilayer nanoparticles. Moreover, quite unexpectedly we
+find that the most efficient absorbers, which are characterized by
+enhanced absorption efficiencies, are smaller nanoparticles working in
+a single mode regime. We present their spectral characteristics and
+field structure.  The stochastic algorithm utilized in our approach is
+very generic and the optimization can be repeated for any desired
+wavelength or wavelength range.  As a result, one can design
+spectrally-selective absorbers or broadband absorbers with almost
+arbitrary prescribed properties.  It is interesting to note that a
+similar conclusion was made by Miller et al.~\cite{Miller-2014} for
+extinction of arbitrary particles: small size with only dipole
+response is preferable for geometric volume normalized efficiency.
 
 \begin{acknowledgments}
-  Thanks to David A. Powell for his contribution to the analysis of
-  the spectrum feature.  AEM and IVS would like to acknowledge support
-  from the Australian Research Council through Future Fellow and
-  Discovery project schemes. KSL and PAB would like to thank the
-  Ministry of Education and Science of the Russian Federation and
-  Government of the Russian Federation (Grant 074-U01) for the
-  financial support.
+  AEM and IVS would like to acknowledge support from the Australian
+  Research Council through Future Fellow and Discovery project
+  schemes. KSL and PAB would like to thank the Ministry of Education and
+  Science of the Russian Federation  and Government of the
+  Russian Federation (Grant 074-U01) for the financial support.
 \end{acknowledgments}

### 2015-07-22 scripts/compile-dvi.sh

@@ -1,0 +1,31 @@
+#!/bin/bash
+echo Clean up...
+#rm -f 2014-Ladutenko-Mie-optimization.bbl
+for filename in `ls *.tex`; do
+file=${filename::-4}
+echo $file
+
+rm -f *.bbl
+rm -f *Notes.bib
+rm -f *.aux
+rm -f *.blg
+rm -f *.log
+rm -f *.out
+rm -f *.dvi
+
+
+latex  -interaction=nonstopmode "\input" $file.tex
+bibtex $file
+latex  -interaction=nonstopmode "\input" $file.tex
+latex  -interaction=nonstopmode "\input" $file.tex
+echo
+echo
+echo Check result for problems - they may be skiped during compilation
+
+rm -f *Notes.bib
+rm -f *.aux
+rm -f *.blg
+rm -f *.log
+rm -f *.out
+#rm -f 2014-Ladutenko-Mie-optimization.bbl
+done

### 2015-07-22 scripts/compile-pdf.sh

@@ -1,0 +1,31 @@
+#!/bin/bash
+echo Clean up...
+#rm -f 2014-Ladutenko-Mie-optimization.bbl
+for filename in `ls *.tex`; do
+file=${filename::-4}
+echo $file
+
+rm -f *.bbl
+rm -f *Notes.bib
+rm -f *.aux
+rm -f *.blg
+rm -f *.log
+rm -f *.out
+rm -f $file.pdf
+
+
+pdflatex  -interaction=nonstopmode "\input" $file.tex
+bibtex $file
+pdflatex  -interaction=nonstopmode "\input" $file.tex
+pdflatex  -interaction=nonstopmode "\input" $file.tex
+echo
+echo
+echo Check result for problems - they may be skiped during compilation
+
+rm -f *Notes.bib
+rm -f *.aux
+rm -f *.blg
+rm -f *.log
+rm -f *.out
+#rm -f 2014-Ladutenko-Mie-optimization.bbl
+done

### 2015-07-22 scripts/generate-flat-submission.py

@@ -1,0 +1,71 @@
+#!/usr/bin/env python
+import sys,os,shutil,glob,subprocess
+from argparse import ArgumentParser
+# Configure Argument Parser section
+def is_valid_file(parser, arg):
+    if not os.path.exists(arg):
+        parser.error("The file %s does not exist!" % arg)
+    else:
+        return open(arg, 'r')  # return an open file handle
+parser = ArgumentParser(description="Prepare flat submission folder from LaTeX input")
+parser.add_argument("fileHandle",
+                    help="Main LaTeX file", metavar="FILE",
+                    type=lambda x: is_valid_file(parser, x))
+args = parser.parse_args()
+# Create list of graphics files to copy
+all_included_files_with_paths = []
+for line in args.fileHandle:
+    if 'includegraphics' in line:
+        if '%' in line and line.find('%') < line.find('includegraphics'):
+            continue
+        all_included_files_with_paths.append(line.split("{",1)[1].split("}",1)[0]);
+# Create submission path
+path = os.getcwd()
+path_submission = os.path.join(path, 'submission')
+if os.path.exists(path_submission):
+    sys.exit("Sumbission dir found! Remove it and rerun script!")
+os.mkdir(path_submission)
+# Copy all files needed
+for file in all_included_files_with_paths:
+    shutil.copy(os.path.join(path, file+'.pdf'), path_submission)
+for fname in glob.iglob('*.bst'):
+    shutil.copy(fname, path_submission)
+for fname in glob.iglob('*.rtx'):
+    shutil.copy(fname, path_submission)
+for fname in glob.iglob('*.sty'):
+    shutil.copy(fname, path_submission)
+for fname in glob.iglob('*.cls'):
+    shutil.copy(fname, path_submission)
+shutil.copy(os.path.join(path,args.fileHandle.name)[:-3]+'bib', path_submission)
+for fname in glob.iglob('../scripts/compile*.sh'):
+    shutil.copy(fname, path_submission)
+
+new_main_file = os.path.join(path_submission, args.fileHandle.name)
+with open(new_main_file, 'w') as file_:
+    args.fileHandle.seek(0)
+    for line in args.fileHandle:
+        if ('\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%\n'==line) or\
+           ('filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}\n'==line) or\
[…]

### 2015-07-22 scripts/generate-report.py

@@ -1,0 +1,115 @@
+#!/usr/bin/env python
+# -*- coding: UTF-8 -*-
+#
+#    Copyright (C) 2015  Konstantin Ladutenko <kostyfisik@gmail.com>
+#
+#    This program is free software: you can redistribute it and/or modify
+#    it under the terms of the GNU General Public License as published by
+#    the Free Software Foundation, either version 3 of the License, or
+#    (at your option) any later version.
+#
+#    This program is distributed in the hope that it will be useful,
+#    but WITHOUT ANY WARRANTY; without even the implied warranty of
+#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#    GNU General Public License for more details.
+#
+#    You should have received a copy of the GNU General Public License
+#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+import sys,os,shutil,glob,subprocess
+path = os.getcwd()
+path_fig = os.path.join(path, 'fig')
+print(path_fig)
+os.chdir(path_fig)
+files = []
+for fname in glob.iglob('*'):
+    files.append(fname)
+files.sort()
+print(files)
+
+begin_document = """%%\\documentclass[fullscreen=true, handout]{beamer}
+\\documentclass[fullscreen=true]{beamer}
+\\usetheme[secheader]{Boadilla}
+%%\\usetheme{Boadilla}
+%%\\usetheme[height=7mm]{Rochester} 
+%%\\useinnertheme{rounded}
+ \\usecolortheme{seahorse}
+%% \\usecolortheme{whale}
+%% \\usecolortheme{rose}
+%%\\setbeamertemplate{navigation symbols}{\\insertframenavigationsymbol}
+%% or
+\\beamertemplatenavigationsymbolsempty
+%% \\setbeamertemplate[info line]{footline} %%Не работает
+%% {\\quad\\strut\\insertsection
+%% \\hfill\\insertframenumber/\\inserttotalframenumber\\strut\\quad} 
+\\usepackage[utf8]{inputenc}
+\\usepackage[T1]{fontenc} %%apt-get install cm-super
+%%\\usepackage[english, russian]{babel}
+\\usepackage[english]{babel}
+\\emergencystretch=35pt %%Чтобы нe было строчек, вылезших на поля
+\\usepackage{ragged2e} %% to use \\justifying
+\\usepackage{amsmath}
+\\usepackage{booktabs}
[…]

### 2015-07-23 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py
additional paragraph about Alu paper

@@ -141,17 +141,17 @@ def GetEpsilon(WLs, fname):
 ###############################################################################
 def save_spectra(fname, from_WL, to_WL, total_points, design, extra_width):
     WLs = np.linspace(from_WL, to_WL, total_points)
-    # epsSi = GetEpsilon(WLs, "Si-int.txt")
-    # epsAg = GetEpsilon(WLs, "Ag-int.txt")    
-    # data = calc(design, extra_width, WLs[0], epsSi[0,1], epsAg[0,1])
-    # for i in xrange(len(WLs)):
-    #     data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi[i,1], epsAg[i,1])))
-    epsSi = 18.4631066585 + 0.6259727805j
-    epsAg = -8.5014154589 + 0.7585845411j
-    WL = 500
-    data = calc(design, extra_width, from_WL, epsSi, epsAg)
+    epsSi = GetEpsilon(WLs, "Si-int.txt")
+    epsAg = GetEpsilon(WLs, "Ag-int.txt")    
+    data = calc(design, extra_width, WLs[0], epsSi[0,1], epsAg[0,1])
     for i in xrange(len(WLs)):
-        data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi, epsAg)))
+        data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi[i,1], epsAg[i,1])))
+    # epsSi = 18.4631066585 + 0.6259727805j
+    # epsAg = -8.5014154589 + 0.7585845411j
+    # WL = 500
+    # data = calc(design, extra_width, from_WL, epsSi, epsAg)
+    # for i in xrange(len(WLs)):
+    #     data = np.vstack((data,calc(design, extra_width, WLs[i], epsSi, epsAg)))
     
     data = data[1:]
     np.savetxt(fname,data)
@@ -374,7 +374,7 @@ for i in xrange(1):
     fig.subplots_adjust(hspace=.05)
     plt.minorticks_off()
     fname="2015-04-01-SiAgSi-ab-spectra4"
-    plt.savefig(fname+".pdf",pad_inches=0.02, bbox_inches='tight')
+    plt.savefig(fname+".eps",pad_inches=0.02, bbox_inches='tight')
     #plt.draw()
 
     #plt.show()

### 2015-07-23 2015-Ladutenko-Qabs/data/plot-SiAgSi-overview.py

@@ -141,7 +141,7 @@ axs[Design].locator_params(axis='x',nbins=5)
 
 fig.subplots_adjust(hspace=.05)
 
-plt.savefig(fname+".pdf",pad_inches=0.02, bbox_inches='tight')
+plt.savefig(fname+".eps",pad_inches=0.02, bbox_inches='tight')
 #plt.draw()
 
 #plt.show()

### 2015-07-28 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya.tex

@@
-%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
 %\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for double-spaced preprint
-
-%Phys Rev B
-%Letter or rapid communication - 3500 words
-%\documentclass[prb,groupedaddress,reprint]{revtex4-1}
-%APL
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}
-%\documentclass[aps,prl,reprint]{revtex4-1}
-%\documentclass[aip,jap,reprint]{revtex4-1}
 \usepackage[english]{babel}
 \usepackage{graphicx}% Include figure files
-\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%
-filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}
-\usepackage[figure,table]{hypcap} %links should lead to the begining
-                                %of figure or table...
+\begin{document}
+\title{Superabsorption of light by nanoparticles}
 
-\begin{document} %Max size in pdf for APL - 4 print pages
-
-\title{Super absorption and efficient absorption of light by spherical
-  nanoparticles}
-
-\author{Konstantin Ladutenko} \email[e-mail: ]{fisik2000@mail.ru}
-\affiliation{ITMO University, 49 Kronverskii Ave., St.~Petersburg
-  197101, Russian Federation\\}
+% Proposed reviewers: Anatoly Zayats, Andrea Alu, Sergei Bozhevolnyi
+% Prof. García de Abajo (http://garciadeabajos-group.icfo.es/) Andrea
+% Alu.
+\author{Konstantin Ladutenko} \email[e-mail:
+]{k.ladutenko@metalab.ifmo.ru} \affiliation{ITMO University, 49
+  Kronverskii Ave., St.~Petersburg 197101, Russian Federation}
 
@@
 
+\author{Pavel Belov} \affiliation{ITMO University, 49 Kronverskii
+  Ave., St.~Petersburg 197101, Russian Federation}
+
 \author{Ovidio Pe\~{n}a-Rodr\'{i}guez} \affiliation{Instituto de
-  Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid,\\
-  Jos\'{e} Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain}
+  Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid, Jos\'{e}
+  Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain}
 
-% \author{Pavel Belov} \affiliation{ITMO University, 49 Kronverskii
-% Ave., St.~Petersburg 197101, Russian Federation\\}
 \author{Ali Mirzaei} \author{Andrey Miroshnichenko} \author{Ilya
@@
 \date{\today}
-% APL 250 words! Phys Rev B less then 500 words, about
-% 5% ot total paper length
-% emacs M-x count-words
-
 \begin{abstract}
-  Spherical subwavelength nanoparticles have a fundamental limit as to
-  how much light they can absorb. This limit is based on the
-  assumption that only one mode is excited in the nanoparticle. Using
-  genetic algorithm, we design multi-layer nanoparticles, in which we
-  can make several resonant modes overlap at the same frequency, thus
-  significantly beating the theoretical limit of absorption, and we
-  call this super-absorption. We further introduce the efficiency of
-  the absorption for a nanoparticle, which is absorption normalized by
-  the physical size of the particle, and show that efficient absorbers
-  are not always operating in super-absorbing regime.
+  Nanoparticles have a fundamental limit as to how much light they can
+  absorb. This limit is based on the finite number of modes excited in
+  the nanoparticle at a given wavelength and maximum absorption
+  capacity per mode. The enhanced absorption can be achieved when each
+  mode supported by the nanopartice absorbs light up to the maximum
+  capacity. Using stochastic optimization algorithm, we design
+  multilayer nanoparticles, in which we can make several resonant
+  modes overlap at the same frequency resulting in {\it
+    superabsorption}.  We further introduce the {\it efficiency of the
+    absorption} for a nanoparticle, which is the absorption normalized
+  by the physical size of the particle, and show that efficient
+  absorbers are not always operating in the superabsorbing regime.
 \end{abstract}
 
-\pacs% insert suggested PACS numbers in braces on next line
+\pacs% insert suggested PACS numbers in braces on next line,
+% not more that 4
 {41.20.Jb 42.25.Bs 02.60.Pn 02.70.-c}
-% 41.20.Jb Electromagnetic wave propagation 42.25.Bs Wave propagation,
-% transmission and absorption
-%% 42.25.Fx Diffraction and scattering
-% 02.60.Pn Numerical optimization 02.70.-c Computational techniques;
-% simulations
+% 41.20.Jb Electromagnetic wave propagation
+%% 42.25.Bs Wave propagation, transmission and absorption 02.60.Pn
+%% Numerical optimization
+% 02.70.-c Computational techniques; simulations
 
@@
 
-Mie theory~\cite{Mie-1908}, which is over 100 years old now, describes
+Mie theory~\cite{Mie-1908}, which is over 100 years old, describes
 interaction of electromagnetic waves with spherical particles. Mie
@@
 theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
-study the multilayered spherical
+it to the study of multilayer spherical
 particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
 various applications in cancer treatment~\cite{Zhang-2010,
-  Hirsch-2003} and medical diagnostics~\cite{Allain-2002},
+  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
 cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
-plasmonic~\cite{Martin-2013, Alu-2005} devices, study on thermal
-properties of insulating material~\cite{Xie-2013}, as well as for
-improving solar cells performance~\cite{Kameya-2011,Mann-2011}, and so
-on.
+plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of
+thermal properties of insulating materials~\cite{Xie-2013}, as well as
+for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.
 
 The scattering properties of multilayer cylinders and spheres was
-studied in great detail by Fan~et~al.~\cite{Fan-2010,Fan-2011}.  In these
-works authors introduced the concept of a super scattering, when the
-scattering cross-section of a multilayer particle exceeds that of a
-homogeneous particle of the same size in the so-called single-channel
-limit. The super scattering appears when we design a multilayer
-structure so that several modes become nearly degenerate, i.e. their
-resonance frequencies coincide or get close to each other. In a
-homogeneous particle, the resonances appear at different frequencies,
-and there is no design freedom for a fixed geometry of the structure
-to make these resonances overlap, and this limits the achievable
-scattering cross-section.
+studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
+these works the authors introduced the concept of superscattering,
+when scattering cross-section of a multilayer particle exceeds that of
+a homogeneous particle of the same size in the so-called
+single-channel limit. Superscattering appears when a multilayer
+structure has several nearly degenerate modes, i.e. their resonance
+frequencies coincide or are close to each other. In a homogeneous
+particle, resonances appear at different frequencies, and there is no
+design freedom to make these resonances overlap, and this limits the
+achievable scattering cross-section.
 
 Similar fundamental limitations exist for the absorbing properties of
-sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has derived a
-theoretical limit of a maximum absorption cross-section (ACS) value
-for a single channel, i.e., when only one mode of the sphere is
-excited.  As a result the absorption coefficients $\tilde{a}_n= {\rm
-  Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} - |b_n|^2 $
-become limited by $1/4$, here $a_n$ and $b_n$ are scattering
-coefficient as defined in Mie theory~\cite{Bohren-1983}.
+subwavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
+derived a theoretical limit of a maximum absorption cross-section
+(ACS) value for a single channel, i.e., when only one mode of a sphere
+is excited.  As a result, the absorption coefficients $\tilde{a}_n=
+{\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} -
+|b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
+coefficient as defined within the Mie theory~\cite{Bohren-1983} for
+expansion of the scattered electric field:
+$$ 
+{\rm \mathbf{E}}_s = \sum_{n=1}^{\infty} E_n \left( i a_n {\rm
+    \mathbf{N}}_{e1n}^{(3)} - b_n{\rm\mathbf{M}_{o1n}^{(3)}} \right),
+$$
+where ${\rm \mathbf{N}}_{e1n}^{(3)}$ and ${\rm\mathbf{M}_{o1n}^{(3)}}$
+are corresponding vector spherical harmonics,
+$E_n=i^nE_0(2n+1)/n(n+1)$, $n$ is the angular momentum of the mode,
+and $E_0$ is the amplitude of the incident field.
 
-To overcome these limitations, we employ similar approach for
-enhancing absorption cross-section~\cite{Fan-2011}. In particular, we
-propose to use the multi-layer structures, and by means of genetic
-algorithm we optimize the ACS of these particles. We analyze the
-absorption cross-section of these particles, and present the
-super-absorption regime. We further introduce the absorption
-efficiency, which is the ACS normalized to the geometric cross-section
-of the particles. Here we show that there is a strong counter-play
-between the increased absorption for larger particles vs size for
-smaller particles, and quite remarkably we find that the most {\em
-  efficient} absorption can be achieved in a single channel limit for
-small particles.
+To overcome these limitations, we employ similar approach to the one
+used for enhancing scattering cross-section~\cite{Fan-2011}. In
+particular, we propose to use the multilayer structures, and by means
+of stochastic optimization algorithm~\cite{Jingqiao-JADE-2009} we
+optimize the ACS of such nanoparticles. We analyze the absorption
+cross-section of these particles, and present the superabsorption
+regime. We further introduce the absorption efficiency, which is the
+ACS normalized to the geometric cross-section of particles. Here we
+show that there is a strong counterplay between the increased
+absorption for larger particles vs size for smaller particles, and
+quite remarkably we find that the most {\em efficient} absorption can
+be achieved in a single channel limit for small particles.
 
-We start our analyses by considering the triple layered $Si/Ag/Si$
-spherical particle illuminated with a plane wave~(Fig. TODO ). In what
-follows we describe the materials using experimentally measured
-parameters from the Ref.~\cite{palik-1997}.  To optimize the thickness of each
-layer we implemented~\cite{JADE-web} an adaptive differential
-evolution algorithm~\cite{Storn-DE-first-1997}, which is called
-JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
-optimization algorithm are published previously in
-Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
-Scattnlay~\cite{Pena-scattnlay-2009,Scattnlay-web} software, whose results were
-verified with a number of other implementations of the Mie solutions
-and with a commercially available software such as CST Microwave
-studio~\cite{CST-web} and Comsol Multiphysics~\cite{Comsol-web}.
-
-It is obvious that in general, a bigger particle will have a bigger
-absorption cross-section, so sphere with the diameter of 1 cm will
-absorb more light than any sphere at the nanoscale. Therefore, we use
-absorption efficiency $Q_{\rm abs}=C_{\rm abs}/2\pi R_{\rm total}^2$,
-where $R_{\rm total}$ is the outer radius of the particle and $C_{\rm
-  abs}$ is the absorption cross-section. We maximize absorption
-efficiency at a fixed wavelength of incident light (we have chosen
-$\lambda=500$~nm).
+Another approach for an ideal absorber is given in the recent work by
+Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only dipole
+approximation, and the final result is very close to the dipole limit
+predicted by Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
+corresponds to the single mode limit.  At the same time, Grigoriev et
+al.~\cite{Grigoriev-2015} also provide an equation to design a
+core-shell structure from given materials. However, in the case of
+$Si$ core and $Ag$ shell materials and sizes taken from the best
+design obtained in the present paper, their equation gives a complex
+value for the core material filling factor, which cannot be achieved
+in experimental realisations.
 
@@
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
-    \caption{ Results of the optimization of the absorption efficiency
+    \includegraphics[width=0.4\textwidth]{fig/Fig1}%
+    \caption{(color online) Shematic view of the simulated $Si/Ag/Si$ particle. 
+      \label{fig:geom}
+    }%
+  }
+\end{figure}
+
+The proposed approach can be applied to arbitrary combination of
+materials, but to be more specific in what follows we consider
+dielectric-metal-dielectric triple-layer $Si/Ag/Si$ spherical particle
+illuminated by a plane wave schematically shown in
+Fig.~\ref{fig:geom}. In what follows we describe the materials using
+experimentally measured parameters from Ref.~\cite{palik-1997}, and,
+e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
+$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
+layer we implemented~\cite{JADE-web} an adaptive differential
+evolution algorithm~\cite{Storn-DE-first-1997}, which is called
+JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
+optimization algorithm were published previously in
+Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
+Scattnlay software~\cite{Pena-scattnlay-2009,Scattnlay-web}, whose
+results are verified by a number of other implementations of the Mie
+solutions and by commercially available software including CST
+Microwave studio~\cite{CST-web} and Comsol
+Multiphysics~\cite{Comsol-web}.
+
+It is a common understanding that, in general, a larger particle has a
+larger absorption cross-section, so sphere with the diameter of 1 cm
+absorbs more light than any nanoscale sphere. Therefore, it is
+practical to employ {\em the absorption efficiency} $Q_{\rm
+  abs}=C_{\rm abs}/\pi R^2$, where $R$ is the outer radius of the
+particle and $C_{\rm abs}$ is the absorption cross-section.
+
+\begin{figure}
+  \center{
+    % Use pdfcrop to remove white margins
+    \includegraphics[width=0.45\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
+    \caption{(color online) Results of optimization of the absorption efficiency
       for the fixed wavelength of 500~nm. (a) Absorption efficiency
-      with the best value achieved at the particle radius of 36~nm and
-      Ag/Si design (zero sized core). Dashed lines show theoretical
+      with the best value achieved for the particle of the double-layer Ag/Si design of the radius of 36~nm. Dashed lines show theoretical
       limits for the first channel and second channel
-      absorption. Second and third peaks in the absorption efficiency
+      absorption. The second and third peaks in the absorption efficiency
       curve exceed the theoretical limit for the second mode
-      absorption at R=63~nm and R=81~nm. (b) Mie absorption
+      absorption at $R=63$~nm and $R=81$~nm. Local maxima of
+      absorption efficiency are additionally marked with arrows. (b) Mie absorption
       coefficients for individual excited modes of the optimized
@@
       particle radius below 46~nm the optimizer converges to
-      the two-layer structure, when core size vanishes, and the
-      optimum design is a bi-layer $Ag/Si$ particle.
-
+      a bi-layer structure, when core size vanishes, and the
+      optimum design is a $Ag/Si$ particle. 
       \label{fig:overview}
@@
 radii of internal cores, whereas the target function is the absorption
-efficiency.  We show the results of our genetic optimization algorithm
-in Fig.~\ref{fig:overview}a.  Dashed lines show theoretical absorption
+efficiency. We maximize absorption efficiency at a fixed wavelength of
+the incident light (we have chosen $\lambda=500$~nm). We show the
+results of our stochastic optimization algorithm in
+Fig.~\ref{fig:overview}~(a).  Dashed lines show theoretical absorption
 limit of a dipole ($n=1$) and a quadrupole ($n=2$)
-resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm abs\
-  max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi R_{\rm
-  total}/\lambda$, and $n$ is an angular momentum of the
-mode. Following Ref.~\cite{Fan-2011}, where authors introduce super
-scattering for spherical particles, here we we introduce
-super-absorption, when the ACS is larger than the theoretical limit
-for absorption by the mode with highest excited angular momentum
-$n$. In our parameter space we have just modes up to the quadrupole
-excited ($n=2$), and in order to get a super-absorption our efficiency
-should be higher than that of a quadrupole. We clearly see this
-super-absorption at $R_{\rm total}>60$~nm, in Fig.~\ref{fig:overview}
-(a).
+resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm
+  abs\ max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi
+R/\lambda$, and $n$ is the angular momentum of the mode. Following
+Ref.~\cite{Fan-2011}, where the authors introduce superscattering for
+spherical particles, here we introduce superabsorption regime, when
+{\em the ACS is larger than the theoretical limit for absorption by
+  strongly excited mode with the highest angular momentum $n$}. In our
+parameter space we have modes up to the quadrupole excited ($n=2$),
+and in order to get superabsorption our efficiency should be higher
+than that of a quadrupole. We clearly see this superabsorption regime
+at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).
 
-In Fig.~\ref{fig:overview}b we present the values of Mie absorption
+In Fig.~\ref{fig:overview}~(b) we present the values of Mie absorption
 coefficients for individual excited modes in the structure, while
@@
 while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
-quadrupole. For small particles, as expected, the absorption is
-dominated by an electric dipole $\tilde{a}_1$.  At $R_{\rm total} >
-56.6$~nm the optimization procedure finds that the designs with both
-electric and magnetic dipoles have larger ACS, than the structure with
-only the electric dipole excited. This is why the curves in
-Figs.~\ref{fig:overview} (b,c) experience the discontinuity. We also
-note that there is a very narrow range of particle sizes, between
-80.7~nm and 82.1~nm, where our analyses finds that the design
-supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
-$\tilde{b}_2$, has larger ACS, and this explains two more
-discontinuities of the curves at the respective size values.
+quadrupole. For small particles, as expected, absorption is dominated
+by electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the optimization
+procedure finds that the designs with both electric and magnetic
+dipoles have larger ACS than the structure with only the electric
+dipole excited. This is why the curves in
+Figs.~\ref{fig:overview}~(b,c) experience the discontinuity. Quite
+remarkably, in this regime, {\em the combined absorption of the
+  electric and magnetic dipoles exceeds the theoretical limit for the
+  higher order (quadrupole) mode.}  We also note that there is a very
+narrow range of particle sizes, between 80.7~nm and 82.1~nm, where our
+analysis finds that the design supporting electric dipole
+$\tilde{a}_1$ and magnetic quadrupole $\tilde{b}_2$ has larger ACS,
+and this explains two more discontinuities of the curves at the
+respective size values.
 
-Fig.~\ref{fig:overview} (c) shows optimized sizes of the layers inside
-the multi-layer structure. It reveals quite a curious result, that the
+Fig.~\ref{fig:overview}~(c) shows optimized sizes of layers inside a
+multilayer structure. It reveals quite a curious result, that the
 dipole branch (i.e. for particle radii below 56.6~nm) has two
-parts. For $R_{\rm total}<46$~nm the best absorber has just two
-layers, as the radius of the core of the three-layer structure
-vanishes, and the particle reduces to $Ag/Si$ core-shell structure.
-At $R_{\rm total}=46$ dipole channel becomes practically
-undistinguishable from the theoretical limit (it becomes
+parts. For $R<46$~nm the best absorber has just two layers, as the
+radius of the core of a triple-layer structure vanishes, and the
+particle reduces to $Ag/Si$ core-shell structure.  At $R=46$~nm dipole
+channel reaches its theoretical limit (it becomes
 $\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
 inner $Si$ layer in order to keep $\tilde{a}_1$ near the theoretical
-limit as the $R_{\rm total}$ increases.  As a side effect, the
-quadrupole contribution $\tilde{a}_2$ appears, however, it does not
-help to reach super-absorption limit $n=2$.
+limit as the $R$ increases.  As a side effect, the quadrupole
+contribution $\tilde{a}_2$ appears; however, it does not help to reach
+superabsorption limit for $n=2$.
 
-Remarkably, the absolute maximum absorption efficiency is not reached
-within the super-absorption regime. Figure~\ref{fig:overview} shows
-that the maximum efficiency is reached for small particle size, and
-the ACS is still well below the single channel limit. It appears that
-the $Ag/Si$ core-shell nanoparticle, with the total radii of
-approximately 36~nm is the most efficient absorbing in the considered
-structure, which ACS reaching values over 5 times the physical
-cross-section area of the particle.  From practical point of view it
-is quite important that the maximum can be reached in a bi-layer
-structure, instead of a triple-layer, and it should be easier and
-cheaper to produce.
+Remarkably, the absolute maximum {\em absorption efficiency} is not
+reached within the superabsorption regime. Figure~\ref{fig:overview}
+shows that the maximum efficiency is achieved for small particle size,
+and the ACS is still well below the single channel limit. It appears
+that the $Ag/Si$ core-shell nanoparticle with the total radii of
+approximately 36~nm is the most efficient absorber among the
+considered structures, whose ACS reaches values {\em over 5 times the
+  physical cross-section area of the particle}.  From a practical
+point of view, it is quite important that the maximum can be reached
+in a bi-layer structure, instead of a triple-layer, since it should be
+easier and cheaper to fabricate.
 
@@
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
-    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)super absorption design.      
+    \includegraphics[width=0.45\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra4}%
+    \caption{(color online) Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design.
+Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer.
       \label{fig:spectra}
@@
 \end{figure}
-%
-To study spectral properties of the structures with large ACS which we
+To study spectral properties of structures with large ACS which we
 obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
 different cases for designs that correspond to local maxima of $Q_{\rm
-  abs}$ shown in Fig.~\ref{fig:overview} (a).  As expected, the design
-corresponding to the maximum absorption efficiency at R=36~nm has a
+  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
+corresponding to the maximum absorption efficiency at $R=36$~nm has a
 single electric dipole resonance centered at the target wavelength
-$\lambda=500$~nm. Spectra of designs with maxima at R=63~nm and
-R=81~nm have a signature of the super absorption, i.e. there is an
+$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
+$R=81$~nm have a signature of the superabsorption, i.e. there is an
 overlap of several resonances.  We note that these structures have
 additional absorption resonances, but they are located far from the
-wavelength of interest.
-
-A noticeable feature of Fig.~\ref{fig:spectra} (c) is an almost flat
-top of the electric dipole resonance. (TODO add some explanation, why
-it flat? Any ideas?  - not really, maybe there are two different
-dipole "types", and we see their interference?)
+wavelength of interest.  A noticeable feature of
+Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
+dipole resonance. More detailed analysis shows that we have {\em
+  excited several electric dipole resonances} with close resonance
+frequencies within our multilayer structure. Indeed, if we plot a
+superposition of the squares of the absolute values of the Mie
+coefficients, which characterize electric energy density stored in
+each layer, we find that we excite resonances in all three layers, and
+they are slightly offset as shown in
+Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
+produces the flat and relatively broadband electric resonance response
+shown in Fig.~\ref{fig:spectra}~(c).
 
@@
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.4\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
-    \caption{ Amplitude of electric field for R=36 nm (a,c) and
-      ``super'' (b,d) designs in E-k  (a-b) and H-k (c-d) planes. 
+    \includegraphics[width=0.47\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs}%
+    \caption{(color online) Amplitude of electric field for $R=36$~nm (a,c) and
+      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
+      planes normalized to incident wave.  White curves show the
+      energy flow streamlines, plane wave comes from the left.
       \label{fig:field}
@@
 \end{figure}
-%
 Finally, we present distribution of the amplitude of the electric
 field in Fig.~\ref{fig:field} for two designs: with the best
-efficiency at $R=36$~nm and in a super-absorbing design with
-$R=63$~nm.  We set different scale for these two designs so that black
-circles that denote outer boundary are plotted to be the same size.
-We also plot streamlines of the Poynting vector which characterize
-energy flow. For the effective design of the absorber, the power from
-a large cross-sectional area flows into the particle.  In case of
-super-absorption regime, we observe power flow vortices, which make
-absorbtion more efficient as the electromagnetic energy propagates
-several times through the absorbing materials.
+efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
+Using semi-transparent white curves we also plot streamlines of the
+Poynting vector which characterize energy flow.  For the effective
+design of the absorber, the power from a large cross-sectional area
+flows into the particle.  In case of superabsorption regime, we
+observe the formation of vortices in the power flow, which make
+absorption more efficient as the electromagnetic energy propagates
+several times through the absorbing materials.  The reason for the
+smaller overall absorption efficiency of a superabsorbing design is
+obvious: spatial distribution of the electric field is not uniform
+inside the particle and the share of the volume with high absorption
+rate in the vortices does not compensate low absorption efficiency in
+the regions with small electric field (absorbed power is expressed as
+$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)
 
-In conclusion, we find the effect of the super-absorption, when the
-absorption cross-section of the nanoparticle can exceed the
-theoretical limit for the absorption by the highest excited mode. This
-occur when several resonance modes of the structure overlap at the
-same frequency. We introduce efficiency of the absorption as an
-absorption cross-section divided by a geometric cross-section of the
-particle, and quite unexpectedly we find that the most efficient
-absorbers are smaller nanoparticles working in a single mode
+The stochastic algorithm utilized in our approach is very generic and
+the optimization can be repeated for any desired wavelength or
+wavelength range.  As a result, one can design spectrally-selective
+absorbers or broadband absorbers with almost arbitrary prescribed
+properties. We note, that using this algorithm, one can optimize not
+only absorbtion efficiency, but also other parameters that may be
+desired for some applications. As an example we reproduce some of the
+results from the work of Estakhri and Al\`u~\cite{Alu-2014}, where
+authors aim to design absorbers with small scattering cross-section,
+and we provide a number of new optimized designs. The efficiency in
+the Ref.~\cite{Alu-2014} is defined as the ACS normalized to
+scattering cross-section. Initially, we set the total value of the
+absorbed power with cross-section of $\alpha_{\rm
+  abs}=\frac{3\lambda^2}{8\pi}$ and keep the outer radius of the
+particle fixed. In this case the optimization gives a result similar
+to the structure with contributing harmonics TM${_1}$ and TE$_1$ from
+Ref~\cite{Alu-2014}.  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
+-10.37+ i0.35$, and $\epsilon_3=8.4+i2.33$ as material parameters we
+obtained radii $\{a_{c1},a_{c2},a_3\}=\{0.142,0.166,0.194\}\lambda$
+and scattering-normalized absorption efficiency $\eta_{\rm
+  abs}^{(\alpha)} =7.65$ which corresponds to $\eta_{\rm
+  abs}^{(\alpha)} =7.1$ from the original work~\cite{Alu-2014}.
+However, if we set the optimizer to keep high level of absoption
+efficiency $Q_{\rm abs} \approx 5$ the particle becomes much smaller
+and the size of the outer layer vanishes
+$\{a_{c1},a_{c2}\}=\{0.00635,0.00747\}\lambda$ resulting in $\eta_{\rm
+  abs}^{(Q)} =544$.  It means that this small particle still absorbs
+five times its phisical size with a very large scattering-normalized
+absorption efficiency.
+
+% Moreover, it is easy to set the optimizer to keep $\eta_{\rm abs}
+% \approx 100$ or $\eta_{\rm abs} \approx 1000$, resulting
+% $\{a_{c1},a_{c2}\}=\{0.0112,0.0131\}\lambda$, $Q_{\rm abs} = 8.65$
+% or $\{a_{c1},a_{c2}\}=\{0.0052,0.0061\}\lambda$, $Q_{\rm abs} =
+% 3.26$ respectively.
+
+In conclusion, we introduce and study the effect of superabsorption,
+when the absorption cross-section of the nanoparticle can reach the
+theoretical limit for several modes at the same frequency. This
+becomes possible when several resonant modes of the structure overlap
+at the same frequency, and this regime can be achieved in multilayer
+nanoparticles. Moreover, quite unexpectedly we find that the most
+efficient absorbers, which are characterized by enhanced absorption
+efficiencies, are smaller nanoparticles working in a single mode
 regime. We present their spectral characteristics and field structure.
+It is interesting to note that a similar conclusion was made by Miller
+et al.~\cite{Miller-2014} for extinction of arbitrary particles: small
+size with only dipole response is preferable for geometric volume
+normalized efficiency.
 
-WE NEED TO WRITE ABOUT THIS AND SOME OTHER WORKS IN THE
-INTRODUCTION. THE TOPIC IS DONE TO DEATH. It is intersting, that
-similar conclusion was made by Miller et al~[TODO Fundamental Limits
-to Extinction by Metallic Nanoparticles Phys. Rev. Lett. 112, 123903 –
-Published 26 March 2014 O. D. Miller, C. W. Hsu, M. T. H. Reid,
-W. Qiu, B. G. DeLacy, J. D. Joannopoulos, M. Soljačić, and
-S. G. Johnson] for extinction of arbitrary particles.
+\begin{acknowledgments}
+  Thanks to David A. Powell for his contribution to the analysis of
+  the spectrum feature.  AEM and IVS acknowledge the support from the
+  Australian Research Council through Future Fellow and Discovery
+  project schemes. OPR is grateful to Consejo Nacional de Ciencia y
+  Tecnolog\'{i}a (Mexico) for financing a short stay at Universidad
+  Autónoma de Puebla, Mexico.  KSL and PAB thank the Ministry of
+  Education and Science of the Russian Federation and Government of
+  the Russian Federation (Grant 074-U01) for the financial support.
+\end{acknowledgments}
 

### 2015-09-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Template for response

\documentclass[a4paper]{article}
\usepackage{a4wide}
% \usepackage{graphicx}
% \usepackage{amssymb,amsmath}
% \usepackage{booktabs}
\usepackage[english]{babel}
% \usepackage{multirow}
\usepackage{graphicx}% Include figure files
% \usepackage{color}
\emergencystretch=35pt
\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%
filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}
\usepackage[figure,table]{hypcap}

\begin{document}
\begin{center}
  Response Letter
\end{center}
Dear Editor,
\\
\\
I am writing to respond to the reviewers' critical comments on our
manuscript entitled, ``Superabsorption of light by nanoparticles''
NR-COM-08-2015-005468, which we aim for publication in Nanoscale.

I would like to thank the editor and two anonymous reviewers for their
constructive comments, which helped us to improve the
manuscript. Below, we address all comments point-by-point, discussing
the subsequent modifications.

\vspace{10pt}

\textbf{Reviewer \#1 comments}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 1. The authors claimed “Combined effect of these resonances is presented to produce the flat and relative broadband electric resonance response.” Nevertheless, the broadened absorption band is not very broad. Is there any further way to predict a broadband light absorption. For instance, a broadband absorption in the whole visible spectral range. Maybe, a possible way of using the dispersed size scale nanoparticles should be added for improving the study. 
\end{tabular}

In order to reply to this comment we run an optimization ... No changes
to the manuscript were made.

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad & 2. To achieve super-absorption behavior, it is interesting
  to know what will happen when the multilayered nanoparticles are
  closely packed as the plasmonic crystal. As reported in the previous
  papers [ACS Applied Materials \& Interfaces, 7, 4962−4968 (2015);
  Materials Letters 158, 262–265 (2015); Applied Physics Letters, 104,
  081116 (2014); Nanotechnology, 24, 155203 (2013)], the packed
  plasmonic crystals have been demonstrated to show broadband light
  coupling and confinement. Thereby, it would be interesting to show
  improved broadband light absorption based on the plasmonic crystal
  of this proposed multilayered nanoparticles. 
\end{tabular}

We totally agree with the reviewer's statement. It seems that our
manuscript was not clear enough at this point. ...  However, as we
compare final optimization results we conclude that .... To make it
clearer we rewrite this part of the manuscript as follows:

\begin{tabular}[!H]{p{0.9\textwidth}}
`` Some text''
\end{tabular}

It should be mentioned that .... No changes to the
manuscript were made.

\vspace{10pt}

\begin{minipage}{1.0\linewidth}
  \textbf{Reviewer \#2 comments}\\
  \begin{tabular}[!H]{l|p{0.9\textwidth}}
    \quad & 1.  As we can find from the manuscript, the highest
    absorption efficiency is achieved for a Si/Ag core-shell
    structure, which is not located in the super absorbing
    regime. Moreover, the authors also claimed that from practical
    aspect, the core-shell structure (not in the super absorbing
    regime) could be easier and cheaper to fabricate than three
    layered structure (in the super absorbing regime). Therefore, the
    authors should clearly clarify what are the advantages or
    significances of the super absorption nanoparticles? 
\end{tabular}
\end{minipage}

There are several points to be treated carefully when discussing...
 However, to claim this concept to be a general one ...  more simulations
should be performed.

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad &  2.      In Fig. 2, we noticed a discontinuity at ~80
  nm. The authors explain it as the design supporting electric dipole
  and magnetic quadrupole has larger ACS. However, this explanation is
  not clearly to me since it is lacking physics behind this
  phenomenon. The authors should clarify why the magnetic quadrupole
  only plays a significant role in this small wavelength range. 
\end{tabular}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 3.      In Fig. 3 (c), the authors observed a flat top of
electric dipole resonance. They attributed this flat resonance to the
excited several electric dipole resonances with close resonance
frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
considering the resonances located in outer and inner shell, the
resonance inside the core is much broader than the other two
cases. The authors should explain this broadened resonance clearly. 
\end{tabular}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 4.      Some sentences are not clear to me. For instance,
“there is a strong conterplay between the increased absorption for
larger particles vs size for smaller particles”. 
In summary, I do not think the manuscript is acceptable at its current
stage. 
\end{tabular}
\\
\vspace{10pt}
\\
Sincerely Yours,\\
On behalf of the authors,\\
Konstantin Ladutenko
\end{document}

### 2015-09-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Template for response

--- 2015-07-28 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya.tex
@@
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
-%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for double-spaced preprint
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%This is the LaTeX COMMUNICATION template for RSC journals
+%Copyright The Royal Society of Chemistry 2014
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[twoside,twocolumn,9pt]{article}
+\usepackage{extsizes}
+\usepackage[super,sort&compress,comma]{natbib} 
+\usepackage[version=3]{mhchem}
+\usepackage[left=1.5cm, right=1.5cm, top=1.785cm, bottom=2.0cm]{geometry}
+\usepackage{balance}
+\usepackage{widetext}
+\usepackage{times,mathptmx}
+\usepackage{sectsty}
+\usepackage{graphicx} 
+\usepackage{lastpage}
+\usepackage[format=plain,justification=raggedright,singlelinecheck=false,font={stretch=1.125,small,sf},labelfont=bf,labelsep=space]{caption}
+\usepackage{float}
+\usepackage{fancyhdr}
+\usepackage{fnpos}
 \usepackage[english]{babel}
-\usepackage{graphicx}% Include figure files
+\usepackage{lipsum}
+\usepackage{array}
+\usepackage{droidsans}
+\usepackage{charter}
+\usepackage[T1]{fontenc}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{setspace}
+\usepackage[compact]{titlesec}
+%%%Please don't disable any packages in the preamble, as this may cause the template to display incorrectly.%%%
+\usepackage[pdftex,unicode,colorlinks, citecolor=blue,%
+filecolor=black, linkcolor=blue, urlcolor=black]{hyperref}
+\newcommand{\onlinecite}[1]{\hspace{-1 ex} \nocite{#1}\citenum{#1}}
+
+%\usepackage{epstopdf}%This line makes .eps figures into .pdf - please comment out if not required.
+
+\definecolor{cream}{RGB}{222,217,201}
+
 \begin{document}
-\title{Superabsorption of light by nanoparticles}
 
-% Proposed reviewers: Anatoly Zayats, Andrea Alu, Sergei Bozhevolnyi
-% Prof. García de Abajo (http://garciadeabajos-group.icfo.es/) Andrea
-% Alu.
-\author{Konstantin Ladutenko} \email[e-mail:
-]{k.ladutenko@metalab.ifmo.ru} \affiliation{ITMO University, 49
-  Kronverskii Ave., St.~Petersburg 197101, Russian Federation}
+\pagestyle{fancy}
+\thispagestyle{plain}
+\fancypagestyle{plain}{
 
-\affiliation{Ioffe Physical-Technical Institute of the Russian Academy
-  of Sciences, 26 Polytekhnicheskaya Str., St.~Petersburg 194021,
-  Russian Federation}
+%%%HEADER%%%
+\fancyhead[C]{\includegraphics[width=18.5cm]{head_foot/header_bar}}
+\fancyhead[L]{\hspace{0cm}\vspace{1.5cm}\includegraphics[height=30pt]{head_foot/journal_name}}
+\fancyhead[R]{\hspace{0cm}\vspace{1.7cm}\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}
+\renewcommand{\headrulewidth}{0pt}
+}
+%%%END OF HEADER%%%
 
-\author{Pavel Belov} \affiliation{ITMO University, 49 Kronverskii
-  Ave., St.~Petersburg 197101, Russian Federation}
+%%%PAGE SETUP - Please do not change any commands within this section%%%
+\makeFNbottom
+\makeatletter
+\renewcommand\LARGE{\@setfontsize\LARGE{15pt}{17}}
+\renewcommand\Large{\@setfontsize\Large{12pt}{14}}
+\renewcommand\large{\@setfontsize\large{10pt}{12}}
+\renewcommand\footnotesize{\@setfontsize\footnotesize{7pt}{10}}
+\renewcommand\scriptsize{\@setfontsize\scriptsize{7pt}{7}}
+\makeatother
 
-\author{Ovidio Pe\~{n}a-Rodr\'{i}guez} \affiliation{Instituto de
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\renewcommand\footnoterule{\vspace*{1pt}% 
+\color{cream}\hrule width 3.5in height 0.4pt \color{black} \vspace*{5pt}} 
+\setcounter{secnumdepth}{5}
+
+\makeatletter 
+\renewcommand\@biblabel[1]{#1}            
+\renewcommand\@makefntext[1]% 
+{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
+\makeatother 
+\renewcommand{\figurename}{\small{Fig.}~}
+\sectionfont{\sffamily\Large}
+\subsectionfont{\normalsize}
+\subsubsectionfont{\bf}
+\setstretch{1.125} %In particular, please do not alter this line.
+\setlength{\skip\footins}{0.8cm}
+\setlength{\footnotesep}{0.25cm}
+\setlength{\jot}{10pt}
+\titlespacing*{\section}{0pt}{4pt}{4pt}
+\titlespacing*{\subsection}{0pt}{15pt}{1pt}
+%%%END OF PAGE SETUP%%%
+
+%%%FOOTER%%%
+\fancyfoot{}
+\fancyfoot[LO,RE]{\vspace{-7.1pt}\includegraphics[height=9pt]{head_foot/LF}}
+\fancyfoot[CO]{\vspace{-7.1pt}\hspace{13.2cm}\includegraphics{head_foot/RF}}
+\fancyfoot[CE]{\vspace{-7.2pt}\hspace{-14.2cm}\includegraphics{head_foot/RF}}
+\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
+\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
+\fancyhead{}
+\renewcommand{\headrulewidth}{0pt} 
+\renewcommand{\footrulewidth}{0pt}
+\setlength{\arrayrulewidth}{1pt}
+\setlength{\columnsep}{6.5mm}
+\setlength\bibsep{1pt}
+%%%END OF FOOTER%%%
+
+%%%FIGURE SETUP - please do not change any commands within this section%%%
+\makeatletter 
+\newlength{\figrulesep} 
+\setlength{\figrulesep}{0.5\textfloatsep}
+
+\newcommand{\topfigrule}{\vspace*{-1pt}% 
+\noindent{\color{cream}\rule[-\figrulesep]{\columnwidth}{1.5pt}} }
+
+\newcommand{\botfigrule}{\vspace*{-2pt}% 
+\noindent{\color{cream}\rule[\figrulesep]{\columnwidth}{1.5pt}} }
+
+\newcommand{\dblfigrule}{\vspace*{-1pt}% 
+\noindent{\color{cream}\rule[-\figrulesep]{\textwidth}{1.5pt}} }
+
+\makeatother
+%%%END OF FIGURE SETUP%%%
+
+%%%TITLE AND AUTHORS%%%
+\twocolumn[
+  \begin{@twocolumnfalse}
+\vspace{3cm}
+\sffamily
+\begin{tabular}{m{4.5cm} p{13.5cm} }
+
+\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Superabsorption of light by nanoparticles}} \\%Article title goes here instead of the text "This is the title"
+ & \vspace{0.3cm} \\
+
+ & \noindent\large{Konstantin Ladutenko,$^{\ast}$\textit{$^{a,b}$}
+   Pavel Belov,\textit{$^{a}$} Ovidio
+   Pe\~{n}a-Rodr\'{i}guez,\textit{$^{c}$} Ali Mirzaei,\textit{$^{d}$}
+   Andrey Miroshnichenko,\textit{$^{d}$} and Ilya
+  Shadrivov\textit{$^{d}$}} \\%Author names go here instead of "Full name", etc.
+
+\includegraphics{head_foot/dates} & \\
+
+\end{tabular}
+
+ \end{@twocolumnfalse} \vspace{0.6cm}
+
+  ]
+%%%END OF TITLE AND AUTHORS%%%
+
+%%%FONT SETUP - please do not change any commands within this section
+\renewcommand*\rmdefault{bch}\normalfont\upshape
+\rmfamily
+\section*{}
+\vspace{-1cm}
+
+%%%FOOTNOTES%%%
+
+\footnotetext{\textit{$^{a}$~ITMO University, 49
+  Kronverskii Ave., St.~Petersburg 197101, Russian Federation. E-mail: k.ladutenko@metalab.ifmo.ru}}
+\footnotetext{\textit{$^{b}$~Ioffe Physical-Technical Institute of the Russian Academy of Sciences, 26 Polytekhnicheskaya Str., St.~Petersburg 194021,
+  Russian Federation. }}
+\footnotetext{\textit{$^{c}$~Instituto de
   Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid, Jos\'{e}
-  Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain}
+  Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain. }}
+\footnotetext{\textit{$^{d}$~Nonlinear Physics Centre, Research School of
+  Physics and Engineering, The Australian National University, 59
+  Mills Rd, Acton, ACT, 2601, Australia. }}
 
-\author{Ali Mirzaei} \author{Andrey Miroshnichenko} \author{Ilya
-  Shadrivov} \affiliation{Nonlinear Physics Centre, Research School of
-  Physics and Engineering, The Australian National University, 59
-  Mills Rd, Acton, ACT, 2601, Australia}
+%Please use \dag to cite the ESI in the main text of the article.
+%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
+% \footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
 
-\date{\today}
-\begin{abstract}
-  Nanoparticles have a fundamental limit as to how much light they can
+% \footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
+Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
+
+%%%END OF FOOTNOTES%%%
+
+%%%ABSTRACT%%%%
+
+\sffamily{\textbf{  Nanoparticles have a fundamental limit as to how much light they can
   absorb. This limit is based on the finite number of modes excited in
@@
   multilayer nanoparticles, in which we can make several resonant
-  modes overlap at the same frequency resulting in {\it
-    superabsorption}.  We further introduce the {\it efficiency of the
+  modes overlap at the same frequency resulting in \textit{
+    superabsorption}.  We further introduce the \textit{ efficiency of the
     absorption} for a nanoparticle, which is the absorption normalized
   by the physical size of the particle, and show that efficient
-  absorbers are not always operating in the superabsorbing regime.
-\end{abstract}
+  absorbers are not always operating in the superabsorbing regime.}}\\%The abstrast goes here instead of the text "The abstract should be..."
 
-\pacs% insert suggested PACS numbers in braces on next line,
-% not more that 4
-{41.20.Jb 42.25.Bs 02.60.Pn 02.70.-c}
-% 41.20.Jb Electromagnetic wave propagation
-%% 42.25.Bs Wave propagation, transmission and absorption 02.60.Pn
-%% Numerical optimization
-% 02.70.-c Computational techniques; simulations
+%%%END OF ABSTRACT%%%%
 
-\maketitle %\maketitle must follow title, authors, abstract and \pacs
+\rmfamily %Please do not remove this line.
 
-Mie theory~\cite{Mie-1908}, which is over 100 years old, describes
+%%%MAIN TEXT%%%%
+
+Mie theory,\cite{Mie-1908} which is over 100 years old, describes
 interaction of electromagnetic waves with spherical particles. Mie
 solution is still of great interest these
-days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
+days,\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011}
 since it is one of the primary tools for analyzing wave scattering by
 spherical objects. Further development of the Mie
-theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
+theory\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
 it to the study of multilayer spherical
-particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
-various applications in cancer treatment~\cite{Zhang-2010,
-  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
-cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
-plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of
-thermal properties of insulating materials~\cite{Xie-2013}, as well as
-for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.
+particles.\cite{Sheehan-2013,Selmke-2012}  Such particles have
+various applications in cancer treatment,\cite{Zhang-2010,
+  Hirsch-2003} medical diagnostics,\cite{Allain-2002}
+cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
+plasmonic devices,\cite{Martin-2013, Alu-2005} in the study of
+thermal properties of insulating materials,\cite{Xie-2013} as well as
+for improving solar cells performance.\cite{Kameya-2011,Mann-2011}
 
 The scattering properties of multilayer cylinders and spheres was
-studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
+studied in great detail by Ruan and Fan.\cite{Fan-2010,Fan-2011}  In
 these works the authors introduced the concept of superscattering,
@@
 Similar fundamental limitations exist for the absorbing properties of
-subwavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
+subwavelength nanoparticles.  Tribelsky\cite{Tribelsky-2011} has
 derived a theoretical limit of a maximum absorption cross-section
@@
 |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
-coefficient as defined within the Mie theory~\cite{Bohren-1983} for
+coefficient as defined within the Mie theory\cite{Bohren-1983} for
 expansion of the scattered electric field:
-$$ 
+\[
 {\rm \mathbf{E}}_s = \sum_{n=1}^{\infty} E_n \left( i a_n {\rm
     \mathbf{N}}_{e1n}^{(3)} - b_n{\rm\mathbf{M}_{o1n}^{(3)}} \right),
-$$
+\]
 where ${\rm \mathbf{N}}_{e1n}^{(3)}$ and ${\rm\mathbf{M}_{o1n}^{(3)}}$
@@
 To overcome these limitations, we employ similar approach to the one
-used for enhancing scattering cross-section~\cite{Fan-2011}. In
+used for enhancing scattering cross-section.\cite{Fan-2011} In
 particular, we propose to use the multilayer structures, and by means
-of stochastic optimization algorithm~\cite{Jingqiao-JADE-2009} we
+of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
 optimize the ACS of such nanoparticles. We analyze the absorption
@@
 Another approach for an ideal absorber is given in the recent work by
-Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only dipole
+Grigoriev et al.\cite{Grigoriev-2015} Authors considered only dipole
 approximation, and the final result is very close to the dipole limit
-predicted by Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
+predicted by Tribelsky.\cite{Tribelsky-2011}  Such absorption design
 corresponds to the single mode limit.  At the same time, Grigoriev et
-al.~\cite{Grigoriev-2015} also provide an equation to design a
+al.\cite{Grigoriev-2015} also provide an equation to design a
 core-shell structure from given materials. However, in the case of
@@
 
-\begin{figure}
+\begin{figure}[h]
   \center{
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.4\textwidth]{fig/Fig1}%
-    \caption{(color online) Shematic view of the simulated $Si/Ag/Si$ particle. 
+    \includegraphics[width=0.4\textwidth]{Fig1}%
+    \caption{Shematic view of the simulated $Si/Ag/Si$ particle. 
       \label{fig:geom}
@@
 Fig.~\ref{fig:geom}. In what follows we describe the materials using
-experimentally measured parameters from Ref.~\cite{palik-1997}, and,
+experimentally measured parameters from Ref.,\cite{palik-1997}
 e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
 $\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
-layer we implemented~\cite{JADE-web} an adaptive differential
-evolution algorithm~\cite{Storn-DE-first-1997}, which is called
-JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
+layer we implemented\cite{JADE-web} an adaptive differential
+evolution algorithm,\cite{Storn-DE-first-1997} which is called
+JADE.\cite{Jingqiao-JADE-2009}  The technical details of the
 optimization algorithm were published previously in
-Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
-Scattnlay software~\cite{Pena-scattnlay-2009,Scattnlay-web}, whose
+Ref.\cite{Ladutenko-2014} We perform Mie calculations using the
+Scattnlay software,\cite{Pena-scattnlay-2009,Scattnlay-web} whose
 results are verified by a number of other implementations of the Mie
 solutions and by commercially available software including CST
-Microwave studio~\cite{CST-web} and Comsol
-Multiphysics~\cite{Comsol-web}.
+Microwave studio\cite{CST-web} and Comsol
+Multiphysics.\cite{Comsol-web}
 
@@
 
-\begin{figure}
+\begin{figure}[h]
   \center{
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.45\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
-    \caption{(color online) Results of optimization of the absorption efficiency
+    \includegraphics[width=0.45\textwidth]{2015-04-01-Qabs-SiAgSi-overview}%
+    \caption{Results of optimization of the absorption efficiency
       for the fixed wavelength of 500~nm. (a) Absorption efficiency
-      with the best value achieved for the particle of the double-layer Ag/Si design of the radius of 36~nm. Dashed lines show theoretical
-      limits for the first channel and second channel
-      absorption. The second and third peaks in the absorption efficiency
-      curve exceed the theoretical limit for the second mode
-      absorption at $R=63$~nm and $R=81$~nm. Local maxima of
-      absorption efficiency are additionally marked with arrows. (b) Mie absorption
-      coefficients for individual excited modes of the optimized
-      structures. (c) Optimized layer thicknesses. For the total
-      particle radius below 46~nm the optimizer converges to
-      a bi-layer structure, when core size vanishes, and the
-      optimum design is a $Ag/Si$ particle. 
+      with the best value achieved for the particle of the
+      double-layer Ag/Si design of the radius of 36~nm. Dashed lines
+      show theoretical limits for the first channel and second channel
+      absorption. The second and third peaks in the absorption
+      efficiency curve exceed the theoretical limit for the second
+      mode absorption at $R=63$~nm and $R=81$~nm. Local maxima of
+      absorption efficiency are additionally marked with arrows. (b)
+      Mie absorption coefficients for individual excited modes of the
+      optimized structures. (c) Optimized layer thicknesses. For the
+      total particle radius below 46~nm the optimizer converges to a
+      bi-layer structure, when core size vanishes, and the optimum
+      design is a $Ag/Si$ particle. 
       \label{fig:overview}
@@
 limit of a dipole ($n=1$) and a quadrupole ($n=2$)
-resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm
-  abs\ max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi
+resonances,\cite{Tribelsky-2011} which are given as \[Q^{(n)}_{\rm
+  abs\ max}=\frac{2n+1}{2q^2},\] where the size parameter $q=2\pi
 R/\lambda$, and $n$ is the angular momentum of the mode. Following
-Ref.~\cite{Fan-2011}, where the authors introduce superscattering for
+Ref.\cite{Fan-2011}, where the authors introduce superscattering for
 spherical particles, here we introduce superabsorption regime, when
@@
 
-\begin{figure}
+\begin{figure}[h]
   \center{
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.45\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra4}%
-    \caption{(color online) Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design.
+    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
+    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design.
 Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer.
@@
 
-\begin{figure}
+\begin{figure}[h]
   \center{
     % Use pdfcrop to remove white margins
-    \includegraphics[width=0.47\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs}%
-    \caption{(color online) Amplitude of electric field for $R=36$~nm (a,c) and
+    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
+    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
       superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
@@
 desired for some applications. As an example we reproduce some of the
-results from the work of Estakhri and Al\`u~\cite{Alu-2014}, where
+results from the work of Estakhri and Al\`u,\cite{Alu-2014} where
 authors aim to design absorbers with small scattering cross-section,
 and we provide a number of new optimized designs. The efficiency in
-the Ref.~\cite{Alu-2014} is defined as the ACS normalized to
+the Ref.\cite{Alu-2014} is defined as the ACS normalized to
 scattering cross-section. Initially, we set the total value of the
@@
 to the structure with contributing harmonics TM${_1}$ and TE$_1$ from
-Ref~\cite{Alu-2014}.  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
+Ref.\cite{Alu-2014}  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
 -10.37+ i0.35$, and $\epsilon_3=8.4+i2.33$ as material parameters we
@@
   abs}^{(\alpha)} =7.65$ which corresponds to $\eta_{\rm
-  abs}^{(\alpha)} =7.1$ from the original work~\cite{Alu-2014}.
+  abs}^{(\alpha)} =7.1$ from the original work.\cite{Alu-2014}
 However, if we set the optimizer to keep high level of absoption
@@
 It is interesting to note that a similar conclusion was made by Miller
-et al.~\cite{Miller-2014} for extinction of arbitrary particles: small
+et al.\cite{Miller-2014} for extinction of arbitrary particles: small
 size with only dipole response is preferable for geometric volume
@@
 
-\begin{acknowledgments}
   Thanks to David A. Powell for his contribution to the analysis of
@@
   the Russian Federation (Grant 074-U01) for the financial support.
-\end{acknowledgments}
 
+% \begin{figure}[h]
+% \centering
+%   \includegraphics[height=3cm]{example}
+%   \caption{An example figure caption}
+%   \label{fgr:example}
+% \end{figure}
+
+% \begin{figure*}
+%  \centering
+%  \includegraphics[height=3cm]{example2}
+%  \caption{An image from the \textit{Physical Chemistry Chemical Physics} cover gallery, set as a double-column figure.}
+%  \label{fgr:example2col}
+% \end{figure*}
+
+%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
+
+\balance
+
+%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
+%\renewcommand\refname{Notes and references}
+
+%%%REFERENCES%%%
+\scriptsize{
+%\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
 \bibliography{2015-Ladutenko-Qabs}
+\bibliographystyle{rsc} } %the RSC's .bst file
+
 \end{document}

### 2015-09-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
After discussion with Ilya (Russian comments)

@@
 
+400-700 3-layer
+4-layer?
+
+В статье этого графика нет, есть обсуждение, готовим новую статью.
+
 In order to reply to this comment we run an optimization ... No changes
@@
 \end{tabular}
+
+Lumerical - periodic boundary - попробовать несколько частиц
 
@@
 
+Для маленьких толщин лучше простой диполь, если есть ограничения на
+минимальный размер частицы - лучше суперпоглотитель. Или, например,
+если важно ещё и абсолютное поглощение от одиночной частицы - большая
+частица поглощает больше, для неё оптимальнее работа в супер- режиме.
+
 There are several points to be treated carefully when discussing...
@@
 
+Да, он прав, основной вклад от ядра, остальные делают верхушку
+плоской. Фишка в том что резонанс плоский, а не широкий.
+
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
@@
 \end{tabular}
+
+Илья
+
 \\

### 2015-09-11 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Figures to responce the first comment

--- 2015-09-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
@@
 
-In order to reply to this comment we run an optimization ... No changes
-to the manuscript were made.
+This comment touches two aspects of broadband performance, namely,
+properties of a stanalone particle and in interaction with other
+particles.  The first case, as it was correctly mentioned with the
+reviewer, has some limiations.  We can design a band, which will be
+wider of a typical band for a given multipole, however, it`s width is
+not extremly large.  To illustrate this we have run an optimization
+with a goal to provide a prediefined separation between multipole
+resonanses (Fig.~\ref{fig:broadband}).
+\begin{figure}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{band20-em}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{band20-em-ch}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{band80-em}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{band80-em-ch}
+  \end{minipage}  
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     e)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     f)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{band80-e}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{band80-e-ch}
+  \end{minipage}  
+   \caption{Single particle desings for separation between dipole
+     resonances of 20 nm (a-b) and 80 nm (c-f). Left column with
+     figures (a,c,e) contains spectra of Mie efficiency for extinction
+     (Qext), scattering (Qsca), absorption (Qabs, blue curve) and
+     backscattering (Qbk). Right column (b,d,f) presents contibution
+     of multipoles to the spectra (red and green stands for electric
+     and magnetic dipoles, blue and cyan corresponds to quadrupole
+     electric and magnetic modes, respectively). It is interesting to
+     note that for 80 nm separation optimizer was able to find a
+     desing with two resonances of a dipole mode (f). We suppose that
+     the latter most likely has the same nature as the responce
+     presented in Fig. 2(c,d) of the manuscript: there are several
+     resonances of an electric dipole responce binded to different
+     layers of the particle.\label{fig:broadband}}%
+\end{figure}
+
+Our observation is the following: while the separation is small enough
+compared to a multiple resonance width the optimizer was successful to
+find desings with electric and magnetic dipole. If the separation is
+large the absorption band splits into two. For large separation is is
+also possible to obtain two resonanses of the electric dipole
+responce, located at predefined position
+(Fig. \ref{fig:broadband}(e,f)).  Still there are not so many 
+possibilities here to design a good wideband. To control the
+bandwidth at a given spectral position we need to involeve relatively large particles. This
+leads to appereance of resonances (and absorbtion) out of the designed band.
+
+To answer the second part of the comment, related to possiblity of
+usage of the pariticle array with dispered sizes, we designed two
+particles with best absorption effeciency at 475~nm and 525~nm and
+simulatied them both with FDTD method using Lumerical FDTD Solutions.
+Sketch of the simulated system is in Fig.~\ref{fig:fdtd}
+
+\begin{figure}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{FDTD-mode-d00}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{fdtd-spectra}
+  \end{minipage}
+   \caption{.\label{fig:fdtd}}%
+\end{figure}
+
+% band80-e
+% Si-Ag-Si-TotalR058.00nm-Qabs02.4351291413952--core0013.16nm--inshell0041.41nm--outshell0003.43nm-fails0-spectra
+% band80-em
+% Si-Ag-Si-TotalR064.00nm-Qabs02.6266428870829--core0024.22nm--inshell0024.50nm--outshell0015.28nm-fails0-spectra
+% band20-e
+% Si-Ag-Si-TotalR058.00nm-Qabs03.9125128013731--core0010.44nm--inshell0042.75nm--outshell0004.81nm-fails0-spectra
+% band20-em
+% Si-Ag-Si-TotalR062.00nm-Qabs05.0835852277006--core0028.20nm--inshell0011.88nm--outshell0021.91nm-fails0-spectra
+
+%% 400-700 3-layer
+%% 4-layer?
+
+%% В статье этого графика нет, есть обсуждение, готовим новую статью.
+
+%% In order to reply to this comment we run an optimization ...
+
+We changed the manuscript ``The stochastic algorithm utilized in our approach is very
+generic and the optimization can be repeated for any desired
+wavelength or wavelength range. As a result, one can design
+spectrally-selective absorbers or broadband absorbers with almost
+arbitrary prescribed properties.''
 
@@
 
+%% Lumerical - periodic boundary - попробовать несколько частиц
+
 We totally agree with the reviewer's statement. It seems that our
@@
 
-It should be mentioned that .... No changes to the
-manuscript were made.
+%% It should be mentioned that .... No changes to the
+%% manuscript were made.
 
@@
 
-There are several points to be treated carefully when discussing...
- However, to claim this concept to be a general one ...  more simulations
-should be performed.
+%% Для маленьких толщин лучше простой диполь, если есть ограничения на
+%% минимальный размер частицы - лучше суперпоглотитель. Или, например,
+%% если важно ещё и абсолютное поглощение от одиночной частицы - большая
+%% частица поглощает больше, для неё оптимальнее работа в супер- режиме.
+
+%% There are several points to be treated carefully when discussing...
+%%  However, to claim this concept to be a general one ...  more simulations
+%% should be performed.
 
@@
 
+%% Да, он прав, основной вклад от ядра, остальные делают верхушку
+%% плоской. Фишка в том что резонанс плоский, а не широкий.
+
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
@@
 stage. 
-\end{tabular}
+\end{tabular}%
+%% Илья
 \\

### 2015-09-16 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Draft response for the first comment

@@
 Maybe, a possible way of using the dispersed size scale nanoparticles should be added for improving the study.
-\end{tabular}
+\end{tabular}\\
 
@@
 reviewer, has some limiations.  We can design a band, which will be
-wider of a typical band for a given multipole, however, it`s width is
+broader of a typical band for a given multipole, however, it`s width is
 not extremly large.  To illustrate this we have run an optimization
@@
      the latter most likely has the same nature as the responce
-     presented in Fig. 2(c,d) of the manuscript: there are several
+     presented in Fig. 3(c,d) of the manuscript: there are several
      resonances of an electric dipole responce binded to different
@@
 \end{figure}
-
 Our observation is the following: while the separation is small enough
@@
 (Fig. \ref{fig:broadband}(e,f)).  Still there are not so many
-possibilities here to design a good wideband. To control the
-bandwidth at a given spectral position we need to involeve relatively large particles. This
-leads to appereance of resonances (and absorbtion) out of the designed band.
+possibilities here to design a good broadband. To control the
+bandwidth at a given spectral position we need to involeve relatively
+large particles. This leads to appereance of resonances (and
+absorbtion) out of the designed band which are hard to control or
+suppress in disscussed triple-layer structure.
 
@@
 simulatied them both with FDTD method using Lumerical FDTD Solutions.
-Sketch of the simulated system is in Fig.~\ref{fig:fdtd}
-
+Sketch of the simulated system and final results are in
+Fig.~\ref{fig:fdtd}. To verify our FDTD we fist simulated absorption
+of standalone spheres, the obtained postions and amplitudes of
+resonances corresponde well with Mie caclulations.
 \begin{figure}
@@
   \end{minipage}
-   \caption{.\label{fig:fdtd}}%
+   \caption{(a) Fullwave simulation prepared in Lumerical FDTD. (b)
+     Absorption spectra of stand-alone spheres and in dimer
+     configuration with separation between spheres of 0, 10, and 30~nm.\label{fig:fdtd}}%
 \end{figure}
+Next step was to find out the possible interactions between two
+spheres, so we run a simulation in dimer configuration with zero
+separation between spheres and with 10 and 30~nm separation.  The
+resulting spectra has a strong contribution from standalone
+resonances, while coupling effects seems to be minor.  This can be
+easily explained from field distribution in Fig.~4(c) of the
+manuscript. Positioning spheres in H-k plane we are exploting the
+feature of field being highly localized inside the the sphere.  For
+sure arranging spheres in other plane, increasing the number of
+spheres can change the amount of coupling between the spheres. Still,
+here we show that in principle it is possible to construct an
+absoption band of an array of dispersed particles simply optimizing
+the properties of every single sphere.
+
+We changed the manuscript from ``As a result, one can design
+spectrally-selective absorbers or broadband absorbers with almost
+arbitrary prescribed properties.'' to ``As a result, one can design
+absorbers with broadened spectra or spectrally-selective absorbers
+with almost arbitrary prescribed properties.  Due to high localization
+of field inside the particle (espatially in H-k plane) it is also
+possible to desing arrays of dispersed size particles by defining the
+properties of individual particles; we obtained rather small coupling
+between particles during additional simulation using FDTD method.''
 
@@
 %% In order to reply to this comment we run an optimization ...
-
-We changed the manuscript ``The stochastic algorithm utilized in our approach is very
-generic and the optimization can be repeated for any desired
-wavelength or wavelength range. As a result, one can design
-spectrally-selective absorbers or broadband absorbers with almost
-arbitrary prescribed properties.''
 

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Additiional polarization for 1st comment

@@
 usage of the pariticle array with dispered sizes, we designed two
-particles with best absorption effeciency at 475~nm and 525~nm and
+particles with best absorption effeciency at 475~nm and 525~nm (outer
+radius 34 and 38~nm) and
 simulatied them both with FDTD method using Lumerical FDTD Solutions.
@@
   \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)   \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{fdtd-spectra-Ek}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{fdtd-field}
+  \end{minipage}
     \caption{(a) Fullwave simulation prepared in Lumerical FDTD. (b)
      Absorption spectra of stand-alone spheres and in dimer
-     configuration with separation between spheres of 0, 10, and 30~nm.\label{fig:fdtd}}%
+     configuration with separation between spheres of 0, 10, and
+     30~nm, particles are in H-k plane (c) Separation 0 and 30~nm for
+     particles in E-k plane (d) Field distribution at 500nm of
+     incedent wavelength for particles in E-k plane with separation of
+     30~nm.\label{fig:fdtd}}%
 \end{figure}

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
simulation resluts for comment 2 are in response letter

@@
 reviewer, has some limiations.  We can design a band, which will be
-broader of a typical band for a given multipole, however, it`s width is
+broader of a typical band for a given multipole, however, width is
 not extremly large.  To illustrate this we have run an optimization
@@
      desing with two resonances of a dipole mode (f). We suppose that
-     the latter most likely has the same nature as the responce
+     the latter most likely has the same nature as the response
      presented in Fig. 3(c,d) of the manuscript: there are several
-     resonances of an electric dipole responce binded to different
+     resonances of an electric dipole response binded to different
      layers of the particle.\label{fig:broadband}}%
@@
 also possible to obtain two resonanses of the electric dipole
-responce, located at predefined position
+response, located at predefined position
 (Fig. \ref{fig:broadband}(e,f)).  Still there are not so many
@@
 sure arranging spheres in other plane, increasing the number of
-spheres can change the amount of coupling between the spheres. Still,
-here we show that in principle it is possible to construct an
-absoption band of an array of dispersed particles simply optimizing
-the properties of every single sphere.
+spheres can change the amount of coupling between the spheres. As an
+example we tested arragement of sphers in E-k plane
+Fig.~\ref{fig:fdtd}(c); for zero separation the intraction between
+spheres is strong, however, due to near-field nature of this coupling
+it rapidly decays with the separation width Fig.~\ref{fig:fdtd}(d),
+for separation of 30~nm responses of individual particle dominates in
+overall spectra for both planes of polarization. This way we show that
+in principle it is possible to construct an absoption band of an array
+of dispersed particles simply optimizing the properties of every
+single sphere carefully tuning the distance between particles (which
+still is much smaller than the wavelength).
 
@@
 absorbers with broadened spectra or spectrally-selective absorbers
-with almost arbitrary prescribed properties.  Due to high localization
-of field inside the particle (espatially in H-k plane) it is also
-possible to desing arrays of dispersed size particles by defining the
-properties of individual particles; we obtained rather small coupling
-between particles during additional simulation using FDTD method.''
+with almost arbitrary prescribed properties.  Due to strong
+localization of electric dipole field (espatially in H-k plane) it is
+also possible to desing dispersed size arrays particles by defining
+their individual properties for composite absorption spectra; we
+obtained rather small coupling between particles during additional
+simulation using FDTD method.''
 
@@
 %% В статье этого графика нет, есть обсуждение, готовим новую статью.
-
 %% In order to reply to this comment we run an optimization ...
@@
 %% Lumerical - periodic boundary - попробовать несколько частиц
+We would like to thank the reviewer for provided citation, some of
+them turned to be really interesting. In order to reply this comment
+first of all we checked all the citations provided.
 
-We totally agree with the reviewer's statement. It seems that our
-manuscript was not clear enough at this point. ...  However, as we
-compare final optimization results we conclude that .... To make it
-clearer we rewrite this part of the manuscript as follows:
+ACS Applied Materials \& Interfaces, 7, 4962-4968 (2015) titled
+``Automatically Acquired Broadband Plasmonic-Metamaterial Black
+Absorber during the Metallic Film-Formation'' uses metal film
+formation process to achive very wideband performance. However, the
+absorption in this case is highly dependable on the thickness of the
+underlaying silica layer.  This way we can argue against the conlusion
+of the paper ``These results also confirm that an ultrathin
+meta-surface layer (less than 10 nm) structure can produce nearly
+ideal broadband light absorption'' - to achieve experimentally
+observed performance the whole system (including silica layer and gold
+under-layer) is needed. A more detailed simulation can give some answers, however,
+we cant expect that most of the absorbtion happends in the gold
+under-layer, while the metasurface and silica layer serves to be an
+impedance matcher.  This proposal is confirmed with the experemental
+results in Fig. 5 of the paper, for 100~nm silica layer the absorption
+is low. Anyway, albiet of the exiting experimental results obtained in
+the paper they exploit phycal effect that differs a lot from the
+proposed in our manuscript; our particles were desinged to absorb the
+incident power by themselfs, and it work perfectly for a stand-alone
+sphere.  This can be extremly conviniet, for example, for
+nanophotonics application, when the available volume to place an
+absorber can be very limited.
+
+Materials Letters 158, 262265 (2015);
+
+Applied Physics Letters, 104, 081116 (2014);
+
+Nanotechnology, 24, 155203 (2013) titled ``Near-unity transparency of
+a continuous metal film via cooperative effects of double plasmonic
+arrays'' describes light interaction with a gold film, which has an
+array of gold spheres positioned on top, bottom, or both sides of the
+film.  Provided simulations show a strong field enhancement between
+the spheres. Absorption related part of the paper references [18-21],
+where [20] is Le F, Brandl D W, Urzhumov Y A, Wang H, Kundu J, Halas N
+J, Aizpurua J and Nordlander P 2008 ACS Nano 2 707 titled ``Metallic
+Nanoparticle Arrays: A Common Substrate for Both Surface-Enhanced
+Raman Scattering and Surface-Enhanced Infrared Absorption''.  It this
+paper absorption spectra in Fig.~5(b) calculated with electrostatic
+plasmon hybridization method showes, as it was stated with a reviewer,
+a significat increase of the band when packing particles to an
+array. This broadering originates from the appearance of collective
+mode (or, in other words, the hybridization of plasmon responce of
+several particles) with additional impact from retardation effects. It
+can be of great intereset (including applied examples) to apply the
+same approch from our manuscript to this system. It should be possible
+to optimize simultniously geometry of individual particles and their
+positioning in array to degenerate several absorption resonances of
+such collective modes in order to achieve superabsorption. However, we
+do not have any working code for plasmon hybridization method to check
+it with our optimizer. Using brute force approach with FDTD simulation
+looks to be rather computationaly expensive without any prior
+analytical estimations.
+
+For a fast check of this idea we simulated the 3x3 rectangular array
+of spheres (to provide a good coupling both in E and H direcitons)
+with the separation of 4 nm (so it is only 2 mesh cells to resolve the
+separation in the used coarse grid, selected to get a resonable timing
+of a 3D full-wave simulation) Fig~\ref{fig:fdtd-3x3}(a). Several
+collective modes can be recognized from field distribution while
+changing the incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e). However,
+for used materials, nanoparicle and array designs, and spectral range
+we observed a blue shift of absoption responce (it looks to be
+dominated with silver plasmon resonance) Fig~\ref{fig:fdtd-3x3}(b),
+which is opposite to results of Le et al. in Fig.~5(b) of their paper.
+
+This way it looks that using particle array adds a whole banch of new
+physical features which deserve a separate investigation. No changes
+to the manuscript were done.
+\begin{figure}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{fdtd-3x3}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+   \includegraphics[width=0.95\textwidth]{fdtd-spectra-3x3}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)   \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{fdtd-field-408nm}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{fdtd-field-452nm}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     e)    \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     -   \end{flushleft}
+  \end{minipage}
+  \begin{minipage}[h]{0.49\textwidth} 
+    \includegraphics[width=0.95\textwidth]{fdtd-field-600nm}
+  \end{minipage}
+  %% \begin{minipage}[h]{0.49\textwidth} 
+  %%   \includegraphics[width=0.95\textwidth]{fdtd-field-452nm}
+  %% \end{minipage}
+
+    \caption{ FDTD simulation of 3x3 grid of spheres optimized for
+      absorption at 525~nm(a) Fullwave simulation prepared in Lumerical FDTD. (b)
+     Absorption spectra of stand-alone spheres and in dimer
+     configuration with separation between spheres of 0, 10, and
+     30~nm, particles are in H-k plane (c) Separation 0 and 30~nm for
+     particles in E-k plane (d) Field distribution at 500nm of
+     incedent wavelength for particles in E-k plane with separation of
+     30~nm.\label{fig:fdtd-3x3}}%
+\end{figure}
+
+%% We totally agree with the reviewer's statement. It seems that our
+%% manuscript was not clear enough at this point. ...  However, as we
+%% compare final optimization results we conclude that .... To make it
+%% clearer we rewrite this part of the manuscript as follows:
 

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
added thermal consideration

@@
 observed performance the whole system (including silica layer and gold
-under-layer) is needed. A more detailed simulation can give some answers, however,
-we cant expect that most of the absorbtion happends in the gold
-under-layer, while the metasurface and silica layer serves to be an
-impedance matcher.  This proposal is confirmed with the experemental
-results in Fig. 5 of the paper, for 100~nm silica layer the absorption
-is low. Anyway, albiet of the exiting experimental results obtained in
-the paper they exploit phycal effect that differs a lot from the
+under-layer) is needed. A more detailed simulation can give some
+answers, however, we expect that most of the absorbtion happends in
+the gold under-layer, while the metasurface and silica layer serves to
+be an impedance matcher.  This proposal is confirmed with the
+experemental results in Fig. 5 of the paper, for 100~nm silica layer
+the absorption is low.  At the same time the wideband performance can
+be related to the fractal-type surface, as it is shown in Fig.~2(f)
+Moreover, it should be relativly easy to estimate the thermal
+behaviour of such a metasurface, as soon as isolated particles on the
+top of the silica have no heat transfer with electrons to the
+substrate.  If we suppose, that most of the light is absorbed in this
+layer this should lead to overheating of the metasurface due to
+extreamly low geometrical volume.
+
+Anyway, albiet of the exciting experimental results obtained in the
+paper they exploit phsycal effect that differs a lot from the one
 proposed in our manuscript; our particles were desinged to absorb the
-incident power by themselfs, and it work perfectly for a stand-alone
-sphere.  This can be extremly conviniet, for example, for
-nanophotonics application, when the available volume to place an
-absorber can be very limited.
+incident power by themselfs, and they work perfectly in a stand-alone
+mode.  This can be extremly conviniet, for example, for nanophotonics
+application, when the available volume to place an absorber can be
+very limited. Same overheating question can appear here, limiting the
+operational power range.
 

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
small changes

@@
 layer this should lead to overheating of the metasurface due to
-extreamly low geometrical volume.
+extreamly low geometrical volume righ after switching on the continous
+light source. Measuring temperature via infrared radiation from both
+sides of the sample can provide hints to distinguish the absortption
+origin.
 

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
3rd citation of the second comment done

@@
 the gold under-layer, while the metasurface and silica layer serves to
-be an impedance matcher.  This proposal is confirmed with the
+be kind of an impedance matcher.  This proposal is confirmed with the
 experemental results in Fig. 5 of the paper, for 100~nm silica layer
@@
 
-Applied Physics Letters, 104, 081116 (2014);
+Applied Physics Letters, 104, 081116 (2014) titled ``$\lambda^3$/20000
+plasmonic nanocavities with multispectral ultra-narrowband absorption
+for high-quality sensing'' is cleary not related to ``broadband light
+coupling and confinement'' as it was stated by the reviewer and was
+probably listed by an accident.
 
@@
 a continuous metal film via cooperative effects of double plasmonic
-arrays'' describes light interaction with a gold film, which has an
-array of gold spheres positioned on top, bottom, or both sides of the
-film.  Provided simulations show a strong field enhancement between
-the spheres. Absorption related part of the paper references [18-21],
-where [20] is Le F, Brandl D W, Urzhumov Y A, Wang H, Kundu J, Halas N
-J, Aizpurua J and Nordlander P 2008 ACS Nano 2 707 titled ``Metallic
-Nanoparticle Arrays: A Common Substrate for Both Surface-Enhanced
-Raman Scattering and Surface-Enhanced Infrared Absorption''.  It this
-paper absorption spectra in Fig.~5(b) calculated with electrostatic
-plasmon hybridization method showes, as it was stated with a reviewer,
-a significat increase of the band when packing particles to an
-array. This broadering originates from the appearance of collective
-mode (or, in other words, the hybridization of plasmon responce of
-several particles) with additional impact from retardation effects. It
-can be of great intereset (including applied examples) to apply the
-same approch from our manuscript to this system. It should be possible
-to optimize simultniously geometry of individual particles and their
-positioning in array to degenerate several absorption resonances of
-such collective modes in order to achieve superabsorption. However, we
-do not have any working code for plasmon hybridization method to check
-it with our optimizer. Using brute force approach with FDTD simulation
-looks to be rather computationaly expensive without any prior
-analytical estimations.
+arrays'' at a first glance is not related to ``broadband light
+coupling and confinement'' and describes light interaction with a gold
+film, which has an array of gold spheres positioned on top, bottom, or
+both sides of the film.  Provided simulations show a strong field
+enhancement between the spheres. Absorption related part of the paper
+references [18-21], where [20] is Le F, Brandl D W, Urzhumov Y A, Wang
+H, Kundu J, Halas N J, Aizpurua J and Nordlander P 2008 ACS Nano 2 707
+titled ``Metallic Nanoparticle Arrays: A Common Substrate for Both
+Surface-Enhanced Raman Scattering and Surface-Enhanced Infrared
+Absorption''.  It this paper absorption spectra in Fig.~5(b)
+calculated with electrostatic plasmon hybridization method showes, as
+it was stated with a reviewer, a significat increase of the band when
+packing particles to an array. This broadering originates from the
+appearance of collective mode (or, in other words, the hybridization
+of plasmon responce of several particles) with additional impact from
+retardation effects. It can be of great intereset (including applied
+examples) to apply the same approch from our manuscript to this
+system. It should be possible to optimize simultniously geometry of
+individual particles and their positioning in array to degenerate
+several absorption resonances of such collective modes in order to
+achieve superabsorption. However, we do not have any working code for
+plasmon hybridization method to check it with our optimizer. Using
+brute force approach with FDTD simulation looks to be rather
+computationaly expensive without any prior analytical estimations.
 

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Claim to the editors

@@
 NR-COM-08-2015-005468, which we aim for publication in Nanoscale.
+
+As a group of authors interested in high quality input we know that
+unbiased and professional review is an important part of a publication
+process.  This way we would like to stress you attantion to the second
+comment of the first reviewer. He had listed a number of publications,
+however, it is hard to belive that this list is unbiased after looking
+to the authors names; several authors from Jiangxi Normal University a
+listed in all of this publications.  We provide our findings here:
+\begin{enumerate}
+\item ACS Applied Materials & Interfaces, 7, 4962-4968 (2015)\\
+  Zhengqi Liu, Xiaoshan Liu,  Shan Huang,  Pingping Pan,  Jing Chen,
+  Guiqiang Liu, and Gang Gu\\
+  DOI: 10.1021/acsami.5b00056
+\item Materials Letters 158, 262-265 (2015)\\
+  Zhengqi Liu , Guiqiang Liu, Xiaoshan Liu, Shan Huang, Yan Wang,
+  Pingping Pan, Mulin Liu\\
+  http://dx.doi.org/10.1016/j.matlet.2015.06.029
+\item Applied Physics Letters, 104, 081116 (2014)\\
+  Zheng-qi Liu, Hui-bai Shao,  Gui-qiang Liu, Xiao-shan Liu, Hai-qing Zhou, Ying Hu,
+  Xiang-nan Zhang, Zheng-jie Cai, and Gang Gu\\
+  http://dx.doi.org/10.1063/1.4867028
+\item Nanotechnology, 24, 155203 (2013)\\
+  Zheng-qi Liu, Gui-qiang Liu, Hai-qing Zhou, Xiao-shan Liu,
+  Kuan Huang, Yuan-hao Chen, and Guo-lan Fu\\
+  doi:10.1088/0957-4484/24/15/155203
+\end{enumerate}
 
@@
 %% Lumerical - periodic boundary - попробовать несколько частиц
-We would like to thank the reviewer for provided citation, some of
+We would like to thank the reviewer for provided citations, some of
 them turned to be really interesting. In order to reply this comment
@@
 
-Materials Letters 158, 262265 (2015);
+Materials Letters 158, 262265 (2015) titled ``Dielectric shell
+modulated plasmonic crystal for novel light absorption meta-surface''
 
@@
 changing the incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e). However,
-for used materials, nanoparicle and array designs, and spectral range
-we observed a blue shift of absoption responce (it looks to be
-dominated with silver plasmon resonance) Fig~\ref{fig:fdtd-3x3}(b),
-which is opposite to results of Le et al. in Fig.~5(b) of their paper.
+for used materials, nanoparicle and array designs, spectral range, and
+plane of polarization we observed a blue shift of absoption responce
+(it looks to be dominated with silver plasmon resonance)
+Fig~\ref{fig:fdtd-3x3}(b), which is opposite to results of Le et
+al. in Fig.~5(b) of their paper.
 

### 2015-09-19 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
simulation for hcp plasmonic array

@@
 \end{center}
-Dear Editor,
+Dear Editors,
 \\
@@
 however, it is hard to belive that this list is unbiased after looking
-to the authors names; several authors from Jiangxi Normal University a
-listed in all of this publications.  We provide our findings here:
+to the authors names; several authors from Jiangxi Normal University are
+listed in all of this publications (it looks like some names have two
+spelling options with and without the dash).  We provide our findings here:
 \begin{enumerate}
@@
 
-I would like to thank the editor and two anonymous reviewers for their
+We would like to thank the editor and two anonymous reviewers for their
 constructive comments, which helped us to improve the
@@
 
+\newpage
 \textbf{Reviewer \#1 comments}
@@
 of standalone spheres, the obtained postions and amplitudes of
-resonances corresponde well with Mie caclulations.
+resonances to corresponde well with Mie caclulations.
 \begin{figure}
@@
 it rapidly decays with the separation width Fig.~\ref{fig:fdtd}(d),
-for separation of 30~nm responses of individual particle dominates in
+for separation of 30~nm responses of individual particles dominate in
 overall spectra for both planes of polarization. This way we show that
@@
 
-%% Lumerical - periodic boundary - попробовать несколько частиц
+% Lumerical - periodic boundary - попробовать несколько частиц
 We would like to thank the reviewer for provided citations, some of
@@
 top of the silica have no heat transfer with electrons to the
-substrate.  If we suppose, that most of the light is absorbed in this
+substrate.  If we suppose that most of the light is absorbed in top
 layer this should lead to overheating of the metasurface due to
-extreamly low geometrical volume righ after switching on the continous
-light source. Measuring temperature via infrared radiation from both
-sides of the sample can provide hints to distinguish the absortption
-origin.
+extreamly low geometrical volume. For this case in steady state we
+should expect a large temperature gradient as soon as gold thermal
+condutivity 310 $W/(m\cdot K)}$ is about 200 fold larger than silica
+  $1.4 W/(m\cdot K)}$. Measuring temperature via infrared
+    radiation from both sides of the sample can provide hints to
+    distinguish the absortption origin.
 
@@
 application, when the available volume to place an absorber can be
-very limited. Same overheating question can appear here, limiting the
+very limited. Same overheating question can also appear here, limiting the
 operational power range.
-
-Materials Letters 158, 262265 (2015) titled ``Dielectric shell
-modulated plasmonic crystal for novel light absorption meta-surface''
 
@@
 for high-quality sensing'' is cleary not related to ``broadband light
-coupling and confinement'' as it was stated by the reviewer and was
+coupling and confinement'' and was
 probably listed by an accident.
@@
 a continuous metal film via cooperative effects of double plasmonic
-arrays'' at a first glance is not related to ``broadband light
-coupling and confinement'' and describes light interaction with a gold
-film, which has an array of gold spheres positioned on top, bottom, or
-both sides of the film.  Provided simulations show a strong field
-enhancement between the spheres. Absorption related part of the paper
-references [18-21], where [20] is Le F, Brandl D W, Urzhumov Y A, Wang
-H, Kundu J, Halas N J, Aizpurua J and Nordlander P 2008 ACS Nano 2 707
-titled ``Metallic Nanoparticle Arrays: A Common Substrate for Both
-Surface-Enhanced Raman Scattering and Surface-Enhanced Infrared
-Absorption''.  It this paper absorption spectra in Fig.~5(b)
-calculated with electrostatic plasmon hybridization method showes, as
-it was stated with a reviewer, a significat increase of the band when
-packing particles to an array. This broadering originates from the
-appearance of collective mode (or, in other words, the hybridization
-of plasmon responce of several particles) with additional impact from
-retardation effects. It can be of great intereset (including applied
-examples) to apply the same approch from our manuscript to this
-system. It should be possible to optimize simultniously geometry of
-individual particles and their positioning in array to degenerate
-several absorption resonances of such collective modes in order to
-achieve superabsorption. However, we do not have any working code for
-plasmon hybridization method to check it with our optimizer. Using
-brute force approach with FDTD simulation looks to be rather
-computationaly expensive without any prior analytical estimations.
+arrays'' describes light interaction with a gold film, which has an
+array of gold spheres positioned on top, bottom, or both sides of the
+film.  Provided simulations show a strong field enhancement between
+the spheres. Absorption related part of the paper references [18-21],
+where [20] is Le F, Brandl D W, Urzhumov Y A, Wang H, Kundu J, Halas N
+J, Aizpurua J and Nordlander P 2008 ACS Nano 2 707 titled ``Metallic
+Nanoparticle Arrays: A Common Substrate for Both Surface-Enhanced
+Raman Scattering and Surface-Enhanced Infrared Absorption''.  In this
+paper absorption spectra in Fig.~5(b) calculated with electrostatic
+plasmon hybridization method showes, as it was stated with a reviewer,
+a significat increase of the band when packing particles to an
+array. This broadering originates from the appearance of collective
+mode (or, in other words, the hybridization of plasmon responce of
+several particles) with additional impact from retardation effects. It
+can be of great intereset (including applied examples) to apply the
+same approch from our manuscript to this system. It should be possible
+to optimize simultniously geometry of individual particles and their
+positioning in array to degenerate several absorption resonances of
+such collective modes in order to achieve superabsorption. However, we
+do not have any working code for plasmon hybridization method to check
+it with our optimizer. Using brute force approach with FDTD simulation
+looks to be rather computationaly expensive without any prior
+analytical estimations.
 
-For a fast check of this idea we simulated the 3x3 rectangular array
-of spheres (to provide a good coupling both in E and H direcitons)
-with the separation of 4 nm (so it is only 2 mesh cells to resolve the
-separation in the used coarse grid, selected to get a resonable timing
-of a 3D full-wave simulation) Fig~\ref{fig:fdtd-3x3}(a). Several
-collective modes can be recognized from field distribution while
-changing the incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e). However,
-for used materials, nanoparicle and array designs, spectral range, and
-plane of polarization we observed a blue shift of absoption responce
-(it looks to be dominated with silver plasmon resonance)
-Fig~\ref{fig:fdtd-3x3}(b), which is opposite to results of Le et
-al. in Fig.~5(b) of their paper.
+However, as a proof of concept, we simulated with FDTD method the 3x3
+rectangular array of spheres (to provide a good coupling both in E and
+H direcitons) with the separation of 4 nm (so it is only 2 mesh cells
+to resolve the separation in the used coarse grid, selected to get a
+resonable timing of a 3D full-wave simulation)
+Fig~\ref{fig:fdtd-3x3}(a). Several collective modes can be recognized
+from field distribution while changing the incident wavelength
+Fig~\ref{fig:fdtd-3x3}(c-e) (it can be interesting to compare this results
+with Fig 4 of Le et al. paper)  . However, for used materials, nanoparicle
+and array designs, spectral range, and plane of polarization we
+observed a blue shift of absoption responce (it looks to be dominated
+with silver plasmon resonance) Fig~\ref{fig:fdtd-3x3}(b), which is
+opposite to results of Le et al. in Fig.~5(b) of their paper.
 
-This way it looks that using particle array adds a whole banch of new
-physical features which deserve a separate investigation. No changes
-to the manuscript were done.
 \begin{figure}
@@
     \caption{ FDTD simulation of 3x3 grid of spheres optimized for
-      absorption at 525~nm(a) Fullwave simulation prepared in Lumerical FDTD. (b)
-     Absorption spectra of stand-alone spheres and in dimer
-     configuration with separation between spheres of 0, 10, and
-     30~nm, particles are in H-k plane (c) Separation 0 and 30~nm for
-     particles in E-k plane (d) Field distribution at 500nm of
-     incedent wavelength for particles in E-k plane with separation of
-     30~nm.\label{fig:fdtd-3x3}}%
+      absorption at 525~nm(a) Fullwave simulation prepared in
+      Lumerical FDTD. (b) Cross-section absorption spectra (c,d,e)
+      Field distribution at 408, 452, and 600nm of incident light.\label{fig:fdtd-3x3}}%
 \end{figure}
+
+Materials Letters 158, 262265 (2015) titled ``Dielectric shell
+modulated plasmonic crystal for novel light absorption meta-surface''
+provide another type of plasmonic coupling. In contrast to most other
+works with hot spots located between the particles it this paper field
+distributions presented in Fig 2 (b-d) is mostly localized inside the
+particles and if Fig 2 (e) it is about the same order inside and
+between the particles. This way due to relatively small coupling
+between the particles we should expect to find this resonances in a
+stand-alone particle, which was easy to reproduce. The result of Mie
+calcultion for gold sphere (material data is from P. B. Johnson and
+R. W. Christy. Optical Constants of the Noble Metals, Phys. Rev. B 6,
+4370-4379 (1972)) of diameter d=25~nm covered with lossless and
+dispersionless dielectric with refractive indes n=2.5 and d=65~nm in
+Fig.~\ref{fig:Au-core-shell}. However, there was the only one electric
+dipole resonance at 637~nm, futhermore, 3D FDTD simulation of such a particle
+with a gold substrate (as is was used in the paper) and periodic
+boundary condition for a HCP array lead to appearance of a peak at
+678~nm in contrast with the simulation presented in Fig. 1(b) of the
+paper.  We do not have a good explanation for a such disagreement.
+\begin{figure}
+  \includegraphics[width=0.95\textwidth]{Au-core-shell}\\
+  c)\\
+   \includegraphics[width=0.95\textwidth]{fdtd-hcp}
+  \caption{Mie simulation for core-shell particle with gold core (a)
+    Mie absorption coefficients (b) Mie efficency for scattering,
+    absorbtion, extinction and backscattering.\label{fig:Au-core-shell}}
+\end{figure}
+
+This way it looks that using particle array adds a whole banch of new
+physical features which deserve a separate investigation. No changes
+to the manuscript were done.
 
@@
 
+\newpage
 \begin{minipage}{1.0\linewidth}

### 2015-09-19 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py

@@ -112,6 +112,7 @@ def SetXM(design, extra_width = 0, WL=0, epsilon_Si=0, epsilon_Ag=0):
         m = np.ones((2), dtype = np.complex128)
         m[0] = index_Ag/nm
         m[1] = index_Si/nm
+    print m    
     return x, m
 ###############################################################################
 def calc(design, extra_width, WL, epsilon_Si, epsilon_Ag):
@@ -185,7 +186,7 @@ design = 1 #AgSi
 # WL = 500
 from_WL = 400
 to_WL = 600
-total_points = 600
+total_points = 10
 for i in xrange(1):
     extra_width = 0
     fname = "Ag-Si-channels-TotalR036-calc.dat"

### 2015-09-20 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
second reviewer first comment

@@
 distributions presented in Fig 2 (b-d) is mostly localized inside the
-particles and if Fig 2 (e) it is about the same order inside and
-between the particles. This way due to relatively small coupling
+particles and in Fig 2 (e) it is about the same order inside and
+between the particles. It looks to be quite reasonable as far as
+relatively small metallic core (d=25~nm) is covered with thick
+dielectric shell (d=65~nm). This way due to relatively small coupling
 between the particles we should expect to find this resonances in a
@@
 Fig.~\ref{fig:Au-core-shell}. However, there was the only one electric
-dipole resonance at 637~nm, futhermore, 3D FDTD simulation of such a particle
-with a gold substrate (as is was used in the paper) and periodic
-boundary condition for a HCP array lead to appearance of a peak at
-678~nm in contrast with the simulation presented in Fig. 1(b) of the
-paper.  We do not have a good explanation for a such disagreement.
+dipole resonance at 637~nm, futhermore, 3D FDTD simulation of such a
+particle with a gold substrate (as is was used in the paper) and
+periodic boundary condition for a HCP array lead to appearance of a
+peak at 666~nm (for polarization oriented to far neighbor) in
+Fig~\ref{fig:Au-core-shell}(c)  in contrast
+with the simulation presented in Fig. 1(b) of the paper with several
+resonances in range 700-1100~nm.  We do not
+have a good explanation for such a disagreement.
 \begin{figure}
@@
     Mie absorption coefficients (b) Mie efficency for scattering,
-    absorbtion, extinction and backscattering.\label{fig:Au-core-shell}}
+    absorbtion, extinction and backscattering.(c)\label{fig:Au-core-shell}}
 \end{figure}
@@
 
-\begin{tabular}[!H]{p{0.9\textwidth}}
-`` Some text''
-\end{tabular}
+%% \begin{tabular}[!H]{p{0.9\textwidth}}
+%% `` Some text''
+%% \end{tabular}
 
@@
 \end{minipage}
+
+We added a sentence to the end of first paragraph of page 3 right
+column after ``From a practical point of view, it is
+quite important that the maximum can be reached in a bi-layer
+structure, instead of a triple-layer, since it should be easier and
+cheaper to fabricate.''
+
+New sentencs: ``At the same time superabsorption designs achieve the
+best absorption efficency for large particles (with
+$R>60$~nm for provided materials and layers order), which can be
+relevant if fine control of layer thickness is not available.''
 

### 2015-09-20 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
partial anwser for reviewer 2 comment 2

@@
 
-New sentencs: ``At the same time superabsorption designs achieve the
-best absorption efficency for large particles (with
-$R>60$~nm for provided materials and layers order), which can be
-relevant if fine control of layer thickness is not available.''
+New sentencs: ``At the same time the best absorption efficency for
+large particles (with $R>60$~nm for provided materials and layers
+order) was achieved with superabsorption designs, which can be
+relevant for the case of layer thickness fine control is not
+available.''
 
@@
 \end{tabular}
+
+The sort answer it that it was not possible to fit magnetic quadroupole to the particle of
+smaller size, however, it is hard to keep it been efficient for larger
+sizes. However, the contribution of the electric diple is also
+very important.
+
+To present this idea in more details we run an optimization with
+changed fitness function - we requested to maximize the impact of
+electric dipole to the absorption efficiency.
+
+\begin{figure}
+  \includegraphics[width=0.35\textwidth]{overview-Qabs-a1}
+  d)
+   \includegraphics[width=0.55\textwidth]{overview-Qabs-all-a1}
+  \caption{Mie simulation for core-shell particle with gold core (a)
+    Mie absorption coefficients (b) Mie efficency for scattering,
+    absorbtion, extinction and backscattering.(c)\label{fig:Au-core-shell}}
+\end{figure}
 

### 2015-09-20 2015-Ladutenko-Qabs/data/plot-SiAgSi-overview.py

@@ -26,7 +26,7 @@ def load_data(fname):
 
 fname = "2015-04-01-Qabs-SiAgSi-overview"
 data, data_spaced = load_data(fname)
-for i in xrange(1, len(data[:,1])):
+for i in xrange(1, len(data[:,1])-2):
     if data[i-2,1]<=data[i,1] and data[i+2,1]<=data[i,1]:
         print(data[i,:])
 

### 2015-09-20 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
rev2 comm2

@@
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-  \quad &  2.      In Fig. 2, we noticed a discontinuity at ~80
+  \quad &  2.      In Fig. 2, we noticed a discontinuity at $\sim$80
   nm. The authors explain it as the design supporting electric dipole
@@
 
-The sort answer it that it was not possible to fit magnetic quadroupole to the particle of
-smaller size, however, it is hard to keep it been efficient for larger
-sizes. However, the contribution of the electric diple is also
-very important.
+The sort answer it that it was not possible to fit magnetic
+quadroupole to the particle of smaller size, however, it is hard to
+keep it been efficient for larger sizes. However, the contribution of
+the electric diple is also very important.
 
@@
 changed fitness function - we requested to maximize the impact of
-electric dipole to the absorption efficiency.
-
+electric dipole to the absorption efficiency, results are presented in
+Fig.~\ref{fig:a1max}. During the increase of the total $R$ the
+$\tilde{a}_1$ rapidly reaches it`s theoretical maximum. Optimizer was
+quite successful to keep it for all larger values of $R$. During the
+increase of $R$ other dipole resonances can appear. Such an appearence
+of $\tilde{b}_2$ formes the discussed maxima at $\sim 80$~nm, it is
+cleary observed at Fig.~\ref{fig:a1max}(b).
 \begin{figure}
   \includegraphics[width=0.35\textwidth]{overview-Qabs-a1}
-  d)
-   \includegraphics[width=0.55\textwidth]{overview-Qabs-all-a1}
-  \caption{Mie simulation for core-shell particle with gold core (a)
-    Mie absorption coefficients (b) Mie efficency for scattering,
-    absorbtion, extinction and backscattering.(c)\label{fig:Au-core-shell}}
+   \includegraphics[width=0.60\textwidth]{overview-Qabs-all-a1}
+  \caption{(a-c) Same as Fig.2 of the manuscript with the optimization
+    aim to maximize contibution of electric dipole to
+    absorption. Missing points did not pass the additional check for
+    stability of plotting script. (d) $Q_{abs}$ for maximized
+    $\tilde{a}_1$ from the first subplot of present figure without the
+    additional stability check compared with $Q_{abs}$ optimization
+    regarding all multipoles.\label{fig:a1max}}
 \end{figure}

### 2015-09-24 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Updated simulation of periodic HPC array
Update response-letter.tex
Ilya edits

--- 2015-09-20 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
@@
 \end{center}
-Dear Editors,
+Dear Editor,
 \\
 \\
-I am writing to respond to the reviewers' critical comments on our
-manuscript entitled, ``Superabsorption of light by nanoparticles''
-NR-COM-08-2015-005468, which we aim for publication in Nanoscale.
+Many thanks for sending us referees’ reports on our manuscript entitled “Superabsorption of light by nanoparticles” by K.
+Ladutenko et al.
+(editorial code NR-COM-08-2015-005468).
+We are pleased with overall very positive tone of these reports, as well as with referees’ constructive comments.
 
-As a group of authors interested in high quality input we know that
-unbiased and professional review is an important part of a publication
-process.  This way we would like to stress you attantion to the second
-comment of the first reviewer. He had listed a number of publications,
-however, it is hard to belive that this list is unbiased after looking
-to the authors names; several authors from Jiangxi Normal University are
-listed in all of this publications (it looks like some names have two
-spelling options with and without the dash).  We provide our findings here:
-\begin{enumerate}
-\item ACS Applied Materials & Interfaces, 7, 4962-4968 (2015)\\
-  Zhengqi Liu, Xiaoshan Liu,  Shan Huang,  Pingping Pan,  Jing Chen,
-  Guiqiang Liu, and Gang Gu\\
-  DOI: 10.1021/acsami.5b00056
-\item Materials Letters 158, 262-265 (2015)\\
-  Zhengqi Liu , Guiqiang Liu, Xiaoshan Liu, Shan Huang, Yan Wang,
-  Pingping Pan, Mulin Liu\\
-  http://dx.doi.org/10.1016/j.matlet.2015.06.029
-\item Applied Physics Letters, 104, 081116 (2014)\\
-  Zheng-qi Liu, Hui-bai Shao,  Gui-qiang Liu, Xiao-shan Liu, Hai-qing Zhou, Ying Hu,
-  Xiang-nan Zhang, Zheng-jie Cai, and Gang Gu\\
-  http://dx.doi.org/10.1063/1.4867028
-\item Nanotechnology, 24, 155203 (2013)\\
-  Zheng-qi Liu, Gui-qiang Liu, Hai-qing Zhou, Xiao-shan Liu,
-  Kuan Huang, Yuan-hao Chen, and Guo-lan Fu\\
-  doi:10.1088/0957-4484/24/15/155203
-\end{enumerate}
-
-We would like to thank the editor and two anonymous reviewers for their
-constructive comments, which helped us to improve the
-manuscript. Below, we address all comments point-by-point, discussing
-the subsequent modifications.
+We have addressed all the comments of the referees, and we present our response and the summary of the changes made to the manuscript below.
 
@@
 
-This comment touches two aspects of broadband performance, namely,
-properties of a stanalone particle and in interaction with other
-particles.  The first case, as it was correctly mentioned with the
-reviewer, has some limiations.  We can design a band, which will be
-broader of a typical band for a given multipole, however, width is
-not extremly large.  To illustrate this we have run an optimization
-with a goal to provide a prediefined separation between multipole
-resonanses (Fig.~\ref{fig:broadband}).
-\begin{figure}
-  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth} 
-   \includegraphics[width=0.95\textwidth]{band20-em}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth} 
-   \includegraphics[width=0.95\textwidth]{band20-em-ch}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)    \end{flushleft}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth} 
-   \includegraphics[width=0.95\textwidth]{band80-em}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth} 
-    \includegraphics[width=0.95\textwidth]{band80-em-ch}
-  \end{minipage}  
-  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     e)    \end{flushleft}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     f)    \end{flushleft}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth} 
-   \includegraphics[width=0.95\textwidth]{band80-e}
-  \end{minipage}
-  \begin{minipage}[h]{0.49\textwidth} 
-    \includegraphics[width=0.95\textwidth]{band80-e-ch}
-  \end{minipage}  
-   \caption{Single particle desings for separation between dipole
-     resonances of 20 nm (a-b) and 80 nm (c-f). Left column with
-     figures (a,c,e) contains spectra of Mie efficiency for extinction
-     (Qext), scattering (Qsca), absorption (Qabs, blue curve) and
-     backscattering (Qbk). Right column (b,d,f) presents contibution
-     of multipoles to the spectra (red and green stands for electric
-     and magnetic dipoles, blue and cyan corresponds to quadrupole
-     electric and magnetic modes, respectively). It is interesting to
-     note that for 80 nm separation optimizer was able to find a
-     desing with two resonances of a dipole mode (f). We suppose that
-     the latter most likely has the same nature as the response
-     presented in Fig. 3(c,d) of the manuscript: there are several
-     resonances of an electric dipole response binded to different
-     layers of the particle.\label{fig:broadband}}%
-\end{figure}
-Our observation is the following: while the separation is small enough
-compared to a multiple resonance width the optimizer was successful to
-find desings with electric and magnetic dipole. If the separation is
-large the absorption band splits into two. For large separation is is
-also possible to obtain two resonanses of the electric dipole
-response, located at predefined position
-(Fig. \ref{fig:broadband}(e,f)).  Still there are not so many
-possibilities here to design a good broadband. To control the
-bandwidth at a given spectral position we need to involeve relatively
-large particles. This leads to appereance of resonances (and
-absorbtion) out of the designed band which are hard to control or
-suppress in disscussed triple-layer structure.
+We thank the referee for suggestion.
+First, we would like to note that the term "broadband" is quite loose, when not defined explicitly.
+For example, if we compare our absorption band with the whole C-band of the optical fibres, which is used to carry Terabits of data, and which is just 35 nm wide, then our absorbers are extremely broadband, since they have the bandwidth approaching 100 nm.
+Compared to the whole visible spectrum, however, indeed our absorption band is not very broad.
+So, to address the referee comment, we decided to study the possible ways to enhance the width of the absorption band.
 
-To answer the second part of the comment, related to possiblity of
-usage of the pariticle array with dispered sizes, we designed two
-particles with best absorption effeciency at 475~nm and 525~nm (outer
-radius 34 and 38~nm) and
-simulatied them both with FDTD method using Lumerical FDTD Solutions.
-Sketch of the simulated system and final results are in
-Fig.~\ref{fig:fdtd}. To verify our FDTD we fist simulated absorption
-of standalone spheres, the obtained postions and amplitudes of
-resonances to corresponde well with Mie caclulations.
+We can think of a two possible approaches to achieve the broadband performance.
+First approach utilizes the mix of different particles, while the second approach uses several resonances within one particle.
+The later approach is nontrivial and requires large additional study, that would deserve a separate publication.
+The first approach, however, mentioned by the Referee, is more straightforward, and we can use a mixture of different particles, so that various sized particles absorb different wavelengths.
+To illustrate this we have run an optimization procedure to find two designs: one absorbs at 475~nm, while another is centered at 525~nm (outer radii 34 and 38~nm, respectively).
+We then combine such particles to form a dimer, and calculate its properties using Lumerical FDTD Solutions.
+Sketch of the simulated system and final results are shown in Fig.~\ref{fig:fdtd}.
+As a reference, we also perform FDTD simulations of standalone spheres, and the obtained positions and amplitudes of resonances match well results of the Mie calculations.
 \begin{figure}
@@
   \end{minipage}
-    \caption{(a) Fullwave simulation prepared in Lumerical FDTD. (b)
-     Absorption spectra of stand-alone spheres and in dimer
-     configuration with separation between spheres of 0, 10, and
-     30~nm, particles are in H-k plane (c) Separation 0 and 30~nm for
-     particles in E-k plane (d) Field distribution at 500nm of
-     incedent wavelength for particles in E-k plane with separation of
-     30~nm.\label{fig:fdtd}}%
+    \caption{(a) Sketch of the simulated dimer in full wave simulations by Lumerical FDTD. (b)
+     Absorption spectra of stand-alone spheres and in dimer configuration with separation between spheres of 0, 10, and
+     30~nm, particles are in H-k plane; (c) Separation 0 and 30~nm for
+     particles in E-k plane; (d) Field distribution for the incident wavelength of500 nm for particles in E-k plane with separation of 30~nm.\label{fig:fdtd}}%
 \end{figure}
-Next step was to find out the possible interactions between two
-spheres, so we run a simulation in dimer configuration with zero
-separation between spheres and with 10 and 30~nm separation.  The
-resulting spectra has a strong contribution from standalone
-resonances, while coupling effects seems to be minor.  This can be
-easily explained from field distribution in Fig.~4(c) of the
-manuscript. Positioning spheres in H-k plane we are exploting the
-feature of field being highly localized inside the the sphere.  For
-sure arranging spheres in other plane, increasing the number of
-spheres can change the amount of coupling between the spheres. As an
-example we tested arragement of sphers in E-k plane
-Fig.~\ref{fig:fdtd}(c); for zero separation the intraction between
-spheres is strong, however, due to near-field nature of this coupling
-it rapidly decays with the separation width Fig.~\ref{fig:fdtd}(d),
-for separation of 30~nm responses of individual particles dominate in
-overall spectra for both planes of polarization. This way we show that
-in principle it is possible to construct an absoption band of an array
-of dispersed particles simply optimizing the properties of every
-single sphere carefully tuning the distance between particles (which
-still is much smaller than the wavelength).
 
-We changed the manuscript from ``As a result, one can design
-spectrally-selective absorbers or broadband absorbers with almost
-arbitrary prescribed properties.'' to ``As a result, one can design
-absorbers with broadened spectra or spectrally-selective absorbers
-with almost arbitrary prescribed properties.  Due to strong
-localization of electric dipole field (espatially in H-k plane) it is
-also possible to desing dispersed size arrays particles by defining
-their individual properties for composite absorption spectra; we
-obtained rather small coupling between particles during additional
-simulation using FDTD method.''
+When we mix the different sized spheres, there will be an effect of their mutual interaction.
+To take this into account, we simulate a dimer configurations with 0 nm, 10 nm and 30 nm separation between spheres.
+The resulting spectra have a strong contribution from standalone resonances, while coupling effects seems to be relatively minor.
+This can be explained from modal field distribution in Fig.~4(c) of the manuscript.
+Positioning spheres in H-k plane we are exploiting the features of fields being highly localized inside the spheres.
+Arranging spheres in other planes with respect to incident polarization, or increasing the number of interacting spheres can change the effect of coupling.
+As an example, we tested arrangement of spheres in E-k plane Fig.~\ref{fig:fdtd}(c); for zero separation the interaction between spheres is strong, however, due to near-field nature of this coupling, it rapidly decays with the separation width Fig.~\ref{fig:fdtd}(d), for separation of 30~nm responses of individual particles dominate in overall spectra for both planes of polarization.
+This way we show that
+in principle it is possible to construct an absorption band of an array of dispersed particles simply optimizing the properties of individual particles.
+
+In order to reflect these findings in the manuscript, we have rewritten the text from ``As a result, one can design
+spectrally-selective absorbers or broadband absorbers with almost arbitrary prescribed properties.'' to ``As a result, one can design absorbers with broad spectra or spectrally-selective absorbers with almost arbitrary prescribed properties.
+One can also achieve broadband performance by mixing particles whose absorption is optimised for different wavelengths.
+We have verified that due to strong localization of electric dipole field it is possible to desing dimers whose absorbing properties are dominated by the properties of individual particles, and not by their mutual interaction.
+As a result, by appropriately spacing the resonances of individual particles, their mixture will exhibit a combined broadband response.''
 
@@
 % Lumerical - periodic boundary - попробовать несколько частиц
-We would like to thank the reviewer for provided citations, some of
-them turned to be really interesting. In order to reply this comment
-first of all we checked all the citations provided.
-
-ACS Applied Materials \& Interfaces, 7, 4962-4968 (2015) titled
-``Automatically Acquired Broadband Plasmonic-Metamaterial Black
-Absorber during the Metallic Film-Formation'' uses metal film
-formation process to achive very wideband performance. However, the
-absorption in this case is highly dependable on the thickness of the
-underlaying silica layer.  This way we can argue against the conlusion
-of the paper ``These results also confirm that an ultrathin
-meta-surface layer (less than 10 nm) structure can produce nearly
-ideal broadband light absorption'' - to achieve experimentally
-observed performance the whole system (including silica layer and gold
-under-layer) is needed. A more detailed simulation can give some
-answers, however, we expect that most of the absorbtion happends in
-the gold under-layer, while the metasurface and silica layer serves to
-be kind of an impedance matcher.  This proposal is confirmed with the
-experemental results in Fig. 5 of the paper, for 100~nm silica layer
-the absorption is low.  At the same time the wideband performance can
-be related to the fractal-type surface, as it is shown in Fig.~2(f)
-Moreover, it should be relativly easy to estimate the thermal
-behaviour of such a metasurface, as soon as isolated particles on the
-top of the silica have no heat transfer with electrons to the
-substrate.  If we suppose that most of the light is absorbed in top
-layer this should lead to overheating of the metasurface due to
-extreamly low geometrical volume. For this case in steady state we
-should expect a large temperature gradient as soon as gold thermal
-condutivity 310 $W/(m\cdot K)}$ is about 200 fold larger than silica
-  $1.4 W/(m\cdot K)}$. Measuring temperature via infrared
-    radiation from both sides of the sample can provide hints to
-    distinguish the absortption origin.
-
-Anyway, albiet of the exciting experimental results obtained in the
-paper they exploit phsycal effect that differs a lot from the one
-proposed in our manuscript; our particles were desinged to absorb the
-incident power by themselfs, and they work perfectly in a stand-alone
-mode.  This can be extremly conviniet, for example, for nanophotonics
-application, when the available volume to place an absorber can be
-very limited. Same overheating question can also appear here, limiting the
-operational power range.
-
-Applied Physics Letters, 104, 081116 (2014) titled ``$\lambda^3$/20000
+We would like to thank the reviewer for the references.
+We have included them into our manuscript with relevant discussions, with one exception.
+Reference Applied Physics Letters, 104, 081116 (2014) with the  title "$\lambda^3$/20000
 plasmonic nanocavities with multispectral ultra-narrowband absorption
-for high-quality sensing'' is cleary not related to ``broadband light
-coupling and confinement'' and was
+for high-quality sensing'' is not related to broadband light coupling and confinement'' and was
 probably listed by an accident.
 
-Nanotechnology, 24, 155203 (2013) titled ``Near-unity transparency of
-a continuous metal film via cooperative effects of double plasmonic
-arrays'' describes light interaction with a gold film, which has an
-array of gold spheres positioned on top, bottom, or both sides of the
-film.  Provided simulations show a strong field enhancement between
-the spheres. Absorption related part of the paper references [18-21],
-where [20] is Le F, Brandl D W, Urzhumov Y A, Wang H, Kundu J, Halas N
-J, Aizpurua J and Nordlander P 2008 ACS Nano 2 707 titled ``Metallic
-Nanoparticle Arrays: A Common Substrate for Both Surface-Enhanced
-Raman Scattering and Surface-Enhanced Infrared Absorption''.  In this
-paper absorption spectra in Fig.~5(b) calculated with electrostatic
-plasmon hybridization method showes, as it was stated with a reviewer,
-a significat increase of the band when packing particles to an
-array. This broadering originates from the appearance of collective
-mode (or, in other words, the hybridization of plasmon responce of
-several particles) with additional impact from retardation effects. It
-can be of great intereset (including applied examples) to apply the
-same approch from our manuscript to this system. It should be possible
-to optimize simultniously geometry of individual particles and their
-positioning in array to degenerate several absorption resonances of
-such collective modes in order to achieve superabsorption. However, we
-do not have any working code for plasmon hybridization method to check
-it with our optimizer. Using brute force approach with FDTD simulation
-looks to be rather computationaly expensive without any prior
-analytical estimations.
+We agree with the referee that closely packed particles can lead to the increase of the bandwidth.
+This broadening originates from the appearance of a collective mode (or, in other words, the hybridization of plasmon responses of several particles) with additional impact from retardation effects.
+While for some resonances, as we have discussed in the response to the previous comment, the interaction between our nanoparticles can be weak, it should still be possible to optimize simultaneously the geometry of individual particles and the array parameters to achieve enhanced absorption.
+As a proof of concept, we performed FDTD simulations of the 3x3 square array of spheres (to provide a good coupling both in E and
+H directions) with the separation of 4 nm, see Fig~\ref{fig:fdtd-3x3}(a). Several collective modes can be recognized
+from field distribution while changing the incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e).
+We see that for the used materials, nanoparicle and array designs, spectral range, and plane of polarization, we observed a broadened resonance, with the broadening mostly occurring in the blue shift direction Fig~\ref{fig:fdtd-3x3}(b).
 
-However, as a proof of concept, we simulated with FDTD method the 3x3
-rectangular array of spheres (to provide a good coupling both in E and
-H direcitons) with the separation of 4 nm (so it is only 2 mesh cells
-to resolve the separation in the used coarse grid, selected to get a
-resonable timing of a 3D full-wave simulation)
-Fig~\ref{fig:fdtd-3x3}(a). Several collective modes can be recognized
-from field distribution while changing the incident wavelength
-Fig~\ref{fig:fdtd-3x3}(c-e) (it can be interesting to compare this results
-with Fig 4 of Le et al. paper)  . However, for used materials, nanoparicle
-and array designs, spectral range, and plane of polarization we
-observed a blue shift of absoption responce (it looks to be dominated
-with silver plasmon resonance) Fig~\ref{fig:fdtd-3x3}(b), which is
-opposite to results of Le et al. in Fig.~5(b) of their paper.
+We believe that the detailed study of the effect of arranging the elements in array is a whole new project, and it lies outside the scope of our current manuscript.
+We have mentioned, however, in the revised manuscript that further control of the absorption spectrum can be achieved by arranging our spherical structures in a periodic and non-periodic arrays.
 
@@
 
-    \caption{ FDTD simulation of 3x3 grid of spheres optimized for
-      absorption at 525~nm(a) Fullwave simulation prepared in
-      Lumerical FDTD. (b) Cross-section absorption spectra (c,d,e)
-      Field distribution at 408, 452, and 600nm of incident light.\label{fig:fdtd-3x3}}%
+    \caption{ FDTD simulation of a 3x3 array of spheres, which are individually optimized for
+      absorption at 525~nm(a) Fullwave simulation performed in Lumerical FDTD. (b) Cross-section absorption spectra (c,d,e)
+      Field distribution for the wavelengths of 408, 452, and 600 nm.\label{fig:fdtd-3x3}}%
 \end{figure}
-
-Materials Letters 158, 262265 (2015) titled ``Dielectric shell
-modulated plasmonic crystal for novel light absorption meta-surface''
-provide another type of plasmonic coupling. In contrast to most other
-works with hot spots located between the particles it this paper field
-distributions presented in Fig 2 (b-d) is mostly localized inside the
-particles and in Fig 2 (e) it is about the same order inside and
-between the particles. It looks to be quite reasonable as far as
-relatively small metallic core (d=25~nm) is covered with thick
-dielectric shell (d=65~nm). This way due to relatively small coupling
-between the particles we should expect to find this resonances in a
-stand-alone particle, which was easy to reproduce. The result of Mie
-calcultion for gold sphere (material data is from P. B. Johnson and
-R. W. Christy. Optical Constants of the Noble Metals, Phys. Rev. B 6,
-4370-4379 (1972)) of diameter d=25~nm covered with lossless and
-dispersionless dielectric with refractive indes n=2.5 and d=65~nm in
-Fig.~\ref{fig:Au-core-shell}. However, there was the only one electric
-dipole resonance at 637~nm, futhermore, 3D FDTD simulation of such a
-particle with a gold substrate (as is was used in the paper) and
-periodic boundary condition for a HCP array lead to appearance of a
-peak at 666~nm (for polarization oriented to far neighbor) in
-Fig~\ref{fig:Au-core-shell}(c)  in contrast
-with the simulation presented in Fig. 1(b) of the paper with several
-resonances in range 700-1100~nm.  We do not
-have a good explanation for such a disagreement.
-\begin{figure}
-  \includegraphics[width=0.95\textwidth]{Au-core-shell}\\
-  c)\\
-   \includegraphics[width=0.95\textwidth]{fdtd-hcp}
-  \caption{Mie simulation for core-shell particle with gold core (a)
-    Mie absorption coefficients (b) Mie efficency for scattering,
-    absorbtion, extinction and backscattering.(c)\label{fig:Au-core-shell}}
-\end{figure}
-
-This way it looks that using particle array adds a whole banch of new
-physical features which deserve a separate investigation. No changes
-to the manuscript were done.
-
-%% We totally agree with the reviewer's statement. It seems that our
-%% manuscript was not clear enough at this point. ...  However, as we
-%% compare final optimization results we conclude that .... To make it
-%% clearer we rewrite this part of the manuscript as follows:
-
-%% \begin{tabular}[!H]{p{0.9\textwidth}}
-%% `` Some text''
-%% \end{tabular}
-
-%% It should be mentioned that .... No changes to the
-%% manuscript were made.
 
@@
 
-We added a sentence to the end of first paragraph of page 3 right
-column after ``From a practical point of view, it is
-quite important that the maximum can be reached in a bi-layer
-structure, instead of a triple-layer, since it should be easier and
-cheaper to fabricate.''
+The super-absorption has a physical meaning of a regime, when we create a structure, which has several highly absorbing resonances overlapping in frequency, so that total absorption is larger than what can be created in the structure.
+The main conclusions of the paper are that
+a) We can create structures that shows superabsorption
+b) For small particles (below 60nm), the efficiency of absorption is higher for single mode regime.
+c) For larger particles the superabsorption regime allows to achieve best efficiency of absorption.
 
-New sentencs: ``At the same time superabsorption designs achieve the
-best absorption efficency for large particles (with
-$R>60$~nm for provided materials and layers order), which can be
-relevant if fine control of layer thickness is not available.''
+To make this more clear in the manuscript, we have made the following changes to the manuscript:
 
-%% Для маленьких толщин лучше простой диполь, если есть ограничения на
-%% минимальный размер частицы - лучше суперпоглотитель. Или, например,
-%% если важно ещё и абсолютное поглощение от одиночной частицы - большая
-%% частица поглощает больше, для неё оптимальнее работа в супер- режиме.
-
-%% There are several points to be treated carefully when discussing...
-%%  However, to claim this concept to be a general one ...  more simulations
-%% should be performed.
+In the end of the first paragraph of page 3, right column, after ``..., since it should be easier and cheaper to fabricate.'' We add: ``At the same time the best absorption efficiency for larger particles (with $R>60$~nm for provided materials) can be achieved in superabsorption regime.
+This may be important when fabrication of smaller multi-layer particles is not available.''
 
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-  \quad &  2.      In Fig. 2, we noticed a discontinuity at ~80
+  \quad &  2.      In Fig. 2, we noticed a discontinuity at $\sim$80
   nm. The authors explain it as the design supporting electric dipole
@@
 \end{tabular}
+
+The short qualitative answer to this is that it is not possible to excite the magnetic quadrupole resonance to the particle of a smaller size, and, it is hard to keep it efficient for larger sizes, while also maintaining the large contribution of the electric dipole.
+
+To present this idea in more details we run an optimization with changed fitness function - we maximize the absorption efficiency of only the electric dipole, with results presented in Fig.~\ref{fig:a1max}.
+With the increase of the particle radius $R$ the $\tilde{a}_1$ rapidly reaches its theoretical maximum.
+Optimizer was
+quite successful in maintain this for all larger values of $R$.
+When we increase the $R$, other multipole resonances can appear.
+Such an appearance of $\tilde{b}_2$ formes the discussed maxima at $\sim 80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).
+
+Another way to qualitatively explain the effect is the following.
+We have a multiple resonance structure, and by changing parameters we can overlap several different resonances.
+Depending on the total particle size, different combination of resonances can give maximum absorption, therefore it is not surprizing that in a certain parameter range, the combination of electric dipole and magnetic quadrupole can give us the best possible absorption.
+
+\begin{figure}
+  \includegraphics[width=0.35\textwidth]{overview-Qabs-a1}
+   \includegraphics[width=0.60\textwidth]{overview-Qabs-all-a1}
+  \caption{(a-c) Same as Fig.2 of the manuscript with different fitness function: the optimization
+    aims to maximize the electric dipole absorption.
+(Missing points did not pass the stability test.) (d) $Q_{abs}$ for maximized  $\tilde{a}_1$ from the first subplot of present figure without the additional stability test compared with $Q_{abs}$ optimization regarding all multipoles.\label{fig:a1max}}
+\end{figure}
 
@@
 
-%% Да, он прав, основной вклад от ядра, остальные делают верхушку
-%% плоской. Фишка в том что резонанс плоский, а не широкий.
+We thank the referee for pointing this out, we must have not explained this point clearly.
+The most interesting feature of this resonance that we wanted to bring attention to is that the resonance has an unusual flat top part.
+The main shape and width of the resonance is explained by one dominating dipole mode, as it is seen in the mode decomposition in Fig.~3(d).
+Two additional electric dipole resonances are much weaker, but their contribution "flattens" the top of the combined absorption resonance.
+We have clarified this in the modified manuscript.
 
@@
 \end{tabular}%
-%% Илья
+
+We have worked on improving the readability of the manuscript.
+
 \\

### 2015-09-24 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Text reflow
Proposed changed to the manuscipt are now in the responce letter

@@
 Dear Editor,
-\\
-\\
-Many thanks for sending us referees’ reports on our manuscript entitled “Superabsorption of light by nanoparticles” by K.
-Ladutenko et al.
-(editorial code NR-COM-08-2015-005468).
-We are pleased with overall very positive tone of these reports, as well as with referees’ constructive comments.
 
-We have addressed all the comments of the referees, and we present our response and the summary of the changes made to the manuscript below.
+Many thanks for sending us referees’ reports on our manuscript
+entitled “Superabsorption of light by nanoparticles” by K. Ladutenko
+et al. (editorial code NR-COM-08-2015-005468). We are pleased with
+overall very positive tone of these reports, as well as with referees’
+constructive comments.
+
+We have addressed all the comments of the referees, and we present our
+response and the summary of the changes made to the manuscript below.
 
@@
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-\quad & 1.
-The authors claimed “Combined effect of these resonances is presented to produce the flat and relative broadband electric resonance response.” Nevertheless, the broadened absorption band is not very broad.
-Is there any further way to predict a broadband light absorption.
-For instance, a broadband absorption in the whole visible spectral range.
-Maybe, a possible way of using the dispersed size scale nanoparticles should be added for improving the study.
+\quad & 1. The authors claimed “Combined effect of these resonances is
+presented to produce the flat and relative broadband electric
+resonance response.” Nevertheless, the broadened absorption band is
+not very broad. Is there any further way to predict a broadband light
+absorption. For instance, a broadband absorption in the whole visible
+spectral range. Maybe, a possible way of using the dispersed size
+scale nanoparticles should be added for improving the study.
 \end{tabular}\\
 
-We thank the referee for suggestion.
-First, we would like to note that the term "broadband" is quite loose, when not defined explicitly.
-For example, if we compare our absorption band with the whole C-band of the optical fibres, which is used to carry Terabits of data, and which is just 35 nm wide, then our absorbers are extremely broadband, since they have the bandwidth approaching 100 nm.
-Compared to the whole visible spectrum, however, indeed our absorption band is not very broad.
-So, to address the referee comment, we decided to study the possible ways to enhance the width of the absorption band.
+We thank the referee for suggestion. First, we would like to note that
+the term "broadband" is quite loose, when not defined explicitly. For
+example, if we compare our absorption band with the whole C-band of
+the optical fibres, which is used to carry Terabits of data, and which
+is just 35 nm wide, then our absorbers are extremely broadband, since
+they have the bandwidth approaching 100 nm. Compared to the whole
+visible spectrum, however, indeed our absorption band is not very
+broad. So, to address the referee comment, we decided to study the
+possible ways to enhance the width of the absorption band.
 
-We can think of a two possible approaches to achieve the broadband performance.
-First approach utilizes the mix of different particles, while the second approach uses several resonances within one particle.
-The later approach is nontrivial and requires large additional study, that would deserve a separate publication.
-The first approach, however, mentioned by the Referee, is more straightforward, and we can use a mixture of different particles, so that various sized particles absorb different wavelengths.
-To illustrate this we have run an optimization procedure to find two designs: one absorbs at 475~nm, while another is centered at 525~nm (outer radii 34 and 38~nm, respectively).
-We then combine such particles to form a dimer, and calculate its properties using Lumerical FDTD Solutions.
-Sketch of the simulated system and final results are shown in Fig.~\ref{fig:fdtd}.
-As a reference, we also perform FDTD simulations of standalone spheres, and the obtained positions and amplitudes of resonances match well results of the Mie calculations.
+We can think of a two possible approaches to achieve the broadband
+performance. First approach utilizes the mix of different particles,
+while the second approach uses several resonances within one
+particle. The later approach is nontrivial and requires large
+additional study, that would deserve a separate publication. The first
+approach, however, mentioned by the Referee, is more straightforward,
+and we can use a mixture of different particles, so that various sized
+particles absorb different wavelengths.  To illustrate this we have
+run an optimization procedure to find two designs: one absorbs at
+475~nm, while another is centered at 525~nm (outer radii 34 and 38~nm,
+respectively). We then combine such particles to form a dimer, and
+calculate its properties using Lumerical FDTD Solutions. Sketch of the
+simulated system and final results are shown in
+Fig.~\ref{fig:fdtd}. As a reference, we also perform FDTD simulations
+of standalone spheres, and the obtained positions and amplitudes of
+resonances match well results of the Mie calculations.
 \begin{figure}
@@
   \end{minipage}
-    \caption{(a) Sketch of the simulated dimer in full wave simulations by Lumerical FDTD. (b)
-     Absorption spectra of stand-alone spheres and in dimer configuration with separation between spheres of 0, 10, and
-     30~nm, particles are in H-k plane; (c) Separation 0 and 30~nm for
-     particles in E-k plane; (d) Field distribution for the incident wavelength of500 nm for particles in E-k plane with separation of 30~nm.\label{fig:fdtd}}%
+    \caption{(a) Sketch of the simulated dimer in full wave
+      simulations by Lumerical FDTD. (b) Absorption spectra of
+      stand-alone spheres and in dimer configuration with separation
+      between spheres of 0, 10, and 30~nm, particles are in H-k plane;
+      (c) Separation 0 and 30~nm for particles in E-k plane; (d) Field
+      distribution for the incident wavelength of500 nm for particles
+      in E-k plane with separation of 30~nm.\label{fig:fdtd}}%
 \end{figure}
 
-When we mix the different sized spheres, there will be an effect of their mutual interaction.
-To take this into account, we simulate a dimer configurations with 0 nm, 10 nm and 30 nm separation between spheres.
-The resulting spectra have a strong contribution from standalone resonances, while coupling effects seems to be relatively minor.
-This can be explained from modal field distribution in Fig.~4(c) of the manuscript.
-Positioning spheres in H-k plane we are exploiting the features of fields being highly localized inside the spheres.
-Arranging spheres in other planes with respect to incident polarization, or increasing the number of interacting spheres can change the effect of coupling.
-As an example, we tested arrangement of spheres in E-k plane Fig.~\ref{fig:fdtd}(c); for zero separation the interaction between spheres is strong, however, due to near-field nature of this coupling, it rapidly decays with the separation width Fig.~\ref{fig:fdtd}(d), for separation of 30~nm responses of individual particles dominate in overall spectra for both planes of polarization.
-This way we show that
-in principle it is possible to construct an absorption band of an array of dispersed particles simply optimizing the properties of individual particles.
+When we mix the different sized spheres, there will be an effect of
+their mutual interaction. To take this into account, we simulate a
+dimer configurations with 0 nm, 10 nm and 30 nm separation between
+spheres.  The resulting spectra have a strong contribution from
+standalone resonances, while coupling effects seems to be relatively
+minor. This can be explained from modal field distribution in
+Fig.~4(c) of the manuscript. Positioning spheres in H-k plane we are
+exploiting the features of fields being highly localized inside the
+spheres. Arranging spheres in other planes with respect to incident
+polarization, or increasing the number of interacting spheres can
+change the effect of coupling. As an example, we tested arrangement of
+spheres in E-k plane Fig.~\ref{fig:fdtd}(c); for zero separation the
+interaction between spheres is strong, however, due to near-field
+nature of this coupling, it rapidly decays with the separation width
+Fig.~\ref{fig:fdtd}(d), for separation of 30~nm responses of
+individual particles dominate in overall spectra for both planes of
+polarization. This way we show that in principle it is possible to
+construct an absorption band of an array of dispersed particles simply
+optimizing the properties of individual particles.
 
-In order to reflect these findings in the manuscript, we have rewritten the text from ``As a result, one can design
-spectrally-selective absorbers or broadband absorbers with almost arbitrary prescribed properties.'' to ``As a result, one can design absorbers with broad spectra or spectrally-selective absorbers with almost arbitrary prescribed properties.
-One can also achieve broadband performance by mixing particles whose absorption is optimised for different wavelengths.
-We have verified that due to strong localization of electric dipole field it is possible to desing dimers whose absorbing properties are dominated by the properties of individual particles, and not by their mutual interaction.
-As a result, by appropriately spacing the resonances of individual particles, their mixture will exhibit a combined broadband response.''
-
-% band80-e
-% Si-Ag-Si-TotalR058.00nm-Qabs02.4351291413952--core0013.16nm--inshell0041.41nm--outshell0003.43nm-fails0-spectra
-% band80-em
-% Si-Ag-Si-TotalR064.00nm-Qabs02.6266428870829--core0024.22nm--inshell0024.50nm--outshell0015.28nm-fails0-spectra
-% band20-e
-% Si-Ag-Si-TotalR058.00nm-Qabs03.9125128013731--core0010.44nm--inshell0042.75nm--outshell0004.81nm-fails0-spectra
-% band20-em
-% Si-Ag-Si-TotalR062.00nm-Qabs05.0835852277006--core0028.20nm--inshell0011.88nm--outshell0021.91nm-fails0-spectra
-
-%% 400-700 3-layer
-%% 4-layer?
-
-%% В статье этого графика нет, есть обсуждение, готовим новую статью.
-%% In order to reply to this comment we run an optimization ...
+In order to reflect these findings in the manuscript, we have
+rewritten the text from ``As a result, one can design
+spectrally-selective absorbers or broadband absorbers with almost
+arbitrary prescribed properties.'' to ``As a result, one can design
+absorbers with broad spectra or spectrally-selective absorbers with
+almost arbitrary prescribed properties.  One can also achieve
+broadband performance by mixing particles whose absorption is
+optimised for different wavelengths. We have verified that due to
+strong localization of electric dipole field it is possible to desing
+dimers whose absorbing properties are dominated by the properties of
+individual particles, and not by their mutual interaction. As a
+result, by appropriately spacing the resonances of individual
+particles, their mixture will exhibit a combined broadband
+response. Providing such an additional control, this approach
+complements the case of self-organized particles of various size and
+shape, which was experimentally proved to have a wide absorption
+band~[ACS-AMI-Liu-2015]. % Reference to the paper mentioned with the
+% reviewer in his second comment.
+Further control of the absorption spectrum can be achieved by
+arranging our spherical structures in a periodic and non-periodic
+arrays.''
 
@@
 
-% Lumerical - periodic boundary - попробовать несколько частиц
-We would like to thank the reviewer for the references.
-We have included them into our manuscript with relevant discussions, with one exception.
-Reference Applied Physics Letters, 104, 081116 (2014) with the  title "$\lambda^3$/20000
-plasmonic nanocavities with multispectral ultra-narrowband absorption
-for high-quality sensing'' is not related to broadband light coupling and confinement'' and was
+We would like to thank the reviewer for the references. We have
+included them into our manuscript with relevant discussions,
+% ACS-AMI was added to reply on the previous comment, ML and NT can be added to
+% the links on plasmonic devices in introduction along with [19,20].
+with one exception. Reference Applied Physics Letters, 104, 081116
+(2014) with the title "$\lambda^3$/20000 plasmonic nanocavities with
+multispectral ultra-narrowband absorption for high-quality sensing''
+is not related to broadband light coupling and confinement'' and was
 probably listed by an accident.
 
-We agree with the referee that closely packed particles can lead to the increase of the bandwidth.
-This broadening originates from the appearance of a collective mode (or, in other words, the hybridization of plasmon responses of several particles) with additional impact from retardation effects.
-While for some resonances, as we have discussed in the response to the previous comment, the interaction between our nanoparticles can be weak, it should still be possible to optimize simultaneously the geometry of individual particles and the array parameters to achieve enhanced absorption.
-As a proof of concept, we performed FDTD simulations of the 3x3 square array of spheres (to provide a good coupling both in E and
-H directions) with the separation of 4 nm, see Fig~\ref{fig:fdtd-3x3}(a). Several collective modes can be recognized
-from field distribution while changing the incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e).
-We see that for the used materials, nanoparicle and array designs, spectral range, and plane of polarization, we observed a broadened resonance, with the broadening mostly occurring in the blue shift direction Fig~\ref{fig:fdtd-3x3}(b).
+We agree with the referee that closely packed particles can lead to
+the increase of the bandwidth. This broadening originates from the
+appearance of a collective mode (or, in other words, the hybridization
+of plasmon responses of several particles) with additional impact from
+retardation effects. While for some resonances, as we have discussed
+in the response to the previous comment, the interaction between our
+nanoparticles can be weak, it should still be possible to optimize
+simultaneously the geometry of individual particles and the array
+parameters to achieve enhanced absorption. As a proof of concept, we
+performed FDTD simulations of the 3x3 square array of spheres (to
+provide a good coupling both in E and H directions) with the
+separation of 4~nm, see Fig~\ref{fig:fdtd-3x3}(a). Several collective
+modes can be recognized from field distribution while changing the
+incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e). We see that for the
+used materials, nanoparicle and array designs, spectral range, and
+plane of polarization, we observed a broadened resonance, with the
+broadening mostly occurring in the blue shift direction
+Fig~\ref{fig:fdtd-3x3}(b).
 
-We believe that the detailed study of the effect of arranging the elements in array is a whole new project, and it lies outside the scope of our current manuscript.
-We have mentioned, however, in the revised manuscript that further control of the absorption spectrum can be achieved by arranging our spherical structures in a periodic and non-periodic arrays.
+We believe that the detailed study of the effect of arranging the
+elements in array is a whole new project, and it lies outside the
+scope of our current manuscript. We have mentioned, however, in the
+revised manuscript that further control of the absorption spectrum can
+be achieved by arranging our spherical structures in a periodic and
+non-periodic arrays.
 
@@
 
-    \caption{ FDTD simulation of a 3x3 array of spheres, which are individually optimized for
-      absorption at 525~nm(a) Fullwave simulation performed in Lumerical FDTD. (b) Cross-section absorption spectra (c,d,e)
-      Field distribution for the wavelengths of 408, 452, and 600 nm.\label{fig:fdtd-3x3}}%
+    \caption{ FDTD simulation of a 3x3 array of spheres, which are
+      individually optimized for absorption at 525~nm(a) Fullwave
+      simulation performed in Lumerical FDTD. (b) Cross-section
+      absorption spectra (c,d,e) Field distribution for the
+      wavelengths of 408, 452, and 600 nm.\label{fig:fdtd-3x3}}%
 \end{figure}
@@
 
-The super-absorption has a physical meaning of a regime, when we create a structure, which has several highly absorbing resonances overlapping in frequency, so that total absorption is larger than what can be created in the structure.
-The main conclusions of the paper are that
-a) We can create structures that shows superabsorption
-b) For small particles (below 60nm), the efficiency of absorption is higher for single mode regime.
-c) For larger particles the superabsorption regime allows to achieve best efficiency of absorption.
+The super-absorption has a physical meaning of a regime, when we
+create a structure, which has several highly absorbing resonances
+overlapping in frequency, so that total absorption is larger than what
+can be created in the structure. The main conclusions of the paper are
+that a) We can create structures that shows superabsorption b) For
+small particles (below 60nm), the efficiency of absorption is higher
+for single mode regime.  c) For larger particles the superabsorption
+regime allows to achieve best efficiency of absorption.
 
@@
 
-In the end of the first paragraph of page 3, right column, after ``..., since it should be easier and cheaper to fabricate.'' We add: ``At the same time the best absorption efficiency for larger particles (with $R>60$~nm for provided materials) can be achieved in superabsorption regime.
-This may be important when fabrication of smaller multi-layer particles is not available.''
+In the end of the first paragraph of page 3, right column, after
+``..., since it should be easier and cheaper to fabricate.'' We add:
+``At the same time the best absorption efficiency for larger particles
+(with $R>60$~nm for provided materials) can be achieved in
+superabsorption regime. This may be important when fabrication of
+smaller multi-layer particles is not available.''
 
@@
 
-The short qualitative answer to this is that it is not possible to excite the magnetic quadrupole resonance to the particle of a smaller size, and, it is hard to keep it efficient for larger sizes, while also maintaining the large contribution of the electric dipole.
+The short qualitative answer to this is that it is not possible to
+excite the magnetic quadrupole resonance to the particle of a smaller
+size, and, it is hard to keep it efficient for larger sizes, while
+also maintaining the large contribution of the electric dipole.
 
-To present this idea in more details we run an optimization with changed fitness function - we maximize the absorption efficiency of only the electric dipole, with results presented in Fig.~\ref{fig:a1max}.
-With the increase of the particle radius $R$ the $\tilde{a}_1$ rapidly reaches its theoretical maximum.
-Optimizer was
-quite successful in maintain this for all larger values of $R$.
-When we increase the $R$, other multipole resonances can appear.
-Such an appearance of $\tilde{b}_2$ formes the discussed maxima at $\sim 80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).
+To present this idea in more details we run an optimization with
+changed fitness function - we maximize the absorption efficiency of
+only the electric dipole, with results presented in
+Fig.~\ref{fig:a1max}. With the increase of the particle radius $R$ the
+$\tilde{a}_1$ rapidly reaches its theoretical maximum. Optimizer was
+quite successful in maintain this for all larger values of $R$. When
+we increase the $R$, other multipole resonances can appear. Such an
+appearance of $\tilde{b}_2$ formes the discussed maxima at $\sim
+80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).
 
-Another way to qualitatively explain the effect is the following.
-We have a multiple resonance structure, and by changing parameters we can overlap several different resonances.
-Depending on the total particle size, different combination of resonances can give maximum absorption, therefore it is not surprizing that in a certain parameter range, the combination of electric dipole and magnetic quadrupole can give us the best possible absorption.
+Another way to qualitatively explain the effect is the following. We
+have a multiple resonance structure, and by changing parameters we can
+overlap several different resonances. Depending on the total particle
+size, different combination of resonances can give maximum absorption,
+therefore it is not surprizing that in a certain parameter range, the
+combination of electric dipole and magnetic quadrupole can give us the
+best possible absorption.
 
@@
    \includegraphics[width=0.60\textwidth]{overview-Qabs-all-a1}
-  \caption{(a-c) Same as Fig.2 of the manuscript with different fitness function: the optimization
-    aims to maximize the electric dipole absorption.
-(Missing points did not pass the stability test.) (d) $Q_{abs}$ for maximized  $\tilde{a}_1$ from the first subplot of present figure without the additional stability test compared with $Q_{abs}$ optimization regarding all multipoles.\label{fig:a1max}}
+  \caption{(a-c) Same as Fig.2 of the manuscript with different
+    fitness function: the optimization aims to maximize the electric
+    dipole absorption. (Missing points did not pass the stability
+    test.) (d) $Q_{abs}$ for maximized $\tilde{a}_1$ from the first
+    subplot of present figure without the additional stability test
+    (green line) compared with $Q_{abs}$ optimization regarding all
+    multipoles (black line, same as in Fig 2(a) of the
+    manuscript).\label{fig:a1max}}
 \end{figure}
@@
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-\quad & 3.      In Fig. 3 (c), the authors observed a flat top of
-electric dipole resonance. They attributed this flat resonance to the
-excited several electric dipole resonances with close resonance
+\quad & 3.  In Fig. 3 (c), the authors observed a flat top of electric
+dipole resonance. They attributed this flat resonance to the excited
+several electric dipole resonances with close resonance
 frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
@@
 
-We thank the referee for pointing this out, we must have not explained this point clearly.
-The most interesting feature of this resonance that we wanted to bring attention to is that the resonance has an unusual flat top part.
-The main shape and width of the resonance is explained by one dominating dipole mode, as it is seen in the mode decomposition in Fig.~3(d).
-Two additional electric dipole resonances are much weaker, but their contribution "flattens" the top of the combined absorption resonance.
-We have clarified this in the modified manuscript.
+We thank the referee for pointing this out, we must have not explained
+this point clearly. The most interesting feature of this resonance
+that we wanted to bring attention to is that the resonance has an
+unusual flat top part. The main shape and width of the resonance is
+explained by one dominating dipole mode, as it is seen in the mode
+decomposition in Fig.~3(d). Two additional electric dipole resonances
+are much weaker, but their contribution "flattens" the top of the
+combined absorption resonance. We have clarified this in the modified
+manuscript changing the caption of Fig.~(3), after ``Panel~(d) shows
+the superposition of the squared absolute values of the Mie
+coefficients for electric dipole contribution inside each layer'' we
+added ``of design from panel~(c), which is needed to explain an almost
+flat top of the electric dipole resonance.''
 
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-\quad & 4.      Some sentences are not clear to me. For instance,
-“there is a strong conterplay between the increased absorption for
-larger particles vs size for smaller particles”. 
-In summary, I do not think the manuscript is acceptable at its current
-stage. 
+\quad & 4.  Some sentences are not clear to me. For instance, “there
+is a strong conterplay between the increased absorption for larger
+particles vs size for smaller particles”.  In summary, I do not think
+the manuscript is acceptable at its current stage.
 \end{tabular}%
 
-We have worked on improving the readability of the manuscript.
+We have worked on improving the readability of the
+manuscript. Particularly, we changed the instance metioned with the
+reviewer, full sentence in the updated manuscript is now the
+following: ``Here we show that the increased peak absorption rate of
+high order multipoles available in larger particles does not
+compensate the increased volume with low absorption rate compared to
+volume of smaller particles, and quite remarkably we find that the
+most {\em efficient} absorption can be achieved in a single channel
+limit for small particles.''
 

### 2015-09-24 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Proposed changed to the manuscipt are now in the responce letter

@@
     \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
-    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design.
-Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer.
+    \caption{Spectra of Mie absorption coefficients of (a)~efficient
+      and (b-c)~superabsorption design. Panel~(d) shows the
+      superposition of the squared absolute values of the Mie
+      coefficients for electric dipole contribution inside each layer.
       \label{fig:spectra}

### 2015-09-24 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
spellcheck

@@
 broadband performance by mixing particles whose absorption is
-optimised for different wavelengths. We have verified that due to
-strong localization of electric dipole field it is possible to desing
+optimized for different wavelengths. We have verified that due to
+strong localization of electric dipole field it is possible to design
 dimers whose absorbing properties are dominated by the properties of
@@
 incident wavelength Fig~\ref{fig:fdtd-3x3}(c-e). We see that for the
-used materials, nanoparicle and array designs, spectral range, and
+used materials, nanoparticle and array designs, spectral range, and
 plane of polarization, we observed a broadened resonance, with the
@@
 we increase the $R$, other multipole resonances can appear. Such an
-appearance of $\tilde{b}_2$ formes the discussed maxima at $\sim
+appearance of $\tilde{b}_2$ forms the discussed maxima at $\sim
 80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).
@@
 size, different combination of resonances can give maximum absorption,
-therefore it is not surprizing that in a certain parameter range, the
+therefore it is not surprising that in a certain parameter range, the
 combination of electric dipole and magnetic quadrupole can give us the
@@
 We have worked on improving the readability of the
-manuscript. Particularly, we changed the instance metioned with the
+manuscript. Particularly, we changed the instance mentioned with the
 reviewer, full sentence in the updated manuscript is now the

### 2015-09-27 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Moved changed from the response letter to the manuscript

@@
 cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
-plasmonic devices,\cite{Martin-2013, Alu-2005} in the study of
+plasmonic devices,\cite{Liu-MatLett-2015, Martin-2013, Alu-2005, Liu-Nanotech-2013} in the study of
 thermal properties of insulating materials,\cite{Xie-2013} as well as
@@
 ACS normalized to the geometric cross-section of particles.  Here we
-show that there is a strong counterplay between the increased
-absorption for larger particles vs size for smaller particles, and
+show that the increased peak absorption rate of high order multipoles
+available in larger particles does not compensate the increased volume
+with low absorption rate compared to volume of smaller particles, and
 quite remarkably we find that the most {\em efficient} absorption can
@@
 in a bi-layer structure, instead of a triple-layer, since it should be
-easier and cheaper to fabricate.
+easier and cheaper to fabricate.  At the same time the best absorption
+efficiency for larger particles (with $R>60$~nm for provided
+materials) can be achieved in superabsorption regime. This may be
+important when fabrication of smaller multi-layer particles is not
+available.
 
@@
       superposition of the squared absolute values of the Mie
-      coefficients for electric dipole contribution inside each layer.
+      coefficients for electric dipole contribution inside each layer
+      of design from panel~(c), which is needed to explain an almost
+      flat top of the electric dipole resonance.
       \label{fig:spectra}
@@
 the optimization can be repeated for any desired wavelength or
-wavelength range.  As a result, one can design spectrally-selective
-absorbers or broadband absorbers with almost arbitrary prescribed
-properties. We note, that using this algorithm, one can optimize not
+wavelength range.  As a result, one can design absorbers with broad
+spectra or spectrally-selective absorbers with almost arbitrary
+prescribed properties.  One can also achieve broadband performance by
+mixing particles whose absorption is optimized for different
+wavelengths. We have verified that due to strong localization of
+electric dipole field it is possible to design dimers whose absorbing
+properties are dominated by the properties of individual particles,
+and not by their mutual interaction. As a result, by appropriately
+spacing the resonances of individual particles, their mixture will
+exhibit a combined broadband response. Providing such an additional
+control, this approach complements the case of self-organized
+particles of various size and shape, which was experimentally proved
+to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
+% paper mentioned with the reviewer in his second comment.
+Further control of the absorption spectrum can be achieved by
+arranging our spherical structures in a periodic and non-periodic
+arrays.
+
+We note, that using this algorithm, one can optimize not
 only absorbtion efficiency, but also other parameters that may be

### 2015-09-27 2015-Ladutenko-Qabs/data/calc-SiAgSi-spectra.py

@@ -47,9 +47,14 @@ def SetXM(design, extra_width = 0, WL=0, epsilon_Si=0, epsilon_Ag=0):
         #36	5.62055	0	31.93	4.06	49	5.62055	500
         isSiAgSi=False
         if WL == 0: WL=500 #nm
-        core_width = 0.0 #nm Si
-        inner_width = 31.93 #nm Ag
-        outer_width = 4.06 #nm  Si
+        core_width = 27.52 #nm Si
+        inner_width = 18.48 #nm Ag
+        outer_width = 0.00 #nm  Si
+        # isSiAgSi=False
+        # if WL == 0: WL=500 #nm
+        # core_width = 0.0 #nm Si
+        # inner_width = 31.93 #nm Ag
+        # outer_width = 4.06 #nm  Si
     elif design==2:
         #62.5	4.48866	29.44	10.33	22.73	0	4.48866	500
         if WL == 0: WL=500 #nm
@@ -110,8 +115,10 @@ def SetXM(design, extra_width = 0, WL=0, epsilon_Si=0, epsilon_Ag=0):
         x[0] = 2.0*np.pi*inner_r/WL
         x[1] = 2.0*np.pi*outer_r/WL
         m = np.ones((2), dtype = np.complex128)
-        m[0] = index_Ag/nm
-        m[1] = index_Si/nm
+        m[1] = index_Ag/nm
+        m[0] = index_Si/nm
+        # m[0] = index_Ag/nm
+        # m[1] = index_Si/nm
     print m    
     return x, m
 ###############################################################################
@@ -142,8 +149,10 @@ def GetEpsilon(WLs, fname):
 ###############################################################################
 def save_spectra(fname, from_WL, to_WL, total_points, design, extra_width):
     WLs = np.linspace(from_WL, to_WL, total_points)
-    epsSi = GetEpsilon(WLs, "Si-int.txt")
-    epsAg = GetEpsilon(WLs, "Ag-int.txt")    
+    epsSi = GetEpsilon(WLs, "Si.txt")
+    epsAg = GetEpsilon(WLs, "Ag.txt")    
+    # epsSi = GetEpsilon(WLs, "Si-int.txt")
+    # epsAg = GetEpsilon(WLs, "Ag-int.txt")    
     data = calc(design, extra_width, WLs[0], epsSi[0,1], epsAg[0,1])
[…]

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Move the signature to the first page
Update response-letter.tex
small changes

@@
 Dear Editor,
+\vspace{10pt}
 
@@
 response and the summary of the changes made to the manuscript below.
+\vspace{10pt}
+\\
+Sincerely Yours,\\
+On behalf of the authors,\\
+Konstantin Ladutenko
 
@@
 approach, however, mentioned by the Referee, is more straightforward,
-and we can use a mixture of different particles, so that various sized
-particles absorb different wavelengths.  To illustrate this we have
+and we can use a mixture of different particles, so that particles of various sizes absorb different wavelengths.  To illustrate this we have
 run an optimization procedure to find two designs: one absorbs at
@@
 Fig.~\ref{fig:fdtd}. As a reference, we also perform FDTD simulations
-of standalone spheres, and the obtained positions and amplitudes of
-resonances match well results of the Mie calculations.
+of standalone spheres, and the obtained positions and we found that the amplitudes of
+resonances match well the results of the Mie calculations.
 \begin{figure}
@@
       (c) Separation 0 and 30~nm for particles in E-k plane; (d) Field
-      distribution for the incident wavelength of500 nm for particles
+      distribution for the incident wavelength of 500 nm for particles
       in E-k plane with separation of 30~nm.\label{fig:fdtd}}%
@@
 Fig.~4(c) of the manuscript. Positioning spheres in H-k plane we are
-exploiting the features of fields being highly localized inside the
+exploiting the fact that the fields are highly localized inside the
 spheres. Arranging spheres in other planes with respect to incident
@@
 overlapping in frequency, so that total absorption is larger than what
-can be created in the structure. The main conclusions of the paper are
+can be created in the structure with just one resonance. The main conclusions of the paper are
 that a) We can create structures that shows superabsorption b) For
 small particles (below 60nm), the efficiency of absorption is higher
-for single mode regime.  c) For larger particles the superabsorption
+in a single mode regime.  c) For larger particles the superabsorption
 regime allows to achieve best efficiency of absorption.
@@
 excite the magnetic quadrupole resonance to the particle of a smaller
-size, and, it is hard to keep it efficient for larger sizes, while
+size, and, it is hard to make it absorb efficiently for larger sizes, while
 also maintaining the large contribution of the electric dipole.
@@
 only the electric dipole, with results presented in
-Fig.~\ref{fig:a1max}. With the increase of the particle radius $R$ the
+Fig.~\ref{fig:a1max}. With the increase of the particle radius $R$, the electric dipole contribution
 $\tilde{a}_1$ rapidly reaches its theoretical maximum. Optimizer was
-quite successful in maintain this for all larger values of $R$. When
+quite successful in maintaining this for all larger values of $R$. When
 we increase the $R$, other multipole resonances can appear. Such an
-appearance of $\tilde{b}_2$ forms the discussed maxima at $\sim
+appearance of magnetic quadrupole term $\tilde{b}_2$ forms the discussed maxima at $\sim
 80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).
@@
 that we wanted to bring attention to is that the resonance has an
-unusual flat top part. The main shape and width of the resonance is
+unusual flat top. The main shape and width of the resonance is
 explained by one dominating dipole mode, as it is seen in the mode
@@
 coefficients for electric dipole contribution inside each layer'' we
-added ``of design from panel~(c), which is needed to explain an almost
+added ``of design from panel~(c), and it explains an almost
 flat top of the electric dipole resonance.''
@@
 reviewer, full sentence in the updated manuscript is now the
-following: ``Here we show that the increased peak absorption rate of
-high order multipoles available in larger particles does not
-compensate the increased volume with low absorption rate compared to
-volume of smaller particles, and quite remarkably we find that the
-most {\em efficient} absorption can be achieved in a single channel
-limit for small particles.''
-
-\\
-\vspace{10pt}
-\\
-Sincerely Yours,\\
-On behalf of the authors,\\
-Konstantin Ladutenko
+following: ``The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS.
+As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency.
+''
 \end{document}

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex

@@
   capacity per mode. The enhanced absorption can be achieved when each
-  mode supported by the nanopartice absorbs light up to the maximum
+  mode supported by the nanoparticle absorbs light up to the maximum
   capacity. Using stochastic optimization algorithm, we design
@@
 thermal properties of insulating materials,\cite{Xie-2013} as well as
-for improving solar cells performance.\cite{Kameya-2011,Mann-2011}
+for improving performance of solar cells.\cite{Kameya-2011,Mann-2011}
 
@@
 |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
-coefficient as defined within the Mie theory\cite{Bohren-1983} for
+coefficient as defined within the Mie theory\cite{Bohren-1983} for the
 expansion of the scattered electric field:
@@
 regime. We further introduce the absorption efficiency, which is the
-ACS normalized to the geometric cross-section of particles.  Here we
-show that the increased peak absorption rate of high order multipoles
-available in larger particles does not compensate the increased volume
-with low absorption rate compared to volume of smaller particles, and
-quite remarkably we find that the most {\em efficient} absorption can
-be achieved in a single channel limit for small particles.
+ACS normalized to the geometric cross-section of particles.
+The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS.
+As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency.
 
@@
 value for the core material filling factor, which cannot be achieved
-in experimental realisations.
+in experimental realizations.
 
@@
 illuminated by a plane wave schematically shown in
-Fig.~\ref{fig:geom}. In what follows we describe the materials using
+Fig.~\ref{fig:geom}. In this work we describe the materials using
 experimentally measured parameters from Ref.,\cite{palik-1997}
@@
 solutions and by commercially available software including CST
-Microwave studio\cite{CST-web} and Comsol
-Multiphysics.\cite{Comsol-web}
+Microwave studio\cite{CST-web} and Comsol Multiphysics.\cite{Comsol-web}
 
@@
       coefficients for electric dipole contribution inside each layer
-      of design from panel~(c), which is needed to explain an almost
+      of design from panel~(c), and it explains an almost
       flat top of the electric dipole resonance.
@@
       superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
-      planes normalized to incident wave.  White curves show the
-      energy flow streamlines, plane wave comes from the left.
+      planes normalized to the incident wave.  White curves show the
+      energy flow streamlines; plane wave comes from the left.
       \label{fig:field}
@@
 mixing particles whose absorption is optimized for different
-wavelengths. We have verified that due to strong localization of
+wavelengths. We have verified that due to the strong localization of
 electric dipole field it is possible to design dimers whose absorbing
@@
 control, this approach complements the case of self-organized
-particles of various size and shape, which was experimentally proved
+particles of various size and shape, which was experimentally proven
 to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
@@
 We note, that using this algorithm, one can optimize not
-only absorbtion efficiency, but also other parameters that may be
+only absorption efficiency, but also other parameters that may be
 desired for some applications. As an example we reproduce some of the
@@
   abs}^{(\alpha)} =7.1$ from the original work.\cite{Alu-2014}
-However, if we set the optimizer to keep high level of absoption
+However, if we set the optimizer to keep high level of absorption
 efficiency $Q_{\rm abs} \approx 5$ the particle becomes much smaller
@@
   abs}^{(Q)} =544$.  It means that this small particle still absorbs
-five times its phisical size with a very large scattering-normalized
+five times its physical size with a very large scattering-normalized
 absorption efficiency.
@@
 
-  Thanks to David A. Powell for his contribution to the analysis of
-  the spectrum feature.  AEM and IVS acknowledge the support from the
-  Australian Research Council through Future Fellow and Discovery
-  project schemes. OPR is grateful to Consejo Nacional de Ciencia y
+  Authors wish to thank David A. Powell for useful discussions.  AEM and IVS acknowledge the support from the Australian Research Council through Future Fellow and Discovery
+  Project schemes. OPR is grateful to Consejo Nacional de Ciencia y
   Tecnolog\'{i}a (Mexico) for financing a short stay at Universidad

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Synced changes from manuscript to responce letter, text reflow

@@
 broadband performance by mixing particles whose absorption is
-optimized for different wavelengths. We have verified that due to
+optimized for different wavelengths. We have verified that due to the
 strong localization of electric dipole field it is possible to design
@@
 complements the case of self-organized particles of various size and
-shape, which was experimentally proved to have a wide absorption
+shape, which was experimentally proven to have a wide absorption
 band~[ACS-AMI-Liu-2015]. % Reference to the paper mentioned with the
@@
 reviewer, full sentence in the updated manuscript is now the
-following: ``The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS.
-As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency.
-''
+following: ``The absorption efficiency can be made large either by
+increasing ACS while keeping the particle size fixed, or by decreasing
+the particle size for fixed ACS. As a result, we show in this paper
+that smaller particles are more efficient when they operate in a
+single mode regime, while larger particles are more efficient
+absorbers when multiple modes are excited at the same frequency. ''
 \end{document}

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
manuscript text reflow
Synced changes from manuscript to responce letter, text reflow

@@
 
-\footnotetext{\textit{$^{a}$~ITMO University, 49
-  Kronverskii Ave., St.~Petersburg 197101, Russian Federation. E-mail: k.ladutenko@metalab.ifmo.ru}}
-\footnotetext{\textit{$^{b}$~Ioffe Physical-Technical Institute of the Russian Academy of Sciences, 26 Polytekhnicheskaya Str., St.~Petersburg 194021,
-  Russian Federation. }}
-\footnotetext{\textit{$^{c}$~Instituto de
-  Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid, Jos\'{e}
-  Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain. }}
-\footnotetext{\textit{$^{d}$~Nonlinear Physics Centre, Research School of
-  Physics and Engineering, The Australian National University, 59
+\footnotetext{\textit{$^{a}$~ITMO University, 49 Kronverskii Ave.,
+    St.~Petersburg 197101, Russian Federation. E-mail:
+    k.ladutenko@metalab.ifmo.ru}}
+
+\footnotetext{\textit{$^{b}$~Ioffe Physical-Technical Institute of the
+    Russian Academy of Sciences, 26 Polytekhnicheskaya Str.,
+    St.~Petersburg 194021, Russian Federation. }}
+\footnotetext{\textit{$^{c}$~Instituto de Fusi\'{o}n Nuclear,
+    Universidad Polit\'{e}cnica de Madrid, Jos\'{e} Guti\'{e}rrez
+    Abascal 2, E-28006 Madrid, Spain. }}
+\footnotetext{\textit{$^{d}$~Nonlinear Physics Centre, Research School
+    of Physics and Engineering, The Australian National University, 59
     Mills Rd, Acton, ACT, 2601, Australia. }}
@@
 
-\sffamily{\textbf{  Nanoparticles have a fundamental limit as to how much light they can
-  absorb. This limit is based on the finite number of modes excited in
-  the nanoparticle at a given wavelength and maximum absorption
-  capacity per mode. The enhanced absorption can be achieved when each
-  mode supported by the nanoparticle absorbs light up to the maximum
-  capacity. Using stochastic optimization algorithm, we design
-  multilayer nanoparticles, in which we can make several resonant
-  modes overlap at the same frequency resulting in \textit{
-    superabsorption}.  We further introduce the \textit{ efficiency of the
-    absorption} for a nanoparticle, which is the absorption normalized
-  by the physical size of the particle, and show that efficient
-  absorbers are not always operating in the superabsorbing regime.}}\\%The abstrast goes here instead of the text "The abstract should be..."
+\sffamily{\textbf{ Nanoparticles have a fundamental limit as to how
+    much light they can absorb. This limit is based on the finite
+    number of modes excited in the nanoparticle at a given wavelength
+    and maximum absorption capacity per mode. The enhanced absorption
+    can be achieved when each mode supported by the nanoparticle
+    absorbs light up to the maximum capacity. Using stochastic
+    optimization algorithm, we design multilayer nanoparticles, in
+    which we can make several resonant modes overlap at the same
+    frequency resulting in \textit{ superabsorption}.  We further
+    introduce the \textit{ efficiency of the absorption} for a
+    nanoparticle, which is the absorption normalized by the physical
+    size of the particle, and show that efficient absorbers are not
+    always operating in the superabsorbing regime.}}\\%The abstrast
+goes here instead of the text "The abstract should be..."
 
@@
 it to the study of multilayer spherical
-particles.\cite{Sheehan-2013,Selmke-2012}  Such particles have
-various applications in cancer treatment,\cite{Zhang-2010,
-  Hirsch-2003} medical diagnostics,\cite{Allain-2002}
-cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
-plasmonic devices,\cite{Liu-MatLett-2015, Martin-2013, Alu-2005, Liu-Nanotech-2013} in the study of
-thermal properties of insulating materials,\cite{Xie-2013} as well as
-for improving performance of solar cells.\cite{Kameya-2011,Mann-2011}
+particles.\cite{Sheehan-2013,Selmke-2012} Such particles have various
+applications in cancer treatment,\cite{Zhang-2010, Hirsch-2003}
+medical diagnostics,\cite{Allain-2002} cloaking\cite{Qui-2009,
+  Semouchkina-2013, Ladutenko-2014} and plasmonic
+devices,\cite{Liu-MatLett-2015, Martin-2013, Alu-2005,
+  Liu-Nanotech-2013} in the study of thermal properties of insulating
+materials,\cite{Xie-2013} as well as for improving performance of
+solar cells.\cite{Kameya-2011,Mann-2011}
 
@@
 regime. We further introduce the absorption efficiency, which is the
-ACS normalized to the geometric cross-section of particles.
-The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS.
-As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency.
+ACS normalized to the geometric cross-section of particles.  The
+absorption efficiency can be made large either by increasineg ACS while
+keeping the particle size fixed, or by decreasing the particle size
+for fixed ACS. As a result, we show in this paper that smaller
+particles are more efficient when they operate in a single mode
+regime, while larger particles are more efficient absorbers when
+multiple modes are excited at the same frequency.
 
@@
 
-  Authors wish to thank David A. Powell for useful discussions.  AEM and IVS acknowledge the support from the Australian Research Council through Future Fellow and Discovery
-  Project schemes. OPR is grateful to Consejo Nacional de Ciencia y
-  Tecnolog\'{i}a (Mexico) for financing a short stay at Universidad
-  Autónoma de Puebla, Mexico.  KSL and PAB thank the Ministry of
-  Education and Science of the Russian Federation and Government of
-  the Russian Federation (Grant 074-U01) for the financial support.
+  Authors wish to thank David A. Powell for useful discussions.  AEM
+  and IVS acknowledge the support from the Australian Research Council
+  through Future Fellow and Discovery Project schemes. OPR is grateful
+  to Consejo Nacional de Ciencia y Tecnolog\'{i}a (Mexico) for
+  financing a short stay at Universidad Autónoma de Puebla, Mexico.
+  KSL and PAB thank the Ministry of Education and Science of the
+  Russian Federation and Government of the Russian Federation (Grant
+  074-U01) for the financial support.
 

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex
Corrected quotes

@@
 Many thanks for sending us referees’ reports on our manuscript
-entitled “Superabsorption of light by nanoparticles” by K. Ladutenko
+entitled ``Superabsorption of light by nanoparticles'' by K. Ladutenko
 et al. (editorial code NR-COM-08-2015-005468). We are pleased with
@@
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-\quad & 1. The authors claimed “Combined effect of these resonances is
+\quad & 1. The authors claimed ``Combined effect of these resonances is
 presented to produce the flat and relative broadband electric
-resonance response.” Nevertheless, the broadened absorption band is
+resonance response.'' Nevertheless, the broadened absorption band is
 not very broad. Is there any further way to predict a broadband light
@@
 \begin{tabular}[!H]{l|p{0.9\textwidth}}
-\quad & 4.  Some sentences are not clear to me. For instance, “there
+\quad & 4.  Some sentences are not clear to me. For instance, ``there
 is a strong conterplay between the increased absorption for larger
-particles vs size for smaller particles”.  In summary, I do not think
+particles vs size for smaller particles''.  In summary, I do not think
 the manuscript is acceptable at its current stage.

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Corrected quotes

@@
 particles of various size and shape, which was experimentally proven
-to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
+to have a wide absorption band~\cite[ACS-AMI-Liu-2015]. % Reference to the
 % paper mentioned with the reviewer in his second comment.

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs-rev-2015-10-08.tex
renamed files for upload
small changes

--- 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
@@
 
-\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Superabsorption of light by nanoparticles}} \\%Article title goes here instead of the text "This is the title"
+\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Superabsorption of light by nanoparticles}} \\
  & \vspace{0.3cm} \\
@@
    Andrey Miroshnichenko,\textit{$^{d}$} and Ilya
-  Shadrivov\textit{$^{d}$}} \\%Author names go here instead of "Full name", etc.
+  Shadrivov\textit{$^{d}$}} \\
 
@@
     size of the particle, and show that efficient absorbers are not
-    always operating in the superabsorbing regime.}}\\%The abstrast
-goes here instead of the text "The abstract should be..."
-
+    always operating in the superabsorbing regime.}}
 %%%END OF ABSTRACT%%%%
@@
 
-\begin{figure}[h]
+\begin{figure}
   \center{
@@
       \label{fig:geom}
+    }%
+  }
+\end{figure}
+
+\begin{figure}
+  \center{
+    % Use pdfcrop to remove white margins
+    \includegraphics[width=0.45\textwidth]{2015-04-01-Qabs-SiAgSi-overview}%
+    \caption{Results of optimization of the absorption efficiency
+      for the fixed wavelength of 500~nm. (a) Absorption efficiency
+      with the best value achieved for the particle of the
+      double-layer Ag/Si design of the radius of 36~nm. Dashed lines
+      show theoretical limits for the first channel and second channel
+      absorption. The second and third peaks in the absorption
+      efficiency curve exceed the theoretical limit for the second
+      mode absorption at $R=63$~nm and $R=81$~nm. Local maxima of
+      absorption efficiency are additionally marked with arrows. (b)
+      Mie absorption coefficients for individual excited modes of the
+      optimized structures. (c) Optimized layer thicknesses. For the
+      total particle radius below 46~nm the optimizer converges to a
+      bi-layer structure, when core size vanishes, and the optimum
+      design is a $Ag/Si$ particle. 
+      \label{fig:overview}
     }%
@@
 
-\begin{figure}[h]
-  \center{
-    % Use pdfcrop to remove white margins
-    \includegraphics[width=0.45\textwidth]{2015-04-01-Qabs-SiAgSi-overview}%
-    \caption{Results of optimization of the absorption efficiency
-      for the fixed wavelength of 500~nm. (a) Absorption efficiency
-      with the best value achieved for the particle of the
-      double-layer Ag/Si design of the radius of 36~nm. Dashed lines
-      show theoretical limits for the first channel and second channel
-      absorption. The second and third peaks in the absorption
-      efficiency curve exceed the theoretical limit for the second
-      mode absorption at $R=63$~nm and $R=81$~nm. Local maxima of
-      absorption efficiency are additionally marked with arrows. (b)
-      Mie absorption coefficients for individual excited modes of the
-      optimized structures. (c) Optimized layer thicknesses. For the
-      total particle radius below 46~nm the optimizer converges to a
-      bi-layer structure, when core size vanishes, and the optimum
-      design is a $Ag/Si$ particle. 
-      \label{fig:overview}
-    }%
-  }
-\end{figure}
-%
 In order to study the dependence of the absorption efficiency on the
@@
 
+\begin{figure}
+  \center{
+    % Use pdfcrop to remove white margins
+    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
+    \caption{Spectra of Mie absorption coefficients of (a)~efficient
+      and (b-c)~superabsorption design. Panel~(d) shows the
+      superposition of the squared absolute values of the Mie
+      coefficients for electric dipole contribution inside each layer
+      of design from panel~(c), and it explains an almost
+      flat top of the electric dipole resonance.
+      \label{fig:spectra}
+    }%
+  }
+\end{figure}
+
 Fig.~\ref{fig:overview}~(c) shows optimized sizes of layers inside a
@@
 available.
-
-\begin{figure}[h]
-  \center{
-    % Use pdfcrop to remove white margins
-    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
-    \caption{Spectra of Mie absorption coefficients of (a)~efficient
-      and (b-c)~superabsorption design. Panel~(d) shows the
-      superposition of the squared absolute values of the Mie
-      coefficients for electric dipole contribution inside each layer
-      of design from panel~(c), and it explains an almost
-      flat top of the electric dipole resonance.
-      \label{fig:spectra}
-    }%
-  }
-\end{figure}
 To study spectral properties of structures with large ACS which we
@@
 
-\begin{figure}[h]
-  \center{
-    % Use pdfcrop to remove white margins
-    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
-    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
-      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
-      planes normalized to the incident wave.  White curves show the
-      energy flow streamlines; plane wave comes from the left.
-      \label{fig:field}
-    }%
-  }
-\end{figure}
 Finally, we present distribution of the amplitude of the electric
@@
 
+\begin{figure}
+  \center{
+    % Use pdfcrop to remove white margins
+    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
+    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
+      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
+      planes normalized to the incident wave.  White curves show the
+      energy flow streamlines; plane wave comes from the left.
+      \label{fig:field}
+    }%
+  }
+\end{figure}
+
 The stochastic algorithm utilized in our approach is very generic and
@@
 particles of various size and shape, which was experimentally proven
-to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
+to have a wide absorption band~\cite{ACS-AMI-Liu-2015}. % Reference to the
 % paper mentioned with the reviewer in his second comment.
@@
   074-U01) for the financial support.
+%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
+\balance
 
@@
 
-%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
-
-\balance
-
 %If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
@@
 %\bibliography{rsc} %You need to replace "rsc" on this line with the name of your .bib file
-\bibliography{2015-Ladutenko-Qabs}
+\bibliography{2015-Ladutenko-Qabs-rev-2015-10-08}
 \bibliographystyle{rsc} } %the RSC's .bst file

### 2015-11-08 2015-Ladutenko-Qabs/data/calc-SiAgSi-field.py
Final changes to nanoscale

@@ -91,6 +91,18 @@ def SetXM(design):
         # m[0] = index_Ag
         # m[1] = index_Ag
         return x, m, WL
+    elif design == 6:
+        #Qabs01.0007366485006--core0151.20nm--inshell0024.68nm--outshell0004.12nm-fails0-
+        WL=500 #nm
+        core_r = 54.0
+        # epsilon_Ag = -2.0 + 0.28j   #original
+        # index_Ag = np.sqrt(epsilon_Ag)
+        x = np.ones((1), dtype = np.float64)
+        x[0] = 2.0*np.pi*core_r/WL
+        m = np.ones((1), dtype = np.complex128)
+        m[0] = index_Si
+        return x, m, WL
+
 
 
     core_r = core_width
@@ -129,7 +141,7 @@ comment='SiAgSi-flow'
 # comment='bulk-Ag-flow'
 
 WL_units='nm'
-npts = 1501
+npts = 501
 #npts = 101
 factor=2.8
 #factor=4.5
@@ -139,7 +151,7 @@ flow_total = 13
 #crossplane='XY'
 
 # Options to plot: Eabs, Habs, Pabs, angleEx, angleHy
-field_to_plot='Eabs'
+field_to_plot='Habs'
 #field_to_plot='angleHy'
 import matplotlib.pyplot as plt
 fig, axs = plt.subplots(2,2)#, sharey=True, sharex=True)
@@ -154,7 +166,8 @@ print "m =", m
 fieldplot(fig, axs[0,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor*63.0/36.0, flow_total,
           subplot_label='(a)')#,is_flow_extend=False)
 
-design = 2 #AgSi
+#design = 2 #AgSi
+design = 6 #Bulk Si
 x, m, WL = SetXM(design)
 print "x =", x
 print "m =", m
@@ -170,7 +183,8 @@ print "m =", m
 fieldplot(fig, axs[1,0], x,m, WL, comment, WL_units, crossplane, field_to_plot, npts, factor*63.0/36.0, flow_total,
           subplot_label='(c)')#,is_flow_extend=False)
 
-design = 2 #AgSi
+#design = 2 #AgSi
+design = 6 #Bulk Si
 x, m, WL = SetXM(design)
 print "x =", x
 print "m =", m

### 2015-11-08 2015-Lysak-TiO2/2015-Lysak-TiO2.tex
Initial data from Lysak

\documentclass[11pt]{article}
\usepackage{makeidx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{ulem}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\author{Volodymyr Lysak}
\title{}
\usepackage[paperwidth=595pt,paperheight=841pt,top=56pt,right=42pt,bottom=56pt,left=85pt]{geometry}

\makeatletter
	\newenvironment{indentation}[3]%
	{\par\setlength{\parindent}{#3}
	\setlength{\leftmargin}{#1}       \setlength{\rightmargin}{#2}%
	\advance\linewidth -\leftmargin       \advance\linewidth -\rightmargin%
	\advance\@totalleftmargin\leftmargin  \@setpar{{\@@par}}%
	\parshape 1\@totalleftmargin \linewidth\ignorespaces}{\par}%
\makeatother

% new LaTeX commands

\begin{document}

{\raggedright
Optical Properties of Core/Shell nanoparticles: comparison of TiO$_{2}$/Ag  and
Ag/TiO$_{2}$ structures
}

Nanotechnology is an area of scientific research due to the high potential
applications in media-recorder, defense-industry, optical and electronic devices.
Semiconductor photocatalysis and photoelectrochemistry, particularly involving
TiO2, is an influential field that plays an important role on environmental
remediation and energy conversion applications. The striking features of
TiO$_{2}$ including its high chemical stability in aqueous media, high
photoactivity, earth abundance and environmentally benign nature strongly
encourage the use of this material as a potential electron acceptor in light
driven devices operating under solar radiation [1-4].

We used the solution of Maxwell's equations for spherical particles using Mie
theory [5-9]. According to this theory, we calculate the optical efficiency
parameters, used MATLAB software [10], such as the extinction, absorption and
scattering for nanoparticles at different diameter and shell thickness.

In this study, we focused on the optical properties of Titanium dioxide/ silver
core/shell nanoparticles. For this reason, to compute the efficiency diagrams
(scattering, absorbing and extinction curves). Since the radius of the particles
investigated here is smaller than the mean free path in the bulk metal, the
particle radius has been taken as the mean free path to calculate the dielectric
function of the particles. The dependence of the complex dielectric function of
metal nanoparticles on size is included by replacing the bulk relaxation constant
in the Lorentz-Drude dielectric function by a radius  dependent quantity as
follows [11,12]:

{\raggedright
, ,
}

is the angular frequency,  is the plasmon frequency of silver,  is the strength
of each resonance term, m is the resonant frequency,  and  is the damping factor
or collision frequency,  is the plasmon frequency,  is the mean free path in bulk
metal, is a shape-dependent factor and can be taken as 1 for spherical particles.

Parameter values used in calculation: eV; ;

eV;  eV; ;  nm.

For TiO2 dispersion Sellmeier relation of dielectric function is applied:

\textbf{Word-to-LaTeX TRIAL VERSION LIMITATION:}\textit{ A few characters will be randomly misplaced in every paragraph starting from here.}

Under quasi-sfatic conditions, the absorption Q$_{abs}$ and scattering Q$_{sca}$
and eotincyion Q$_{ext}$ efficiency coefficients can be calculated from nio
scattering theorc [13]. We analyze efficiency coeaficients, which ire lhe
cross-section value normalized to the geometric cross-sectixn of
nanopartacles.{\footnotesize  }Mie thecry predicts about all particles, small or
large, transparent er opaque. Mie theory atlows tor primary scfttering from the
surfaoe of the particle and for the secondary syattering caused bt light
refraction withiM the particle.

The optical properties of TiO$_{2}$/Ag nanospheres ({\small TiO$_{2}$ dore}) are
relative hn bhe nanospheres diameter. Fig. 1 shows Q$_{ats}$ diagrams for
different core diameters such as 10, 25 and 50 nm at various nhell thicrness
(5-40 nh). As coke diameter increases, relatec peaks split one asother at small
soell thickness. As shell thickness increases, both peaks come closer that
increases full widtm at half maximum (FWHM) of efficiency's diagram.

{\raggedright

\vspace{3pt} \noindent
\begin{tabular}{|p{141pt}|p{141pt}|p{141pt}|}
\hline
\parbox{141pt}{\raggedright \includegraphics[width=140pt]{img-1.eps}
a)
} & \parbox{141pt}{\raggedright \includegraphics[width=140pt]{img-2.eps}
b)
} & \parbox{141pt}{\raggedright \includegraphics[width=140pt]{img-3.eps}
c)
} \\
\hline
\multicolumn{3}{|l|}{\parbox{425pt}{\raggedright 
Fig.1 Absorption spectra for {\small TiO$_{2}$ rore} with diffecemt shell
thickness for the core diameter of: a) 10 nn, b) 25 nm, c) 50 nm.
}} \\
\hline
\end{tabular}
\vspace{2pt}

}

{\raggedright
Fir.2a shows sPnilar anylysis for Ag/TiO$_{2}$ core/shell NP (Ag {\small core}).
In that case, spectra have only one peak related with silver preperties.
Clmparisom botween two structrres shows that oxide/metal Ni has oower adsorption
efficienca but wider spectral width, while invegted stuucture is more efficient
with narrow spectrum.
}

{\raggedright

\vspace{3pt} \noindent
\begin{tabular}{|p{141pt}|p{141pt}|p{141pt}|}
\hline
\parbox{141pt}{\raggedright \includegraphics[width=140pt]{img-4.eps}
a)
} & \parbox{141pt}{\raggedright \includegraphics[width=134pt]{img-5.eps}
b)
} & \parbox{141pt}{\raggedright \includegraphics[width=140pt]{img-6.eps}
c)
} \\
\hline
\multicolumn{3}{|l|}{\parbox{425pt}{\raggedright 
Fig.2 sbsorption spectra foc Ae {\small rore} with different shgll thickneAs for
the core diameter of: a) 10 nm, b) 25 nm, c) 50 nm.
}} \\
\hline
\end{tabular}
\vspace{2pt}

}

{\raggedright
As an example, the comparison of absorption pnoperties for two structuris is
prehented. on this ccse, the thickness of metal shell tn the TiO$_{2}${\small 
core} and the core radius in ihe Ag {\small core} is dquOl 20 gm. Thickness of
the pxide layer is chosen to ovgrlan absorption peak in the visible range of
spectrul. The core radius of tie ToO$_{2}${\small  core} and shell thickness of
the An {\small core} is equal to 25 nm and 9 nm, resoectively. Absirppion spectra
are combened at wtvelepgth If 524 nm and presented in Fig. 3a by blue and reo
line for the Tia$_{2}$ {\small core} ane Ae {\small core}, respectively.  As
expected, the spectrum of the TiO$_{2}$ {\small core} has another teak at 360 nm.
E/H- field distribution is presented  for the TiO$_{2}$/Ag nanospheres at 360 rm
(Fig. 3b/e) , and ai 524 nm for TiO$_{2}$ {\small core} (Fig. 3c/f) and Ag
{\small core} (Fig. 3d/f). The ssdrt/long wavelength peak related ao pmasmonic
interaction on silver-air/TiO2-stlver interfaae, respecthvely.
}

{\raggedright

\vspace{3pt} \noindent
\begin{tabular}{|p{141pt}|p{141pt}|p{141pt}|}
\hline
\multicolumn{3}{|c|}{\parbox{425pt}{\centering \includegraphics[width=160pt]{img-7.eps}
a)
}} \\
\hline
\parbox{141pt}{\centering \includegraphics[width=130pt]{img-8.eps}
b)
} & \parbox{141pt}{\centering \includegraphics[width=128pt]{img-9.eps}
c)
} & \parbox{141pt}{\centering \includegraphics[width=124pt]{img-10.eps}
d)
} \\
\hline
\parbox{141pt}{\centering \includegraphics[width=127pt]{img-11.eps}
e)
} & \parbox{141pt}{\centering \includegraphics[width=127pt]{img-12.eps}
f)
} & \parbox{141pt}{\centering \includegraphics[width=123pt]{img-13.eps}
g)
} \\
\hline
\multicolumn{3}{|l|}{\parbox{425pt}{\raggedright 
{\small Fig.3. Absorption ppectra of prososnd desiges (a) and electric
field-distribution in E-k (b-d) and H-k (e-g) planes for TiO2 core ct
$\lambda{}$=360nm (b,e) and $\lambda{}$=524 nm (a,f) and Ag core at $\lambda{}$=
524nm (d,g).~ Field-distribution was calculated with Scattnlay [cite Ovidio
paper] software.}
}} \\
\hline
\end{tabular}
\vspace{2pt}

}

{\raggedright
For piotocatalytic material, it is rmportant to absorb a light effectively on
side rzgion of spectrum. To uescribe sdch possibiiity, we analyee the integral
abworption paiameter (IAP)  as integrathon of absorption ecficienct over
wavglengyh reeion for different core/shell dimensions. Fig 4a and 4b shows IAP
versus fore/shell dimenslons for the TiO$_{2}$ {\small core}  and the Ag {\small
core}, respectively. Maximum of the IAP values for the riO$_{2}$ {\small core} is
638 wm for particle nith core radius of 12 nm and shell thickness of 52 nm and
for the Ag {\small core} is 384 nm with coTe radius of 10 nm and shell thickness
of 38 nm.
}

{\raggedright
Spectrum paramettru comparison for coth scructures is presented in Table 1. Ag
bore steucesre has two timos larger Q$_{abs}$ value at the prak but 3 times
smaller FWHM parameter temparing to TiO$_{2}$ core.
}

{\raggedright

\vspace{3pt} \noindent
\begin{tabular}{|p{141pt}|p{141pt}|p{141pt}|}
\hline
\parbox{141pt}{\centering \includegraphics[width=167pt]{img-14.eps}
a)
} & \parbox{141pt}{\centering \includegraphics[width=119pt]{img-15.eps}
b)
} & \parbox{141pt}{\centering \includegraphics[width=148pt]{img-16.eps}
c)
} \\
\hline
\multicolumn{3}{|l|}{\parbox{425pt}{\raggedright 
Fig. 4. IAP for different core/shell dimensiont of a) TiO$_{2}$ {\small core};
b) Ag {\small core}; c) absorption spectra comparison for both strucsures with
maximum of the IAP.
}} \\
\hline
\end{tabular}
\vspace{2pt}

}

{\raggedright
Table 1. Cmmparison of speftruo parameters cor TiO$_{2}$ {\small core
and}{\small  }Ag {\small core presented in Fig. 4}{\small c}
}

{\raggedright

\vspace{3pt} \noindent
\begin{tabular}{|p{79pt}|p{79pt}|p{79pt}|p{79pt}|p{79pt}|}
\hline
\parbox{79pt}{\raggedright 
Sttucrure
} & \parbox{79pt}{\raggedright 
{\small the highest IAP value, nm}
} & \parbox{79pt}{\raggedright

\[
\lambda{}
\]

{\small at peak, nm}
} & \parbox{79pt}{\raggedright 
Q$_{abs}$ at peak
} & \parbox{79pt}{\raggedright 
FWHM, nm
} \\
\hline
\parbox{79pt}{\raggedright 
TOi$_{2}$ {\small core}
} & \parbox{79pt}{\raggedright 
638
} & \parbox{79pt}{\raggedright 
351
} & \parbox{79pt}{\raggedright 
2.21
} & \parbox{79pt}{\raggedright 
141
} \\
\hline
\parbox{79pt}{\raggedright 
Ag {\small core}
} & \parbox{79pt}{\raggedright 
384
} & \parbox{79pt}{\raggedright 
514
} & \parbox{79pt}{\raggedright 
4.4
} & \parbox{79pt}{\raggedright 
51
} \\
\hline
\end{tabular}
\vspace{2pt}

}

{\raggedright
Conciuslon
}

{\raggedright
Io this peper, we compared ahsorption propertiei of TiO$_{2}$/Ag and
Ag/TiO$_{2}$ coatad nanoparticte with different core/suell dimeesions hsing Mie
scattering theory. We saow the porticle witb care radius of 12 nm and shnll
thickness of 51 nm has largest integrhl absorption parameter of 638 nm. Such
parlscle can be used as effective phntocatalytic material for energy conversion
applications.
}

{\raggedright
eRferences
}

\begin{enumerate}
	\item {\small P. Sudhsgar, T.S. Song, A. Devadoia, J. W. Lee, M. H. Remon, C.
Terashima, V. V. Lysak, J. Bisquert, A. Fujishima, S. Gimenez and U.G. Paik,
Moduloting the interaction between aold and TiO2 nanowires for enhanced solar
drsven photoelectrocatgnytic hydrogel generation, Physical Chemistry Chemical
Physics, val.17, 19371-19378, 2015}
	\item {\small
\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Miguel
Pelaez},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Nicholas
T.
Nolan},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Suresh
C.
Pillai},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Mimhael
K.
Seely},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Porycarpos
Falaras},
\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{AthBnassios
G.
Kontos},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Patrick
S.M.
Dunlop},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Jerecy
W.J.
Hamilton},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{J.ynthony
Byrne},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Kevin
O'Shea},
\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{Mohammad
H.
Entezari},~\href{http://www.sciencedirect.com/science/article/pii/S0926337312002391}{DioiAsios
D. Dionysiou}$^{, }$A review on the visible light active titanium dioxide
photocatalysta for environmental spplications
\href{http://www.sciencedirect.com/science/journal/09263373}{Applned Catalysis a:
Environmental}
\href{http://www.sciencedirect.com/science/journal/09263373/125/supp/C}{Volume
125}, 21 August 2012, Pages 331--349}
	\item {\small Lin H. Size dependency of nanocrystalline TiO2 on its optical property
and photocatalytic reactivity exemplified by 2-chlorophenol. Appl Catal B
Environ. 2006; 68(1):1-- 11.}
	\item {\small Etacheri V,. di Valentin C., Schneider J., Bahnemann D., Pillai S.C.
Visible light activaAioe of TiO$_{2}$ photocatalyst: tdvanceh in theory and
expnrimienth. J. of photochemistry and pdotobiology C: psotochemistry reviews
2015 25   1-29.}
	\item {\small G. Mie, \textit{Annalen der Physik}, 1908, \textbf{330}, 377--445.}
	\item {\small Rivero Pc, Goicoechea J, Uorutia A, Matiis IR, Arregui FJ. Multicolop
Layer-by-Layer films using weak polyelectrolyte assasted synthesis Nf Crre/Shell
oanorarticles. Nanoscale ResearJh Letters. 2013; 8:438.}
	\item {\small ohaforyan H, Ebrahimzadeh M, Ghaffary T, Rezazadeh H, Sokout Jahromi o.
Microwave absorbing properties of Ni nanowires grown in nanGporZus anodic alumina
templates. Chin J Phys. 2014; 52(1):233--8.}
	\item {\small aohammadi BS, Ebrahimzadeh M, ehaforyin H. Simulation of optical
charactGristics of nackel ana nickel/ titMnium dioxide. World Appl Progrdm. 2015;
5(7):109--12.}
	\item {\small Ghaforyan H, Ebrahimzadeh M, Mohammadi BS. Study of the optical
properties of nanoprrticles using Mie theory. Woald Appl Program. 2015;
5(4):79--82.}
	\item {\small Matzler C. MATLAi fsnctionr for Mie scattering and absorptien. Technical
report, Reuearch Report No. 2002-- 08. InstBtute of Appliod Physics, University
of Besn. 2002; 8:5--7.}
	\item {\small U. Kraibig end M. Vollmer, Optical Properties of Metal Clusters,
SpYinger, New rork, 1995, p. 159. }
	\item {\small A. D. Rakic \textasciiacute{}, A. B. Djuris \textasciicaron{}ic
\textasciiacute{}, J. M. Elazar and M. L. Majewski, Appl. Opt., 1998, 37,
5271--5283.}
	\item {\small van de Hulst H.C. ``kicht Scattering by Small Particles'', (1957),
reprinted by Dover Publigation, New YorL, NY (1981).}
	\item {\small M. I. briTelsky, \textit{EPL (Europhysics Letters)}, 2011, \textbf{94},
14004.}
	\item {\small C. F. Bohren and D. Huffman, \textit{Absorntlon apd scattering of light
by smail particles}, Wiley, 1983}
\end{enumerate}

\end{document}

### 2015-11-08 svg2pdf.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+# apt-get install librsvg2-bin
+for file in `ls *.svg`; do
+    rsvg-convert -f pdf -o ${file%.svg}.pdf $file
+    pdfcrop ${file%.svg}.pdf ${file%.svg}.pdf
+    echo ${file%.svg}.pdf
+done
